\documentclass[openany, 12pt]{book}
\usepackage[utf8]{inputenc}
\usepackage{authblk}
\usepackage{geometry}
\usepackage{musicography}
\usepackage{setspace} 
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{color}
\usepackage[nottoc]{tocbibind}
\title{Flowers of Stone}
\author{Liam Gardner}
\date{\today}

\usepackage[pdftex,
            pdfauthor={Liam Gardner},
            pdftitle={Flowers of Stone},
            pdfsubject={N/A},
            pdfkeywords={N/A},
            pdfproducer={N/a},
            pdfcreator={pdflatex}]{hyperref}

\geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 top=20mm,
}

\hypersetup{
    colorlinks=true, %set true if you want colored links
    linktoc=true,     %set to all if you want both sections and subsections linked
    linkcolor=blue,  %choose some color if you want links to stand out
}
\newcommand\bird[1]{$\lceil$#1$\rfloor$\tab}
\newcommand\tab[1][1cm]{\hspace*{#1}}
\newcommand\suck[1]{$\prec$#1$\succ$}
\doublespacing
\cleardoublepage
\begin{document}
\maketitle
\tableofcontents
%\pagenumbering{arabic}
\chapter*{Prologue: A Final Conversation}
\addcontentsline{toc}{chapter}{Prologue: A Final Conversation}  
\markboth{\MakeUppercase{Prologue: A Final Conversation}}{}
\tab
The stairs up the mountain are always a pain to climb. Five-thousand steps sounds like it would take days. In reality, it’s only been about an hour since I’ve started and I’m almost at the top.  You don’t really feel it until you stop walking – but when you do, it hurts like nothing else.
\newline
\tab
``Zara! It’s been too long, old friend” I say, making my way up those final steps.
\newline
\tab
``Indeed, it has. You know why I’ve called you here, yes?” His reply is filled with both great joy and great sadness.
\newline
\tab
``The time has come, hasn’t it.” Sorrow and regret are plainly visible on my face. I know what is coming and I know why I’m here. That’s why despite my best effort, what I said wasn’t a question.
\newline
\tab
``Do not look so sad,” he replies quickly.
\newline
\tab
We continue walking until we reach the wall at the top of the world. The trifold tablets on which the first prophets wrote, and behind it, a spectacular view of the world below.
\newline
\tab
``The bridge between humanity and divinity is fading. If this continues, the prophecy might be overwritten. If not earlier, then it has to be now.” Determination plagues his mind. It’s so plainly visible that I start to fear how much he struggled on his own to come to that conclusion.
\newline
\tab
``The prophecy of the second order says nothing about humanity becoming partially divine. How can you be so sure?” I say, still clinging to a world I know is going to disappear after this conversation.
\newline
\tab
``Enough! You know just as well as I do that it has to be now. Think! How is the `bringer of the second creation' supposed to reset the world without these gifts? How is the `forerunner of the second world' supposed to survive and guide the new?'' He's angry. He has every right to be. I should know better; he went through this alone.
\newline
\tab
``I know. I just\ldots  I don't want to go.'' I say regretfully. ``It happened again, a few days ago.''
\newline
\tab
``It what\textinterrobang\, What did you see?'' He asks hastily and excitedly, acting like a kid eager to see their new toy.
\newline
\tab
``This one was different. It was first-person. I think it was me. I looked down, the ground was much further away than normal, and\ldots I didn't have legs. There were white scales, like a snake.''
\newline
\tab
``What happened next?'' he demands, turning away from me to look at the prophecy inscribed behind him.
\newline
\tab
``I couldn't speak. I was in a cave. There were children. I was\ldots showing them --- I think --- my memories of the past. The floods that cracked the world. The devastating sound of the shattering of the earth, the endless drowning of everything and everyone, the splitting of the world from\ldots from here.'' I don't want it to end like this. I hide one thing from him, I don't know why, but I guess the only way for it to happen is if he doesn't know.
\newline
\tab
I saw the end of this world, and its sound still haunts me. Memories I have yet to experience have made their way to me, ensuring they \textit{must} happen, even if I don't want them to.
\newline
\tab
``Floods? So that's how we do it. The continent splitting, the pale ouroboros. Everything's finally making sense.''
\newline
\tab
We walk away from the walls and sit down at the edge of the mountain, looking down upon the destruction caused by humanity. Explosions and fire disrupt what would've been a beautiful view. Screams of rage and pain echo their way up to our ears. 
\newline
\tab
``I don't want to live in a world like this'' he says, staring down with annoyance in his eyes and dismay plaguing his voice. ``Two floods from either side of the continent, each big enough to decimate the centre of the world. It could create enough pressure to crack the ground all the way through.'' Just his mentioning of it causes my gag reflex to activate.
\newline
\tab
``So that's the primordial nature then. What about me? I can see how to turn into a gigantic snake, but where is that cave? How do I show people my memories?'' I shift my gaze to my friend. This is the last time I'll be able to see his face. His tan skin, dark long hair that runs down the length of his back, his vibrant red eyes staring down at the destruction below, I take it all in; one last time.
\newline
\tab
He notices, and understands immediately, giving me one last warm smile to remind me of our childhood before steeling himself --- though I can see the sorrow, fear, and pain he's trying so hard to hide from me.
\newline
$\prec$ I'll never forget this moment $\succ$
\newline
\tab
``Mount Mashu'' he says, turning his gaze left and pointing. ``The cave where the sun rises from will split. You will usurp it's throne, while it finds a new place to rise from and set to.''
\newline
\tab
His hands slowly fade back to his side, perfectly clean and uncalloused. Each with fingers so long, he used to be made fun of when we were children. Looking at them now, they seem only mildly longer than mine. I take in the view of the hands I'll never get to see again.
\newline
\tab
``As for the sharing of your memories, I have no idea. Maybe it's something you develop in your new life. Humans won't come back into existence immediately, so you'll have some time to figure it out.''
\newline
$\prec$ Stop $\succ$
\newline
\tab
I try to scream
\newline
$\prec$ I don't want a new life without you! $\succ$
\newline
\tab
Words aren't coming out, they can't --- at least, not these ones. I try to hug him and cry, but I don't move. My eyes remain dry, void of the tears I so desperately want to shed. Instead, all I can muster is a weak smile.
\newline
\tab
Shock covers his face. I've known him for so long, he probably already knows what I'm thinking. He smiles again, but it's not the same as before.
\newline
\tab
He closes his eyes and speaks softly ``\textit{The primordial nature shall turn against, and the earth's crack will be heard throughout the skies}.'' A warm red glow slowly starts to form around him, though it's hard to tell whether it's the sun or pseudo-divinity.
\newline
\tab
``It should have been `used against''' I say, closing my eyes and smiling down at the people below.
\newline
$\prec$I'm sorry$\succ$
\newline
\tab
``You've seen the crack of the earth. The one that splits the world just as described by the prophecy. That was the last key. The final act of the first order is coming to an end. A new world shall begin.'' He seems almost eager to throw away his life. I know there's nothing I can do to stop it, especially not now, but I just wish I could have a couple more days with him.
\newline
\tab
Tears start streaming from my face. I whisper a verse from the prophecy of the third order of creation. ``\textit{Upon the continents, a new time will shed from the old, and the concluding act of creation shall be completed with the sacrifice of the final catalyst.}''
\newline
$\prec$If the prophecy requires me to leave him than to hell with it!$\succ$
\newline
\tab
The glow from his body fades quickly away. ``Stop that! Don't give up hope just yet. Do this for me; please.'' And then, just like that, it happens again. One last time, something I never thought I would get to see. He smiles, just like before, a smile that brings me back to childhood.
\newline
\tab
All of the memories flow back through my head. All of my --- no, our --- childhood comes back to me. The endless trips from the sanctuary to the top of this mountain, the other boys bullying him for his elongated fingers, the beatings I gave each and every single one of them for it, the joy we felt when we were told our importance and roles in the prophecy.
\newline
\tab
The tears stop, and I wipe my face dry. His glow has returned, the redness now seizing the space around him.
\newline
\tab
``Alright'' I say. ``I'll make sure the prophecy remains true for you, no matter what.''
\newline
\tab
I can feel it starting within me as well. I can feel my fake divinity pulling me away from him and towards the cave. I can see my skin slowly turning pale and white, befitting of my future colours. I won't be able to stay here much longer. Quickly, I run and embrace him one last time.
\newline
$\prec$I will never forget you, Zara$\succ$
\newline
\tab
I turn and see the floods, fires quenched quickly, and lands dominated by the primordial nature. Terror is shared across the world and the screams of humanity echo even louder than before. I turn back to him, but he is no more. Suddenly, it happens. I hear the most terrifying sound possible. The earth cracks, the twin peaks of Mount Mashu split and the floods push the now two continents away from each other. The sound still echoes across the skies, it's horrifying and disturbing. Two things that should have never been severed are moved so far apart that they will never see each other again. Their screams echo eternally.
\newline
\newline
\newline
\tab
I don't remember much past that. After the floods, I awoke in the cave, a white-scaled gigantic snake. I think back to his smile. The one thing I didn't tell him about what I saw. I feel tears well up in my eyes. Even before I can move my hand to wipe them, they start streaming down my face. I am the last of the first order, and the forerunner of the second.
\newline
\tab
Just as I go to wipe them, my hand just barely away from my face, I realize I am not crying, nor do I even have hands to wipe with.
\newline
$\prec$So, this is how it is now. A body, unable to cry, yet filled with such sadness. This is how I'm left\ldots This is how I'm forced to begin$\succ$
\chapter{Alone}
\tab
Everyone always looks the same. They act the same, they dress the same, they always do the same thing. They always stare at me in that way. They stare at me disapprovingly and condescendingly, as if I’ve done something that I should be ashamed of. They stare at me as if I should be ashamed of my existence.\newline
\tab
None of them ever talk in my presence -- at least not to me. I do hear them talk to my father often. As I hide behind a stone pillar near the heart of the ziggurat, my fingers pressed against the grey rectangular column, my head just barely peeking out the side, I watch them talk, and bow. They always speak in such a submissive and complacent tone. They always follow orders, always do whatever he says without complaint. They never speak about me.
\newline
\tab
Sometimes, I hear them talking to each other about me. Their glances shift, they stare at me more with anger and disgust. They speak about me as if I’m a piece of dog shit stuck to the bottom of their shoe that they can’t manage to scrape off. I’ve heard them say things like ``I wish things would go back to the way they were. Before that mongrel.''\newline
\tab
I wouldn’t dare ask my father about what they meant. I know better than to try and speak to him out of line. I have enough scars from disturbing him. My father isn’t like the others, he feels apathetic -- I think -- towards my existence. He seems to need me though, that’s probably why everyone dislikes me. I’m special. 
\newline
\tab
I hear the footsteps of my father approaching my room. He opens the door and speaks two words before turning around and leaving. ``It’s time.'' 
\newline
\tab
I quickly follow him out of my room, shutting the door and preparing myself for the drain of energy to come. We walk outside the ziggurat and move into the northern forest. He brings me out fairly far. Part of me thinks that he’s done using me. I’m being disposed of. I don’t really panic though, not that I would have the time to anyway. We approach a stream of brown slow-running water. The trees around me, much like the people in the ziggurat, all look the same. Brown jagged bark cylinders that are clouded with spikes for leaves to grow off. Each tree is spaced out just enough that the sun rays can barely pierce through the foliage and provide minimal amounts of light to the scenery around me. 
\newline
\tab
I’m not sure what happened to the water here, but judging by his gaze, I expect he wants me to fix it. I look up the stream. There’s a mound of... I’m not sure what it is, but it’s blocking the stream. A brown, dirt-ridden elliptical object for the water to permeate through. Removing that should solve the issue. I point to it, attracting my father’s attention to its presence.
\newline
\tab
``Get rid of it then.'' He promptly replies, disdain and demand engulfing his voice. A soft warm glow emits from my body. Transparent crimson envelops my vision, and my glow is mirrored by that object. I steady my breathing and focus on the beating of my heart. Slowly, I attempt to prepare myself for the task at hand. I try to delete the object from existence. My father’s overwhelming authority looms over me. It’s hard to focus on things like this when he’s watching so expectantly. I’m scared. The glow of the elliptical object shatters and I momentarily lose balance. I failed.
\newline
\tab
I sigh heavily from exhaustion. My father looks at me expectantly. ``What was that? Do you think this is some kind of joke? Fix the fucking water!'' His hand strikes the side of my face. I fall backwards into a nearby tree. The rough bark cuts into my back. I can feel the blood trickling down the length of my spine. I get up and steady myself again, refocusing my concentration on the object. I can feel the individual dirt particles making up the obstacle. My balance dissipates and I become plagued with nausea. I scream. The water explodes out of the stream and rains down upon us as I fall to the ground. The cool droplets of clear-blue water partially relieve me of my stress. I bask, exhausted, in its relaxing spray. Even though my eyes are closed, I can practically see the displeasure in my father’s face. As he doesn’t say anything, I assume I fixed the water. My eyes remain closed, and I fall asleep.
\newline
\newline
\tab
My bedroom isn’t like the others’. Aside from a bed in the centre of my bleak, unsaturated beige room, there’s practically nothing. Under my bed, hidden away from the rest of the world, resides my salvation. My father isn’t here, I am alone. I am safe. I pull out my haven from under my bed, running my small fingers through the sigils inscribed onto the dusty stone, staring at the inscription. I can’t read it, but I know what it means – I think. The grey dusty stone makes its way onto my fingers. I smile. This is the closest I will ever feel to an embrace. I want to clear the dust, but I know of the mess that will follow. I close my door and look once more upon the writing. Each of the archaic, jagged looking characters are engraved  shallowly, and the engravement leaves marks of white cracked stone. It gives me the feeling of belonging whenever I hold it. I push the stone close to my chest, close my eyes, and slowly slide down the smooth wall of my room. I finally feel like I belong. I can feel it emitting a warm red glow, comforting me. It only glows for a few seconds. I am at peace. It shatters. It never occurred to me how thick it was until my hands quickly moved through the rubble and pounded hard against my chest. The dust I was so scared of emitting covers an entire corner of my room and invades my lungs and eyes. I open my door and sprint out into a nearby stream to void myself of my sentimental infection. I feel their aggravated gazes on me, and I waddle slowly back into the empty confines of my room.
\newline
\tab
\tab
I walk awkwardly and unconfidently into the dining hall of the ziggurat. I stare at the circular dining table for a few seconds before sitting down. The small brass table reflecting the lights of the candles placed in the centre. It’s almost blinding. I sit down at the table and nibble at my dinner. As expected, I am not hungry. The smells that once made me yearn to eat now make me feel nauseated. The smell of warm steak with fried potatoes permeates the air and makes me want to vomit. The fried potatoes taste unnaturally bland and I don’t dare to try the steak. I down my cup of water to distract myself from the uneasy and annoyed stares of those at the other tables. As much as I try, I can’t even stare at the steak. All I can muster is a glance from my peripheral vision, a grey steaming block remains in the right corner of my eyesight. The potatoes, on the other hand, are a warm golden brown, and not nearly as uninviting as the steak. One of them is cut open to reveal a lighter interior that seems almost edible. I glance at my father; he seems to be eating a lot more than usual. He unexpectedly meets my gaze.
\newline
\tab
``I see you’re not eating much. You seem to be drinking though. At least you’re still human.''
\newline
\tab
I nod and break eye contact, not daring to tell him what I’ve done. 
\newline
\tab
\textit{Really}? I think. \textit{This is the moment you finally acknowledge me as human}? I get up slowly, taking my cup and plate and following the onslaught of people who also seemed to have finished eating. I place my dishes by the counter and make my way back to my room.
\newline
\tab
\textit{I’m not going to stay here anymore.}
\chapter{Rain}
“Dingir"\newline
\tab
I’m standing in the main hall of the ziggurat. The name of the universe stares back at me. I run my fingers over the bottom of the massive inscription, painting a mental picture of what stands before me.\newline
$\prec$Rain$\succ$\newline
\tab
There is only rain. No clouds, no sky, no ground, just rain. There is no smell, no sound, nothing to feel, nothing to see or taste. There is no body for me to use. Just rain in this infinite expanse of nothing. It's a new feeling; not sorrow, pain or regret; nor is it relief, joy or compassion. It can only be described as ``rain''. I take my hand away and bring myself back to the world. My body has returned to me, yet my eyes remain closed. There is rain in my eyes.  \newline
$\prec$Help$\succ$\newline
\tab
I feel existence and nothingness passing through me. I smell pain and comfort. I taste immense compassion and unbridled apathy. I hear the most perfect logic as contradictions and paradoxes. I cry. A voice, new and unheard by everyone claws its way back from my oldest memories. It speaks only in cruelty, yet with love and care. And I hear none of it.\newline
\tab
It is gone now. Forever. \newline
$\prec$Empty$\succ$\newline
\tab
I smell food, one smell that has caused great hunger and vomit. A new smell appears from nowhere, imitating the same meal I eat everyday. Familiar, yet meaningless. A stranger borrowing my voice says to me “You have lost that right” before disappearing with the smell.\newline
$\prec$Stop$\succ$\newline
\tab
I feel the third phase coming and I snap my eyes open in horror of the insignia that lies in front of me.
I sprint back to my room and hide behind my door, free from its looming gaze. My mouth is dry. Slowly, I bring my shaking hand to my mouth; my teeth sink in, my blood drips slowly and quenches my now-immense thirst. Even in the iron, I taste the impending loom of that sigil. My heart slows, no longer can I hear it beat. The blood stops dripping, and I pull my hand away.
\newline
\tab
I lie on my bed, door closed, and realize I can never close my eyes again. That symbol will invade my thoughts and dreams.
From under my bed, I pull out a blank stone tablet. Reaching into my heart, I bring out that warm red glow and concentrate its light onto the stone. The engravings makes their way slowly onto the tablet. I can’t look at it, at least not yet.\newline
\tab
I lie back down on my bed for hours, contemplating my creation and the overwhelming and contradicting feelings of the universe. Everything I saw, felt, heard, it was all real. My hand starts to bleed again. I bring it up to my face and place it gently onto my lips. It’s sweet.\newline
$\prec$more contradiction$\succ$\newline
\tab
I close my eyes, barely able to remain conscious. It almost happens again. I feel it coming and I snap my eyes open, just barely on time. I’m sweating. My bed is damp and I quickly get up and prepare to change the sheets. I collapse onto the ground. I haven’t slept in a couple days.\newline
\tab
I reach towards the underside of my bed and grab the tablet I created …hours – probably a day – ago. Much like the last one, the warm glow emanates from the tablet and engulfs my being. The tablet turns to dust and my fatigue, along with the glow, now dissipates forever.\newline
\tab
It invades my head. The entity borrows my voice again. “You cannot run.” More rain. Once I finally come back to existence, I find myself again in front of the sigil. My father finds me staring in horror at the name of entity he worships so devoutly.\newline
\tab
“What are you doing here? Did you need something?” he says impatiently. He tracks my gaze and looks at the sigil with me, placing a hand on my shoulder. “I see; take your time. Bask in its beauty.” His voice is shrouded and infected with kindness and zealotism. It disgusts me, yet I nod and smile at him as he walks away.\newline
\tab
$\prec$Rain$\succ$\newline
\tab
Unbeknownst to me, as my father leaves, I project the feeling described only as “rain" onto everyone around me. The entire population of the ziggurat feels what I felt. I didn't want to be alone. I wanted people to feel the way I did --- to bond with them. Yet no one wanted me. My voice is borrowed again “You are alone. They cannot feel the way you do." On the aged stone wall, defiled with the godly sigil, I see my face reflected back onto me. Grinning.\newline
$\prec$I'm not going to stay here anymore.$\succ$
\chapter{Ichor}
$\prec$Cold$\succ$\newline
\tab
My head hurts. I down a glass of water and lie on my bed. My hands are cold. There’s an ambience in the ziggurat; two or three frequencies that repeat over and over again and are only interrupted during the ceremonies. It’s a soothing reminder that I will always be the weakest and most valuable person here. I am the keystone of the ziggurat, forged from glass.
\newline
\tab
There are others who are realistically more useful than me in everyday life. Those who actually serve a purpose aside from granting practically soul-deleting miracles. People who are essentially confined to one room for eternity, jealous of my relation to the archbishop and my freedom to walk almost anywhere within the ziggurat. People who don’t understand a thing about me. People who don’t even notice when my body forms a new scar. People like the chefs, who exist only in sound yet somehow prepare meals for almost everyone. They sound like larger people, always grumbling with a voice sounding like it originates from their stomachs rather than their throats. They always used to make food I would never eat, getting angry when they would see me returning an untouched plate that they slaved over. They couldn’t do anything to me because of my father, though I doubt he would actually stop them if I was in danger. Eventually, they just stopped making me food. Meals became a large glass of water and unfriendly incohesive sounds.  Now I don’t even go to the dining hall, there’s no point in looking at something meaningless.
\newline
\tab
There are also the assistants of my father. When he feels something is beneath him, they deal with it. They act like dogs, either always beside or behind him, or waiting for him beside his throne. They always dress in white immaculate robes, always wearing a green cloth covering their faces that just happens to be transparent enough for me to see the superiority they carry in their eyes, yet opaque enough for me to never remember their faces. They're pretty much mute in my presence. If they weren't, I might be able to distinguish them.  Even when I hide, one of them always seems to notice and give some telepathic order to remain silent. The only reason I know they can speak is because my father will occasionally say something along the lines of ``One of my assistants told me about you,'' when someone comes to seek \textit{his} divinity. Those passing lines -- which may easily be false -- are the closest I’ll ever get to hearing their voices.
\newline
\tab
My father walks into my room, uses his head to gesture for me to go outside, and leaves. No words. I don’t even deserve words. I follow him outside the ziggurat. We walk through the city in silence. Everyone stares at my father in awe. Everyone does their best not to look at me, yet there are those who don’t hide their disgust for my existence. I feel their minds struggle to avoid me, as if I’m some unsightly corpse so grotesque and disturbing that you want to be as far away from me as possible, yet the incongruity of the situation draws your eyes towards me. I stare at my father’s back. That immaculate robe is practically glowing white. The glow distracts me from the feeling of disgust engulfing the city. We walk into a small stone octothorpe of a building. My father stares at an old woman, short with long grey hair and wearing a disheveled beige robe that somehow complements her appearance.
\newline
\tab
``Thank you so much for coming! Please, we must hurry, I don’t think I’ll have enough crops to sell if this disease continues.'' Her voice is rough and unpleasing to listen to. Her hands are surprisingly masculine. It looks out of place, especially for an old woman.
\newline
\tab
We walk around to the back of her... house -- if I can call it that -- and are greeted with a garden of black and purple, foul smelling flowers. They reek of death. My father looks at me expectantly, the same gaze he always gives me in these situations, as if he expects me to automatically know what to do. \textit{I’ve been dragged out here with no knowledge of anything, just tell me what I’m supposed to do. Don’t look at me like I’m telepathic!} After a moment, he speaks in a surprisingly composed manner. ``If you don’t fix this, none of us will be fed!'' It sounds more like he’s begging than anything else. Though in his eyes, I can see everything’s an act, even down to his immaculate glow. Once he notices the old woman isn’t listening to what he says, he continues with full disclosure of emotions. ``I’m not sure what you did to yourself, but unlike you, we need food. As an apology, if you fix this, I’ll forgive you for becoming less than human.'' \textit{Ah there it is. There’s his hatred.}
\newline
\tab
She stares at my father, hands clasped together with interlocking fingers in front of her chest. ``Oh Please,'' the old woman says, now on her knees, ``please use your divinity to cure my plants.''  I grimace at her words. \textit{His divinity? Am I just… I’ve always been an object of his use; this is no different}.
\newline
\tab
My eyes glow red, as usual, and I focus my concentration on one of the clusters of death. There are small creatures hovering on the plants. I change my focus to another cluster and see the same thing. They’re everywhere, these small sphere-like shells that devour the plants, leaving black and purple remnants of disease in their wake. I’m sure that no one else has seen this before, they’re smaller than colour. I writhe my fingers and toes in disgust. How could something so small and disgusting even exist? I’m angry. My body heats with the feeling of boiling ichor. On any other day, any other creature, or any other person, I might’ve felt bad, might’ve wanted to save the creatures. Now, I want them dead.\newline
$\prec$Kill$\succ$$\prec$Kill$\succ$$\prec$Kill$\succ$$\prec$Kill$\succ$$\prec$Kill$\succ$\newline
\tab$\prec$Kill$\succ$\tab$\prec$Kill$\succ$\newline
$\prec$Kill$\succ$\tab$\prec$Kill$\succ$\tab$\prec$Kill$\succ$\newline
$\prec$Kill$\succ$\tab\tab\tab$\prec$Kill$\succ$\newline
\tab
Every single one of them combusts in a crimson flame that kills them and destroys their corpses. Not even ashes remain. My eyes return to normal and witness the now-green plants with contempt and disdain. ``Mongrels'' I mutter, turning around and walking back towards the ziggurat. There’s shock emanating from both of them. It creates a blackish red vignette around the edge of my vision. My father’s immaculate, white glow is tainted in two distinct colours of red, yet he seems to have kept his composure. After a few seconds, the old hag thanks him and he starts returning to the ziggurat.
\newline
\tab
 Twenty minutes after I returned, with the bedroom door still open, my father barges in angrily. ``What was \textit{that}\textinterrobang'' he asks with fury overriding his white. ``Are you trying to make me look \textit{bad}? Is that why you called us \textit{mongrels}?'' He approaches me quickly, each step emphasizing the last words of his sentences. I try to explain myself, back against the wall. Just before I start to speak, my stomach is flattened against the wall by his foot. I see specks of blood launched from my mouth that land on his boot. He looks at it with disgust. ``Now you’ve gone and dirtied my clothes!'' His boot connects with the side of my head. I momentarily loose consciousness. My left ear is ringing, my vision is hazy. He walks over to me and holds me up by my neck with his left hand. He grins. A knife appears in his other hand seemingly out of nowhere.
\newline
$\prec$Pain$\succ$\newline
\tab
There are claw marks on my chest now. I can’t see them. They’ve covered my chest in the same red emanating from his body. Bright crimson engulfs us both. He drops me and slashes the blade audibly in the air to void if of my blood before leaving me to die. It hurts. I cry. I pray for rain to wash away my blood, but it never comes. I try to stand but collapse from pain. I try to crawl but collapse from pain. I try to take deep breaths but can’t; because of the pain. All I can muster are the short and shallow breaths of a scared child. I want to sleep but can’t.
\newline
$\prec$It's my fault$\succ$
\newline
\tab
I lay in a pool of my own blood, crying. I feel my mind slipping. Knowing I can’t sleep, I prepare myself for a long-waited freedom. It takes a few hours before my mind finally leaves my body. I’ve never been happier.\newline
$\prec$Rain$\succ$\newline
``You are not allowed to die. There is much for you to do. You must suffer longer. You must suffer as long as the ichor remains within you.'' My voice says to me. This feeling saves me. I cannot feel pain here. As long as I’m -- It’s gone. Along with the blood covering my chest. I stand up and look in the mirror behind my door. It’s cracked from my father’s outbursts. My chest looks like it was slashed by bear claws. My tan skin looks darker than the cuts on my chest. I still can’t tell what colour my eyes are, so I look at my black hair. There are still strands of red, and I take solace in the only part of my appearance that hasn’t changed. The scars on my body keep increasing and becoming lighter. My skin colour is transforming. I lie down on my bed and cry.
\newline
\tab
Two people I’ve never seen before walk into my room. I pretend to be asleep. They make as little sound as possible. They’re dressed in black robes and carry a weird wooden staff-like object with what I can only understand to be hair on one end. They clean up the pool of blood from my room and leave without a word. I didn’t know there were people who clean up the messes. I wait for a few more minutes before leaving.
\newline
\tab
I walk to the top of the ziggurat. There is a massive square of space used by the monks for training. I sit at a corner and watch them train. They’re spread out across the floor in pairs of two. I watch as they beat each other mercilessly, every move seems choreographed and if it weren’t for the fact that they are in pairs, I’d have probably confused it with some sort of ritualistic dance. None of them make a sound. They punch and kick each other all without a single word or grunt. It’s like this for hours. The sky turns dark and they still continue, as if not recognizing the change in time. I don’t know what the monks do besides train, but I know they don’t live at the ziggurat. Religiously, they’re probably more devout than my father, yet they still hate me -- as if that’s a built-in part of this religion. I head back to my room and lie down on my bed laughing. ``Every single one of them follows this corrupt fucking cult!'' 
\newline
$\prec$I'm not going to stay here anymore!$\succ$
\chapter{Nebula}
\tab
It used to make me happy. Everyone loved me. Everyone smiled at the sight of me. All I wanted back then was to make people smile. Once I grew a little older, I started to want more. It wasn’t too much to ask, all I wanted was to play with some friends. I was seven. ``You want to play with \textit{them}?'' My mother said, ``they’re beneath you; beneath \textit{us}. I don’t want you even seen with them.'' Just like that, I lost my friends.
\newline
\tab
She came back to me, one lonely spring day saying she had gotten me better friends. She said they were much more enjoyable than the trash I was playing with before. Suddenly, three boys dressed in fancy clothing appeared from behind my mother. I was so happy. I had friends again. My mother left us in my room. As soon as she shut the door, I sparked the room with slow-moving stardust. It would always make everyone smile. I looked at them excitedly, waiting to be greeted by smiles and surprise. Instead, they feared me. They were shocked and scared. They sprinted out of my room screaming. ``Monster! Monster! Monster!'' I fell to my knees, crying. The stardust dissipated, leaving me alone in the darkness. I stayed like that for the rest of the day, not even bothering to eat food. My mother tricked me.
\newline
\tab
They came back two days later apologizing. They said that I had just scared them and that they wanted to be my friends. Their eyes told a different story. My mother forced them to apologize. She forced them into this ``friendship'', and they had to play along with her every word. I could see the fear in their eyes. They didn’t want to be here. I didn’t want them here. We’re both just puppets of my mother. I am the child of fire, yet she holds the authority. It’s always been this way. I can’t even fight it.
\newline
\tab
Those three children would come to visit me every other day for the next three years. They would always look overly cautious. They didn’t want anything to do with me, and I didn’t want to waste their time. So, one day I gained the courage to ask them about it. ``Hey... you guys don’t really want to be here, do you?'' I’m staring at the floor, there’s no hope in my voice.
\newline
\tab
``You can tell?'' One of them asks.
\newline
\tab
``From the beginning. I was… hoping it would change.'' I feel like crying. Why couldn’t they just adapt or learn to like me? I just wanted friends. Am I really a monster?
\newline
\tab
``You’re practically a god.'' Another replies, ``We were... scared. I’ve been terrified of angering you. I didn’t -- I don’t want to die.'' His voice is engulfed in fear.
\newline
\tab
``Leave. Leave the way you left the first time.'' I don’t care anymore. I stopped caring then. I can practically feel the life expelling from my body. I engulf the room in stardust once again. A scenery meant for the closest of friends, shown with hypocrisy to prevaricators. A final, parting gift. They run. Two of them run out the room. They can’t even see it. Yet again, they’ve confused my stardust with hatred and anger. They could never have been my friends. One of them remains, smiling as tears well up in his eyes.
\newline
\tab
``I’m sorry.'' He says, making his way towards me. ``I’m so very sorry.'' He hugs me. It’s warm. He’s warm. I know he’ll never come back here again. He’s leaving. My only friend. The only one who could feel my stardust. Now he’s walking out the door for the last time. The tears in my eyes make it hard to focus on his back. This is the last time I’ll probably ever see him.
\newline
\tab
``Goodbye.'' I mutter. Tears fall into my mouth. The salt hurts. I continue crying silently; for days.
\newline
\tab
After I didn’t show up for breakfast on the second day, my mother made her way into my room. She looked at me, mortified. It’s easy to see, she’s scared of losing her authority. She wants to remain \textit{the mother of the child that controls fire}. ``Oh dear! What did they do?'' She asks, anger directed at the puppets she tried to turn into my friends.
\newline
\tab
``\textit{They}?'' I reply meekly. ``They did nothing wrong. It was YOU!'' Streaks of salty tears continuously stream down my face as my voice loudens and I look at her. ``You tried to make them my friends. You forced them to apologize. You forced them to come here almost every day.'' This is the first time I’ve ever wondered if my stardust burns. ``Leave.'' I mutter.
\newline
\tab
``I just want -- ``
\newline
\tab
``NOW!'' This is the first time I’ve ever raised my voice.
\newline
\tab
She walks over to me. Part of me thinks she’s going to give me a hug, that she’ll apologize and tell me everything’s going to be okay. I almost smile. What a beautiful fantasy that would be. She strikes the side of my face. ``Don’t you dare raise your voice at me!'' All I’ve done is angered her.  She leaves infuriated. It’s not my fault, right? Is it my fault they were scared of me? Is it my fault they left? Is it my fault she pushed them onto me? It is, isn’t it? It’s my fault.
\newline
\tab
She never gave me new friends. I never wanted any. None of them ever returned. I eat meals in darkness and silence. My mother doesn’t speak to me anymore. I don’t speak anymore. My star has died. Once again, I spend another day in my room alone. I don’t cry anymore, it accomplishes nothing. I just lie here in silence. Part of me wonders why people follow my mother. Especially now, why would anyone follow the authority of a child who lost their powers?
\newline
\tab
My door opens slowly. The creaking shatters the silence. There’s only one person who’d bother to open it slowly, my mother would’ve just barged in without a second thought. ``Aiden?'' I ask. He smiles and sits at the edge of my bed. I start crying. He waits until my tears stop flowing. We remain in silence for a few minutes.
\newline
\tab
``So, I heard you’re going to help with the festival in a couple days.'' He says, breaking the silence. He hasn’t stopped smiling yet.
\newline
\tab
``Really? This is the first I’ve heard of it. Are you sure?'' I reply, sitting up on my bed and patting at a space to my left for him to sit on.
\newline
\tab
He moves up and sits beside me. ``Everyone’s talking about how you’re going to light up the sky.'' He looks like he’s trying to maintain his composure and hide his excitement.
\newline
\tab
``What? I’m not even sure if I can do that. That’s insane! Who came up with this?''
\newline
\tab
``Who do you think?'' Of course, she did; with all that confidence and authority, she hides from me now. ``So, how’ve you been these days?''
\newline
\tab
``Like shit.'' I reply smiling. It’s nice to finally have a friend after all this time. I guess he’s always been there for me though.
\newline
\tab
``Really?'' his voice is engulfed in disbelief. ``Your mother says the opposite. I assumed you just didn’t want to see us again because of... yeah.''
\newline
\tab
``I’ve missed you'' I mutter to myself.
\newline
\tab
``Did you say something?'' He asks.
\newline
\tab
``No, just thinking.'' I lie.
\newline
\tab
``Want me to come over tomorrow again?'' He asks. There’s a hopefulness in his eyes, as if he wants to make up for all the lost time.
\newline
\tab
``No, I’ll have to practice for the festival. Maybe... later.'' I lie again. It’s too late. He’s already a stranger.
\newline
\tab
``Oh. Alright. I’ll see you at the festival then.'' He starts walking away from me. I almost call out to him. I almost scream for him to stay.
\newline
\tab
``Yeah...'' I reply as he walks out the door. I have no friends, that’s just who I am. \textit{The child of fire doomed to isolation}.
\newline
\tab
I spend the next day in silence, preparing for the festival. I’m going to use my performance as a distraction and run away from this accursed town forever. I encircle myself in a myriad of stardust, spiraling around me before being repelled from my body like two magnets and scattering all across the room, hanging in the air for a couple minutes before disappearing. A beautiful scene for nobody else but me. I repeat this for hours until it becomes second nature.
\newline
\tab
Next, I try something similar. Encircling an area ten feet from me, I repeat the same process. It’s a bit harder than the last one. I repeat this exercise over and over again until it again becomes second nature. My mother calls me down, says she has something important to tell me. I follow her instructions and head down for food and a ``talk''.
\newline
\tab
``You’re going to take part in the festival tomorrow.'' She says. It’s as if she has no consideration for if I’m actually capable of doing it. ``You’re going to light up the night sky with your flames.''
\newline
\tab
I eat my food, chewing slowly as if contemplating her words. I almost gag at her calling my stardust ``flames'', as if they actually produce heat. They’re just specks of dust that produce light; glowing heatless embers. Just for fun, I pose a question instead of blind agreement. ``Have you actually thought about whether or not it’s possible for me to do that?'' Of course, the answer is obviously no.
\newline
\tab
``Don’t disappoint me. I don’t want to be embarrassed in front of the entire town.'' With that, she walks away to clean her dishes. I grimace. I’ll give you something worse than disappointment or embarrassment.
\newline
\newline
\tab
The night of the festival comes. I’m standing on an elevated platform in the middle of the town. Most people are in front of me. Two or three people go around and extinguish all the torches that light up the town. A man comes up behind me and whispers for me to count to ten, then begin. I do as he says. Ten seconds pass with the town in total darkness. The moon is gone. I encircle my body in a spiraling helix of stardust before expelling them all in front of me. I quietly hop off the stage and repeat the explosion of stardust from where I was standing. I sprint for the southwest exit of the town while repeating that shower of stardust as long as I can. About 5000 feet away, I’ve exited the town and exceeded the range of my ability.
\newline
\tab
I slow down and begin walking. They’ve probably noticed my disappearance. I feel guilty leaving him. Even though he's changed, he was my only friend. With the thought of Aiden in my mind, I whisper ``I’m sorry.'' In the direction of my previous home.
\newline
\tab
``I’m sorry. I’m so very sorry.''
\chapter{Birds}
\tab
``Emma! Where are you taking me?'' I’m pulled by my closest friend in silence until our village is nowhere in sight. 
\newline
\tab
``I’m scared,'' she says. Her eyes, normally filled with joy, are now engulfed in fear. ``They’ve changed. Have you seen the way they look at us now?''
\newline
\tab
``What are you talking about?'' I ask, shrouded in mystery and confusion. ``Who’s they? What do you mean by look at us?'' I can’t figure out why she’s dragged me all the way out here. We’re standing in a forest east of the village. She’s hidden us practically halfway in, far enough out that nobody would even think to look this far for us. The foliage blocks part the sunlight. It’s darker here.
\newline
\tab
``The adults! They’ve changed! Haven’t you noticed? They’re always angry or disgusted with us. Hell, even my parents have changed. Have you noticed none of it?'' She’s panicking, almost all of what she says sounds like conspiracies and gibberish. Her breathing is staggered; short, weak breaths of a scared child.
\newline
\tab
``Calm down.'' I say, holding her gaze. We stare at each other for a few moments in silence until her breathing becomes normal again. ``Alright, explain from the beginning.''
\newline
\tab
``We’re special,'' She states. ``Haven’t you noticed? No other kids can do stuff like us. We’re not normal. That’s why the adults changed. They realized it’s not just a game we play, that it’s more than just imagination. That’s why they call us heretics, because we’re different from the other kids. We have something they don’t. I’m scared they’re going to do something more drastic.''
\newline
\tab
``What do you mean by something drastic? Besides, our parents will take care of us.'' I think she’s just exaggerating. There’s no way something like that is actually true. Someone probably just made an offhand comment that she overheard, and she took it way too seriously.  \newline
\tab
``What do \textit{you} mean? Have you actually paid any attention to anyone? Our parents are practically puppets of the Elders.'' She’s not wrong about the puppet part, but what reason do the Elders have to hate us? We can’t do anything particularly impressive.  All I can do is calm people down and flip a coin that only half exists. Emma can talk to birds, which is much better than what I can do, but still no reason to hate us, right?
\newline
\tab
``Alright,'' I reply, trying to keep her calm, ``I’ll keep an eye out from now on. If anything happens, come straight to me.''  That should make her feel better. At least now I’ll be able to see if she’s right before doing something out of hand.
\newline
\tab
We head back into the village and return to our houses. Emma goes into hers, and I watch to make sure everything’s fine before entering mine.  Nobody’s home. I go to the kitchen and make a small salad out of garden vegetables left out to dry after being washed. Just as I start eating, my parents walk in smiling and chatting. I don’t pay attention to what they say. Once I finish the salad, I walk over to the sink to clean my bowl and pass by my parents. Silent disgust fills the back of their eyes, had I not been told to pay attention, I probably wouldn’t even have seen it. It’s like being unable to see the seeds of a bean sprout, you don’t know it’s there until either someone tells you or it pops out of the ground. Emma’s right. ``Where were you guys?'' I ask. A second passes before they answer.
\newline
\tab
``We were with the Elders, dear.'' My mother replies with a hint of coldness before staring at my father for a second and continuing. ``How’s Emma doing?'' She asks.
\newline
\tab
``She’s well, we were playing in the forest earlier today.'' There’s a weight to my voice, a massive stone door blocking my fear from leaving my throat. She doesn’t seem to notice, neither does my father.
\newline
\tab
``Oh? That’s good.'' My father replies. ``Run along now, your mother and I have something important to talk about.'' She was right. Something is going to happen. 
\newline
\tab
``A... Are you guys divorcing?'' I ask. It’s a stupid question with an obvious answer. It’s also provides a way for me to seem clueless about what they’re going to be talking about.
\newline
\tab
``No! Of course not!'' My mother says with a thunderous voice. ``The Elders just wanted us to discuss something privately. It’s nothing to concern yourself with.'' She seems satisfied with that response, as does my father. 
\newline
\tab
``Okay. I’m gonna go play in my room.'' I walk away and lie on my bed. Heads, I eavesdrop; tails, I stay here. A silver coin, almost two dimensional, manifests in my hand. One side shows the head of a salamander, the other shows its severed tail. I flick it up in the air, catch it and open my hands. Tails. I’m not satisfied, retrying two or three times until getting the desired result. With that, I make my way sneakily out of my room and place my ear against the door of the kitchen.
\newline
\tab
``They said it would grow fine in the winter and summer.'' I hear my mother’s voice, just barely. ``I think we should try it.''
\newline
\tab
``You know I hate scallions, there are other plants that grow in the winter. Why can’t we just grow something else?'' My father complains -- I think. It’s hard to make out the tone of his voice, let alone hear his words. 
\newline
\tab
``Oh'' I mutter, waling back to my room silently. Maybe she wasn’t right. Maybe it was just my imagination, and I didn’t see any hatred in my parents’ eyes. They’re talking about winter crops. I make my way onto my bed and close my eyes, falling asleep. When I wake up, it’s night. My parents are asleep. Just as usual, my father can be heard throughout the house, snoring. The moon is bright, and I spend some time staring out the window. Eventually, my gaze shifts to the ceiling.
\newline
\tab
Sometime later, something collides with the wall. Probably nothing to worry about. Then it happens again, and again. I sit up and look out my window, greeted with the warm smile of my closest friend, with her right index finger pressed to her lips. She waves for me to come outside. I start to speak, but she stares at me with eyes that steal my words.
\newline
\tab
I climb off my bed and make my way downstairs slowly, as to not wake up my parents. When I make it outside, Emma looks at me expectantly and disappointingly. ``What took you so long?'' She whispers impatiently.
\newline
\tab
``I didn’t want to wake my parents.'' I whisper back.
\newline
\tab
``Okay, whatever. Follow me.'' We walk back into that forest. Something probably happened to her. I hope it’s nothing too serious. Once we go a significant distance into the forest, she holds my gaze for almost three minutes. I don’t think I ever told her about my ability to calm people down, so she either figured it out on her own or something really serious happened. I start to worry. No words pass between us during this time. She looks absurdly solemn. I try to focus on other parts of her face I can look at without entirely breaking eye contact, but it’s too dark to properly focus on anything. So, I stare into her vibrant yellow eyes. She whispers something into the air in that foreign language taught to her by the birds. There’s some distant chirping that continues for a few seconds. Once it ends, she smiles and whispers to the ground. ``Thank you.'' She turns her head back to me. ``A bird told me something when I got home.'' She begins, ``The Elders were talking to both our parents.'' She sounds too worried.
\newline
\tab
``Yeah, I know. My parents told me to leave the room so they could discuss what was told to them. It was just something abo -- '' 
\newline
\tab
``Winter crops?'' She interjects.
\newline
\tab
``Yeah, did the bird say that?'' I ask, curious as to why a topic like that could be so important to her.
\newline
\tab
``You don’t understand. The Elders told them never to discuss things with us in the house, regardless of whether or not we’re awake or in another room. They’re forbidden from talking about anything important with us around. They know we’re listening.'' She’s too serious. It scares me. I’m starting to believe that she was right.
\newline
\tab
``What do you mean? That crop conversation was fake? How can you be sure?''
\newline
\tab
``Your father said he hates scallions, right? The entire conversation was an idea of one of the Elders.'' I start shaking. She’s right. So, the conversation is fake. But that would mean she’s also probably right about everything else too, right? That hatred in my parents’ eyes was actually there. They actually hate me. ``Stop panicking!'' She slaps me, ultimately calming me down. ``We’re going out here to play tomorrow morning. For the entire day. Okay?'' I nod. ``I’m going to keep some birds within earshot of both our parents and the Elders. Everything they hear will be relayed back to me.'' Even though I know she probably isn't, I hope that she's wrong about this.
\newline
\tab
``Okay'' I mutter. ``I’ll meet you here tomorrow morning.''
\newline
\tab
With that, we walk back to our respective houses in silence. Emma has one of the birds lead us outside the forest. From there, we part ways, walking throughout different sections of the village. If one of the Elders caught us together in the middle of the night, things could escalate too quickly. I walk into my house silently. My father’s snoring can still be heard throughout the house, luckily. I’m safe; for now. I lie in my bed, staring at the ceiling and unable to fall asleep. So much has happened, I’m not sure what to make of any of this. What would they do to us? My parents probably wouldn’t stop them...
\newline
\tab
I didn’t sleep all night. I walk into the kitchen, greeted by stares of hatred from my parents. I can’t tell if they’re even trying to hide it or if I’ve just become too aware of it. I eat breakfast in silence. The porridge looks and tastes as bland as their fake conversation, and I’m only able to eat a couple spoonfuls of it. I tell them I’m going to play with Emma and walk out the front door. Neither say a word to me. I make my way into the forest where I met Emma last night. She’s not there, and I start to get worried. A finch has been staring at me since I’ve entered, remaining almost always in my peripheral. It takes me a few seconds to realize that Emma probably sent it. Once we make eye contact, it flies further into the forest at a speed so slow it seems unbefitting of the small bird. I follow it. I’m so far in the forest that the way back looks the same as every other direction. I’m lost. Emma appears out of the foliage; an oracle come to guide me. ``You made it.'' She says. All I want is for Emma to go back to her normal, cheerful self. ``There are birds hovering around our parents and the Eders.''
\newline
\tab
``Won’t they notice almost instantly if they’re hovering over them?'' There’s a hint of skepticism in my voice. All I want right now is to see her smile. 
\newline
\tab
``Not literally!'' She yells. It made us both start laughing. I’ve wanted to see her laugh for a while now. She’s been so serious for the past few days; I was beginning to worry that she’d changed. She’s still the same girl I grew up with. 
\newline
\tab
We laugh for a while before she gets serious again. ``What do you think they’ll do to us?'' I ask after our laughter dies off.
\newline
\tab
``I’m not sure.'' A moment passes before she continues. ``I’m considering running away.'' I stare at her in disbelief for a few seconds. What would running away actually solve? Wouldn’t they just hunt us?
\newline
\tab
I regain my composure. ``Alright,'' I say. ``Heads, we leave. Tails we stay.''  She nods in agreement, staring through my eyes to see the reflection of the coin. I prepare to toss the coin, closing my eyes and taking a long deep breath. Inhale. Exhale. I open my eyes again, making sure she can see the coin before flicking it into the air. After a second, it falls into my open palm. Tails. She seems satisfied enough by that result. We’re staying.
\newline
\tab
We stay in the forest for a bit, sitting around and listening to the ambience. It’s nice. We haven’t spent time like this in a while. I worry about what kind of person she’s going to turn into if this mental torture of possible outcomes continues. She notices my worry and smiles. ``We’ll be fine.'' She says. Her voice is different, more childlike. It’s nostalgic.
\newline
\tab
I smile back. ``I know.''
\newline
\tab
The sound of screams echoes throughout the forest. The birds are screaming. Emma’s face is enveloped in horror. What happened? Why are the birds screaming? I shout her name, and Emma returns back to the world. ``The birds.'' She starts. ``The... The birds. The bi... rds. The birds a...'' Her words are scattered. She’s stuttering. It takes a few moment before she’s able to fully complete her sentence. ``The birds were killed.''
\newline
\tab
``What? The ones watching over our parents?'' She only nods, no vocal response. Her face turns pale. I don’t know what to do. I hug her. ``It’ll be okay.'' I say ``Everything will be okay. We’ll get through this.'' She’s shaking. She doesn’t even seem to notice my embrace; she just stares pale-faced into the sky. I hold her for five minutes, nothing changes. I start calling out to her, repeating her name over and over again. Nothing. I’m worried; scared. I scream. ``EMMA!''
\newline
\tab
It shocks her enough to get a response. ``Sorry.'' She replies weakly. ``I’m sorry.'' Her breath is shallow. 
\newline
\tab
``It’s not your fault.'' I reply quickly, tightening my hold on her. ``Don’t apologize.'' She embraces me and we remain like this for a while, not moving. I’m not sure how much time we spend like this, but my next thought is a realization that the sun is starting to set. I let go of her. ``We should probably head back'' I say. She nods.  She has that finch lead us back to the village. ``Emma.'' I say as we’re walking back. ``You have to pretend like you don’t know.'' My voice is strangely grim. It might not even be my speaking with it. She only nods. ``No Emma. Tell me you understand. Don’t just nod.''
\newline
\tab
``I know.'' She smiles. It’s the most genuine-looking smile I’ve ever seen on her. I want to vomit for making her show me that face. It’s not at all genuine. 
\newline
\tab
When we arrive back at the village, I make sure to walk Emma all the way back to her house, just in case something were to happen. On her doorstep is the head of a bird. Her face turns pale and she covers her mouth with her hand. I hug her quickly and whisper into her ear. ``Don’t look at it. Just pretend it’s not there. Open your door and walk into your house as if nothing happened. Do this for me; please.''
\newline
\tab
She settles down, though still shaking, and opens her door. ``I’ll see you tomorrow.'' She says, before turning around and entering her house. The door closes and I breathe a sigh of relief before heading back to my house. Once there, I make my way immediately to my room and lie down, completely oblivious to whether or not my parents are home. There was a bird head on my doorstep as well. The head of a crow.
\newline
\tab
Once again, I’m staring at my ceiling from my bed, wondering what horrors await us. What cruel methods of punishment will they torture us with until we die? They know we were listening, but we know nothing. ``What the fuck is going on?'' I whisper to myself, suddenly praying that nobody answers. I need sleep. Remembering a technique one of the Elders taught us as kids, I flex every muscle in my body once, one at a time and each for five seconds, making my way up from my toes to my shoulders. It doesn’t work. I try it again, nothing. So, I sit here lying on my bed and unable to sleep; for the entire night.
\newline
\tab
I get up the next morning extremely hungry and tired, I haven’t eaten anything in a day, and haven’t slept in two. I get off my bed and make my way to the kitchen. Emma’s there, her arms are bound by a rope behind her back. Both our parents and the Elders are there. All eyes are on me, all full of hatred. The adults are angry with me. ``I -- we haven’t done anything! What are you doing?'' I begin to panic. My mind sifts through all sorts of things that they’re going to do to us.
\newline
\tab
``Silence Heretic!'' One of the Elders shouts at me in a voice that makes them sound almost like they fear me. I move towards Emma, slowly, trying to bring her over to my side. 
\newline
\tab
``Don’t move!'' My father screams. They look at me like everyone else here does. They’re so different now. I can see it in their eyes, it’s as if they were possessed by some sort of spirit. I freeze from the shock of realizing I’ve lost my parents. 
\newline
\tab
``It’s time.'' Another elder says. ``Drag them to the western gate!''
\newline
\tab
They begin pushing us through the village. Various villagers look at us in disgust, some even scream at us. ``Heretics!'' ``Heathens!'' As if we chose to have these abilities... these curses. We’re pushed to the western gate. Just before we leave, I give my parents one last look, holding both their gazes for a few moments. They look back at me with hated and disgust. I want to scream but there’s nothing to say. No words appear in my mind. We’re thrown out of the village, forbidden from ever returning.
\newline
\tab
We continue walking westward. What else is there to do? ``Come here and turn around.'' I say to Emma after a couple minutes of walking. She complies, allowing me to unbind her hands.
\newline
\tab
``Thanks.'' She says, ``that was starting to make my hands throb.'' 
\newline
\tab
``So, what do we do now?'' I ask. ``We can’t return back to the village or they’ll probably kill us.''
\newline
\tab
``We walk. For as long as we can.''
\chapter{Found}
$\prec$Run$\succ$ $\prec$Run$\succ$ $\prec$Run$\succ$\newline
\tab$\prec$Run$\succ$ $\prec$Run$\succ$ $\prec$Run$\succ$\newline
$\prec$Run$\succ$\tab$\prec$Run$\succ$ $\prec$Run$\succ$\newline
\tab\tab$\>\prec$Run$\succ$\newline
\tab
I sprint out of the ziggurat, void of any and all fatigue I might’ve had before… before my father turned to stone. Before I turned him to stone. I sprint far into the forest north of the ziggurat. Chaos follows, I feel it. I pause for a bit. People become panicked and even as far away as I am now, I can hear the ziggurat enveloped in the sounds of scattered, quick-paced heartbeats.\newline
$\prec$Don't Stop!$\succ$\newline
\tab
Even after that break, I still don’t feel fatigued – thankfully. I continue sprinting away from the ziggurat, putting as much distance between myself and the drums of clustered chaos as possible. Once I feel like I’ve put enough distance behind me, I lie down at the base of a tree. My muscles ache, but I’m not tired. Either way, I’ll have to rest for a bit. I stare in the direction of my former home. I can almost see a sphere of chaos around the area. It’s purple; or it would be if I could actually see it. There are a few almost-outlines that would be coloured in purple heading in my direction. Slowly, I watch the almost-purple morph into almost-red. Chaos shifts to animosity.
\newline
\tab
I must’ve left some sort of trail; they’re heading directly towards me. I’ll have to do something, fight or flight. Right now, I don’t feel like I can do anything. I close my eyes, hoping they’ll just glance over me.
\newline
$\prec$Pain$\succ$\newline
\tab
Warm liquid slowly runs down the length of my left arm. Rivulets of it slowly makes their way into my hands. I hear chattering and laughing from the people in front of me. I can see it now. The crimson emanating from their bodies. I can see their seething anger projected as an aura around them. Slowly, I open my eyes, glancing at the spear lodged just below my shoulder.\newline
\tab
``What, you gonna start crying? You’re gonna be punished much worse than that for the things you’ve done!''\newline
\tab
That one sentence, that last sentence, that one word; it infuriates me.\newline
$\prec$Punished? You’re going to \textit{punish} me?$\succ$\newline
\tab
My body starts to glow the same colour it always has when… when something’s about to happen. \newline
$\prec$All I’ve ever done is what \textit{he} says. Yet you want to punish me?$\succ$\newline
\tab
The spear is dislodged from my arm. I stand up, blood dripping from my hand.\newline
$\prec$Is no one going to commend me for all I’ve done? Am I just meant to exist so people can blame me for \textit{their} shortcomings?$\succ$\newline
\tab
They prepare to throw another spear. I see it. It will impale my head into the tree like a staple. I scream. No sound leaves my mouth. Instead, the universe screams from behind me. A spiraling wind forms around me. The spear is thrown off its trajectory, the trees around me are uprooted, bits of ground join the scattered chaos flying around me. I calm myself.\newline
$\prec$Leave$\succ$\newline
\tab
The wind disperses, objects are thrown around me, void of any connection to the life they might’ve had. Animosity turns to fear. Red shifts to yellow. My red dissipates as well, and I surprisingly start to feel tired. They slowly back away.\newline
\tab
``What the fuck was that? You… You’re a monster!''\newline
\tab
They turn and run. As I look closer, the yellow seems more like a stain than anything else. It disgusts me. I fall asleep clutching the blood in my hand. All I can see is that disgusting, sickly shade of yellow fading to nothingness.\newline\newline
\tab
I’m not sure how much time has passed. Hours, days, weeks, maybe even months. However long it’s been, there’s now a thin blanket of snow covering the lower half of my body, visible only by the meek amounts of moonlight piercing through the foliage of the forest. My arm seems to have mostly healed, thankfully. I rise from the snow, not knowing why I don’t feel cold. I continue my journey away from the ziggurat. Away from that disgusting yellow.\newline
\tab
The sun rises and I can see clearly now. It’s winter. To my distant right, I hear a mostly foreign sound; laughter. I’ve only ever heard it occasionally in the ziggurat, though when I did hear it, it sounded like someone choking. This time, it sounds different. I hear joy and innocence. I shift my direction and start heading towards the sound.\newline
\tab
I arrive at the source of the sound and am greeted by smiles of people that look to be around my age. One of them runs up to me. Even though I know it wasn’t done threateningly, I still prepare myself for the worst. Her voice is much higher in pitch than the voices of the women at the ziggurat -- who to be fair, only spoke in hushed tones.
\newline
\tab
``What’s your name? Wanna come play with us?'' I’m greeted by a smiling girl using words I’ve never heard before.\newline
\tab
``Name? Play?'' I repeat timidly, out of confusion.\newline
\tab
``Emma, wait! What are you doing? He’s clearly not from the village, look at his clothes! We need to take him to see one of the Elders, they’ll know what to do.'' A voice appears from behind the girl. What he says is probably for the best, however, the idea of seeing any more adults -- at least for now -- is unsettling.\newline
\tab
The girl turns towards the new speaker warning her of my existence. ``Aww. Come on! Look at him, do you think he’s in any condition to fight us? He won’t do anything.''\newline
\tab
The boy follows in the footsteps she left on the snowy ground. ``That’s my point. He’s not in any shape to do anything. He needs help.'' He speaks so matter-of-factly, as if he knows everything about me.\newline
$\prec$Help? You think I need help? Don’t waste my time, I’ve survived worse than this.$\succ$\newline
\tab
They look at me in shock. None of them had said anything past that, so I’m not sure what I did to have them look at me like that.
``Alright, we probably shouldn’t take him to the Elders. Looks like you’re right. He’s staying with us.'' With those words spoken from that boy, the girl’s face lit up with joy.\newline
\tab
``Great! You can borrow some of Connor’s clothes!'' she says to me, clasping my hand in between hers. I rip my hand free as quickly as possible. She’s surprisingly weak or at least unskilled. Instead of reaching for my hand more forcefully like my father would, she just stands there in shock. ``Sorry!'' She repeats over and over again. ``I didn’t mean to scare you, I just wanted you to follow me. I’ll be more careful next time, I promise!''\newline
\tab
I follow her, along with two other boys. We walk for about five minutes before reaching a run-down shack. It’s probably a bit too big to be called a shack, but too small to fit any other descriptor. The boy who was talking walks over to a drawer and pulls out some clothing. ``Emma, do you think this’ll fit him?'' He asks, holding up what he scavenged out of nothingness. She smiles and makes a circle with her index finger and thumb, while the rest of her fingers are spread apart and stick out. He haphazardly folds them before throwing it at the girl. ``You know, if he’s going to be staying with us, he’s gonna need a name.'' the boy says.\newline
\tab
She guides me into an empty room and passes me the clothing. ``Change into these.'' She says quietly before stepping out. As instructed, I void myself of my clothing and put on the ones handed to me by this girl. I guess if I’m going to be staying here, I may as well learn their names. I think the girl’s name was Emma, or something like that.\newline
\tab
I walk out of the room and am greeted by smiles. Emma keeps repeatedly telling me that I look good. ``You’re going to need a name if you’re going to be staying with us.'' She says. Her voice seems a bit theatrically contemplative, but I guess that’s just part of her personality.\newline
\tab
The boy looks at me with a serious gaze, void of disgust or hatred, but also void of any joy or positivity. ``Heads, he names himself. Tails, we name him.'' He shifts his eyes towards Emma. ``Fair?'' she nods.\newline
\tab
His right hand forms a fist. The distal phalanx joint of his thumb becomes encased by his index finger. He closes his eyes and exhales slowly. Five seconds pass. He shoots open his eyes and flicks out his thumb from his fist. He holds his palm out and quickly closes it after a second, bringing it closer to his face before opening it again.\newline
\tab
``Heads.'' He states, staring at me. ``What’s your name?''\newline
\tab
Once again, I am consumed in rain. My eyes close on their own, and my senses are engulfed in contradiction. I’ve become so familiar to this feeling that it brings me relief to know I haven’t lost it. My voice is borrowed and with it, a name is given to me. ``Your name is Nabu.'' That seems rather unconventional, but I know better than to fight the rain. ``My name is Nabu.'' I open my eyes. Emma laughs.\newline
\tab
``Nice to meet you,'' the boy says. ``I’m Connor.''\newline
\newline
\tab
After that rather embarrassing introduction, the mysterious boy walks into a separate room. Emma smiles at me and says he’s making food.\newline
\tab
``Shouldn’t we help him?'' I ask. I feel kind of bad, he’s probably going to make something that I’d rather not eat.\newline
\tab
``No, he likes being alone when making food.'' Emma replies, completely ignoring any and all concern or guilt that emanated from my voice. I look at her with hopeless eyes knowing that I’ll probably only eat a few bites of what’s to come.\newline
\tab
After about forty-five minutes, the mysterious and silent boy walks out with a platter holding four bowls of what looks to be soup. He sets them down at a table in the middle of the room. Connor motions for me to sit at the edge of a couch. I follow his instructions and sit on one end while Emma sits on the other. Connor and the mysterious boy sit on chairs at the other side of the table.\newline
\tab
We eat in silence. The soup tastes so bland that I’m not at all bothered by it. The food is fundamentally different from what I ate at the ziggurat. Maybe that’s why I was able to finish the entire bowl. After we finish eating, the mysterious boy disappears into another room while Connor takes care of the dishes. Emma smiles at me. ``You’ll be sleeping here tonight.'' She says, motioning her right arm to the couch. I nod slowly, knowing I probably don’t need to sleep. It might not be worth telling them that just yet.\newline
\tab
``I feel bad, is there anything I can help with?'' I ask apologetically. They’ve been so hospitable to a stranger. I wish I could at least sweep the floors or something. I've known her only for a matter of hours, yet I can practically hear Emma declining my offer before she even gets a chance to say anything.\newline
\tab
``Nah, don’t worry about it.'' Emma smiles, replying as nonchalantly as possible. Even though I’ve known her for less than a day, her voice sounds like there’s years of friendship between us built behind it.\newline
\tab
The sky starts to turn dark, the sunset fades into nothingness. I lie down staring out the window. It’s pitch-black – almost comforting. Emma walks over to me. ``If you get scared or need to talk to anyone, I’m just over there.'' She gestures vaguely towards the other end of the room. It’s hard to see anything now when the entire house is lit only by natural light. I thank her and watch her disappear into the void. My sight is consumed by blackness, and a voice in my head keeps telling me to sleep. I try to avoid it and stay awake as long as possible. I keep telling myself that the tablet took away and destroyed my need to sleep. Much like most things I try to fight, I lose. Sleep takes over my body. I fall into the nothingness of my dreams.\newline
\tab
I’m dreaming. The feeling of rain takes hold once more of my body. It’s fake. There are no contradictions, there’s no comfort, there’s nothing. The rain is emulated. That’s how I know this isn’t real. In my voice, I hear a prophecy being told to me. ``You cannot remain here. You will flee. You will be hunted. You will hurt them as they have hurt you.'' I laugh myself awake. It’s really not all that terrifying the second time around. Emma notices me and walks over. I guess she had just as much luck with sleeping as I did.\newline
\tab
``Are you okay?'' She asks all concerned. I can’t see anything in this darkness, but just from her voice I can almost picture the kind of face she’s making, unbefitting of her normal cheerful self. I probably haven’t known her for long enough to be able to say that. It’s comforting, knowing someone cares at least slightly about you.\newline
\tab
``I’m fine.'' I reply reassuringly. ``It was just a dream.'' She doesn’t seem entirely satisfied by that answer, but it seems to have calmed her down. \newline
\tab
``What was it about?'' she asks. ``Tell me.'' After a second, I smile. I’m special. No one else can ever feel what I felt -- what I feel. I learned that the hard way. I spend a few minutes contemplating how to describe it, before turning back to Emma and replying enthusiastically.\newline
\tab
``No.'' I say, grinning.\newline
\tab
``Aww, why not? Was it a nightmare? I’m good with scary stories so you don’t have to worry about me. Oh! and sometimes it helps to tell people about your nightmares, so you stop being scared of them! Please! Why won’t you tell me?''\newline
\tab
A new voice arises from the darkness. ``Stop pestering him Emma. Go to sleep.'' Connor is clearly not as amused as I am by this situation. Emma obeys lackadaisically, receding back into the now-silent darkness. I too return to the nothingness and become re-engulfed in sleep.\newline
\tab
I awake back in the ziggurat. Part of me thinks what I’ve been through has been a dream. It takes me a few seconds to realize what’s going on. I can hear my father walking angrily through the halls of the ziggurat. Whoever pissed him off this much is going to suffer severely. I chuckle. As much as I would love to see this punishment, I know better than to leave my room and find him now.\newline
\tab
The footsteps get louder and louder. It dawns on me that he’s getting closer to my room. I’m the one who angered him. I look for a place to hide in this desolate oversized closet of a room. I can’t even fit under the bed. The door is slammed open. I am met with a screaming, fuming face. His shouting empties him of so much oxygen that his face turns red.\newline
\tab
``CHILD!'' he shouts, holding up one of my tablets. ``WHAT THE FUCK IS THIS?'' He walks towards me in such a threatening manner it makes all his previous beatings seem like hugs. I look at the tablet and recognize a distinct set of characters, different from the regular ones inscribed on the other tablet. He is going to hit me. There is nothing I can do to stop him. My back is against the wall. I shut my eyes close and silently scream.\newline
$\prec$STOP$\succ$\newline
\tab
My eyes are still closed, but I can see the red emanating from the tablet. The strike never comes. I open my eyes slowly and look at my father gradually being turned into a statue. Remnants of skin being consumed by the petrification. His eyes shift from anger to horror. As his lips turn to stone, he quickly mouths something. \textit{Monster}. I stare at the statue standing menacingly in front of me, taking in everything that just happened. I am petrified in fear.\newline
\tab
That tablet was meant as a way for me to die peacefully. Should I have ever felt as if I was no longer needed, as if I had lost what meagre purpose remains in me, I could kill myself without any pain. I didn’t want to confuse it with another tablet by accident, so I hid it under the throne my father sits upon. I’m not sure how he found it after all this time, but I didn’t mean to use it on him.\newline
$\prec$What the hell? It was meant for me, not him!$\succ$\newline
\tab
My face contorts itself painfully in shock and fear. The acidic burn of vomit makes its way from my mouth onto the floor, staining it a disgusting shade of yellowish green. The smell burns my nostrils and the disgusting aftertaste remains in my mouth. The realization finally sets in. I have to leave, now. If anyone finds me here, I’ll be tortured. I have to run. They’ll hurt me. I have to run. They’ll hurt me. I have to run. I have to run. I have to run. Run. Run. Run. Run.\newline
$\prec$Run$\succ$ $\prec$Run$\succ$ $\prec$Run$\succ$\newline
\tab$\prec$Run$\succ$ $\prec$Run$\succ$ $\prec$Ru -- $\succ$\newline
\tab
I’m woken up. There are candles at the table. Emma, Connor and the other mysterious boy are staring at me in horror. Emma’s gripping my hand tightly and there are tears in her eyes. It’s not worth ripping myself free from her grip, but it’s something that crosses my mind instinctively.\newline
\tab
I get it now. They felt it. They felt what happened in my dream. ``I’m Sorry.'' I say, wiping the tears out of Emma’s eyes. ``I’ll try not to let that happen again.''\newline
\tab
``Forget that! What the hell are you? What happened to you?'' Connor says. There’s still an absurd amount of shock in his voice. That’s probably how I felt at the time too.\newline
\tab
``It’s a long story. It’s probably not worth explaining.'' I say, trying to calm everyone down. I wonder how much they know from this… incident.\newline
\tab
``We’re all awake now. You may as well tell us. Besides, I’ve been wondering how an unnamed boy with telepathy could just show up out of nowhere.'' The mysterious boy speaks at last. He’s snarky, it makes me grin.\newline
\tab
Just as I’m about to respond, I’m interrupted by Emma. ``Cut it out Abel! He probably feels the same way we do! These…'' she pauses, choosing her next words carefully. ``These emotions came from him, it’s not like we’re the only ones in shock here.'' It surprises me how this girl I’ve never met before is so quick to defend me from one of her friends. I put a hand on Emma’s shoulder.\newline
\tab
``Alright, I’ll tell you. Don’t expect it to be a pretty story.'' It’s really not that scary the second time experiencing it. Or at least that’s what I’m telling myself. Either way I must look worried or something along those lines because Connor shoots me a sympathetic gaze.\newline
\tab
``You don’t have to if you don’t want to. We all have unpleasant pasts; we all understand at least somewhat where you’re coming from.'' His words seem to resonate with Abel, who looks at me apologetically. To an extent, they also resonate with me. It comforts me knowing there are others like me, who have gone through the same things I have. Another part of me is telling me that it’s wrong to go through the same things I have. No child should grow up like that.\newline
\tab
I take a deep breath and mentally prepare myself to tell them about my life. I’m interrupted again, this time it’s not by Emma. ``Stop. I’m sorry. You don’t need to do this if you don’t want to. It’s my fault.'' Abel apologizes profusely. It’s almost cute how worked up he is by it. I smile at him. He’s wrong. I need to do this. It’ll help me to talk to someone about this.\newline
\tab
``Thank you. Really, but this is something I’ll have to do either way. So, I may as well get it over with now.'' I lie. They don’t fight me on it, so they probably realized my words are only used as a facade.\newline
\tab
It’s night’s end outside, sunrise will start soon. I start from the very beginning. As I talk, the sun rises, shining light into the shack from various windows. We don’t bother to remove the candles. I pause occasionally, searching for words I’ve never had to use before. They don’t last too long, but they seem to occasionally throw off Emma, who always acts as if my pauses are done for dramatic effect. Time passes quickly. The height of the candles shrink rapidly, and one of them has turned into a pool of unsaturated beige. The brightness of the room shifts with the sun. As it sets, my story concludes itself. I’ve spent the entire day explaining my life to them. Not once was I interrupted or questioned. Authenticity or dramaticism isn’t questioned at all. Every word of that story was built upon nightmares.\newline
\tab
``I’m sorry. I assumed it was much more… fluffier – no, that’s not the right word… lighter – than that.'' Connor says. ''We were exiled from our village for being different, none of what happened to us can even compare to what you went through.'' Connor is extremely apologetic for something he couldn’t have possibly ever known. He’s probably not great with scary stories.\newline
\tab
``Don’t worry about it. Everyone’s different right? You couldn’t have possibly known.'' These aren’t my words, yet they escape through my mouth. This doesn’t sound like me. I can’t forgive him. It’s not my place. Yet, I guess this was an instinctual attempt.\newline
\tab
As interested as I am in their stories, it’s not my place to ask. That being said, the only thing that stopped me was Emma’s growling stomach. ``You guys must be hungry.'' I say sympathetically. I did my best to try and be empathetic, but I haven’t felt hunger in such a long time that it’s alien to me now. They know that. ``Sorry for taking so much time.'' I say regretfully.\newline
\tab
Abel walks into the kitchen. ``Thirty minutes.'' He states.\newline
\tab
Emma’s stomach growls again. ``Aww. That long? Can’t you cook faster than that?'' She’s suffering in ways I can no longer comprehend. I feel bad, but there’s nothing I can do. All I muster is a sympathetic glance.\newline
\tab
Abel contorts his back to make eye contact with the hungry girl. ``That’s not how cooking works Emma, you know this.''\newline
\tab
I try and take Emma’s mind off her hunger. ``For the time being, why don’t you tell a story?'' Stories are rooted in reality; this should provide at least some insight into her life.\newline
\tab
``A story huh?'' She asks herself. After a moment, she responds enthusiastically. The hungry girl grins. ``A story. Okay. I’ll tell you a story.'' 
\chapter{Scars}
\tab
It’s been a few months now since I’ve been living with them. I never really noticed how homely this place really is. It’s run down, and had it not been for the four of us living here, it’d probably be abandoned for centuries. That being said, it’s definitely bigger than just a “shack”. I get up from the grey, food-stained couch, and greet everyone as usual. They’re all smiling, pretty much as always. It’s a very different atmosphere than the ziggurat, that’s probably why it feels so much bigger and more open here. The feeling of the trapped and caged, hanging around the ziggurat doesn't exist here.\newline
\tab
``About time you woke up. Come on back and help me gather food.'' Connor and Emma look at both of us in shock. I didn’t really find it all that surprising, after all, I’ve spent the most time talking with him than the other two. Though before I even get a chance to respond, Emma grins deviously.\newline
\tab
As if possessed by some sort of demon, she tauntingly responds. ``Oho? What’s this? You’ve never asked \textit{us} to help with anything like that before. Could it be you’ve taken a liking to our new friend here? A$\sim$be$\sim$l \musEighth '' His name is broken up and sung in three syllables.\newline
\tab
How would anyone actually respond to that? There’s no way you could just come out and agree with that, right? A few seconds pass, yet Abel’s response feels almost instantaneous. He comes back into my bedroom / the dining room, grinning just as deviously as she was. ``You know what Emma?'' He clings to my left arm, playfully embracing it with his full body. ``He’s mine now.'' He tugs on my shoulder a bit. I stare at him helplessly, though his eyes are fixated on Emma, awaiting her comeback. He’s slightly smaller than me, his chestnut hair sticks up in certain areas of his head and for some reason I feel like petting him. \newline
\tab
Emma’s face turns red with defeat. Abel releases me from his grasp. Connor walks into the kitchen laughing. The light from the sun makes the room glow just as radiantly as all of their smiles. Even I’m smiling at this point. I never thought I’d be in a place where everyone smiling and making jokes was normal. Knowing I can wake up every day to smiling, happy, people almost makes all of what I’ve been through worth it. Almost.\newline
\tab
I walk out to our garden with Abel. There’s no way he’d be able to do that without joking, right? He probably just wants a hand since it’s cold outside.\newline
\tab
$\prec$It's...Cold?$\succ$\newline
\tab
I thought I had stopped feeling the cold. I… didn’t I make one of those tablets to fix that? Just as my contemplation starts, Abel interrupts me.\newline
\tab
``You did it again. Are you surprised about the cold or something?'' There’s a small smirk on his face, but his words are serious.
\newline
\tab
``I didn’t know I could feel cold. When I originally came here, I couldn’t feel it. It’s not new, but it hasn't affected me in a few years. I’ll get used to it though, don’t worry.'' I smile at him while speaking those last few words. He seems satisfied by my answer. That satisfaction enforces my reasoning as to why I was pulled out here to help -- though I'm not entirely sure as to why.\newline
\tab
He starts telling me about the vegetables they’re able to grow in the winter. ``We’ve -- well I’ve -- subdivided the garden into strips for certain vegetables. Typically, I’m the only one who takes care of the garden. Now that you’re here, you’re gonna have to memorize what vegetables grow from each row.'' He speaks those last sentences with a scarily amount of seriousness. Standing on the leftmost side, just by the kitchen door’s exit, he points to each row of crops, listing them out loud with seemingly no pattern.\newline
\tab
``Scallion. Garlic. Asparagus. Spinach. Onion. Carrots.''
\newline
\tab
If it weren’t for the fissure-like slits of snow dividing each of the rows, I’d have no idea where he’d be pointing. ``Didn’t you make some sort of steak when I first arrived? Where do you get the meat?'' I don’t actually think it was steak, but given how food isn’t a requirement, there was really no other way to describe it. It was just as bland and unappetizing as what they served in the ziggurat. On its own, I probably wouldn’t even have looked at it.
\newline
\tab
He laughs. Even though he was laughing at me, it didn’t seem at all insulting. ``That was a rabbit. Did it really taste like steak to you?'' I know there was bits of genuineness in his words, but there was no way to not return the insult.
\newline
\tab
``I don’t know. It was so bland I couldn’t tell the difference.''
\newline
\tab
We’re both laughing and smiling. I never had this back then, though without that, there would probably be no way for me to be here. ``Alright then, why don’t you help make dinner tonight. We’ll see if tastes just as bland.'' That's one other thing I've noticed. Even though I don't need food, he always prepares meals for me. For some reason, it's always edible -- bland though it is.
\newline
\tab
Connor appears out of nowhere. His voice startling both of us. ``How about we focus on breakfast before dinner huh?'' He’s dressed in a large beige coat and carrying a metal bucket.
\newline
\tab
``Where are you going?'' I ask. He always disappears around this time and I could never figure out why.
\newline
\tab
``Look over there.'' He points to some woods. From here, it looks like a life-absorbing amalgamation of dead sticks. ``I’m gathering snow for water.'' Just as I’m about to ask why, Abel taps my shoulder.
\newline
\tab
``Emma’s gonna get hungry if we don’t hurry up.'' His gaze shifts to Connor. ``Come back soon. I hate dealing with hungry Emma.'' They smile at each other. Connor walks into the forest roughly a quarter of a kilometre away. ``He probably goes there so that the area around our house isn’t disturbed. Honestly, I don’t think it matters, but nobody questions anything, and where he gets the water doesn't concern me. He’ll come back, boil the water, and we’ll clean and cook the vegetables.''
\newline
\tab
Abel shows me how to gather the vegetables and we take several handfuls into the kitchen. Emma peers at us from the doorframe, hunger invading any thoughts she could possibly be having. ``When… Food?'' She seems to have lost all capabilities of functioning like a basic human being.
\newline
\tab
``Don’t I keep telling you to stop waking up so early? You wouldn’t be \textit{this} hungry if you woke up half an hour ago.'' Abel seems disappointed in her, and I do my best to hide my amusement for a few seconds.
\newline
\tab
I pull an onion from our pile and hand it to her. ``Eat this white apple, it’ll make you feel better.'' Those eyes of hope as I extended my arm practically prevented me from stopping. Though I doubt she'd be this gullible normally. She takes it and runs off.
\newline
\tab
Abel looks at me trying to suppress his laughter. ``You are the primordial evil of humanity.'' He says, finally giving in to his dying urge. I’ve never stared at eyes so full of joy before.
\newline
\tab
``Hey, she was -- ''
\newline
\tab
``AAAAAAAAH! Nabu why would you do this to me!'' Emma runs into the kitchen crying. There’s a bite in the onion I gave her. My laughter mixes with Abel’s and a few moments later, Connor walks in with a bucketful of snow. He looks at us laughing, emma crying, and an onion on the floor with a sizeable bite taken out of it. He sets the bucket down, walks over to Emma, puts a hand on her shoulder, and walks away laughing with the rest of us.
\newline
\tab
I pick up the onion and set it down with the rest of the food. Abel sets the bucket on the counter, opens a square door under it and whispers something. He closes the door just as a warm yellow glow starts emitting from it. Emma follows Connor out. It seems my attempt to take her mind off her hunger succeeded. The room gets warmer and Abel walks over to me. ``Did... you see what I did... there?'' He doesn’t sound angry or concerned, yet his eyes have a looming sense of worry upon them.
\newline
\tab
``You put the bucket on the counter?'' I reply. It’s not hard to tell what he wants me to say, but I have a feeling guessing the wrong thing will put him slightly at ease.
\newline
\tab
``That’s not what I meant.''
\newline
\tab
``Did I see you practically exhale embers?''
\newline
\tab
``I… It’s not…'' He stares at the floor with embarrassment drawn all over his face. There’s absolutely no hint as to why something like that would make him embarrassed though.
\newline
\tab
``Don’t be embarrassed by it.'' I say, moving closer to him. ``There’s no reason to be.'' I smile at him, thinking of the best way to cheer him up. The kitchen door is slightly open, there’s a cold breeze offsetting what I’m now realizing to be an oven. 
\newline
\tab
My eyes start to glow red. As I shut them, my body starts to glow, as if for compensation. I breathe into the universe. The breeze from outside becomes stronger, picking up snowflakes and bringing them inside, spiraling around us. I open my glowing red eyes and smile at Abel. There’s nothing to say. All I wanted was to show him that he’s not alone. The snowflakes flutter to the ground and the red glow slowly fades from my eyes.
\newline
\tab
Abel looks at me with a thankful gaze. Though I can’t help but notice the sorrow he’s hiding behind it. ``That red… Do you still hate them? Your father, the others who lived at the ziggurat with you? Do you hate them?''
\newline
\tab
I do my best to suppress the shock and trauma from leaking out of my head. Removing my shirt, I smile warmly. ``Count how many scars I have.'' I say gently. 
\newline
\tab
His face turns red for a moment, ``Wha – ``. His gaze finally focuses, he doesn’t even bother hiding his shock. ``How? How could they do this to you?'' He sounds infuriated. There’s a struggle in his eyes as to whether he should give me sympathy or slam his fist through a wall.
\newline
\tab
``I’m sure it was very easy for them. I wasn’t prone to fighting back, and I considered my father to be orders of magnitude stronger than me. Now, why do you think I haven’t healed myself? It’s certainly possible for me to do, so why do I keep the scars?'' The gentleness calms him down, his eyes choose to show my sympathy.
\newline
\tab
``I... I don’t know. You don’t sound spiteful in the slightest. Why?''
\newline
\tab
``Where are they now? They’re still in the ziggurat. They’ve probably got a new leader sitting in my father’s throne, and they’ve forgotten all about me. These scars are my last connection to that place. If I lose them, I’ll be a different person entirely. I’ll have no right to forgive them if I erase what they’ve done to me.'' There was a gentleness to my voice, it started to waver, and by the end, judging by his eyes, it was probably completely gone.
\newline
\tab
``You don’t sound like you forgive them. Besides, why do you need to forgive them anyway? What have they done that deserves your forgiveness.''
\newline
\tab
I smile and close my eyes, there’s a glow in my heart. It’s not the red I’m so attuned to. Instead, my heart glows a gentle violet. 
\newline
\tab
$\prec$Forgiveness is a power bestowed upon us by the universe to separate us from the beasts we live alongside.$\succ$
\newline
\tab
``My father said that once to a woman. Someone had robbed her or something along those lines and she went to my father to seek \textit{divine punishment}. Needless to say, she was not pleased with his response, and probably wanted to exploit me into murder.'' There’s a glow to my words as well. It seems to resonate with Abel, who glides towards me in an attempted embrace before slipping on the wet ground. I catch him, dropping my shirt. His pale blue eyes stare into my heart, he embraces me. He’s warm. I wrap my arms around his back, just as he does to me. I embrace his warmth, and we stay like this for a few minutes.
\newline
\tab
``Besides, without these scars, I wouldn’t have run away and found you. What would you do without me? You’re a mental disaster!''
\newline
\tab
Our laughter dies off just as the water finishes boiling. He shows me how to clean the vegetables and prepare a surprisingly complicated breakfast. We walk out and serve the food as usual in my room. The smell seems to attract Emma, whose entrance is followed by Connor. They sit down in the same places as usual. Just before Emma starts eating, she stares at me quizzically. ``Why is your shirt off?'' I smile at Abel, who blushes and avoids my gaze.
\newline
\tab
``Don’t worry about it.'' I respond. She grins devilishly, while staring at Abel.
\chapter{Storyteller}
\tab
``You’re happy here, right?'' I ask one morning. Abel and I are gathering crops from the garden.
\newline
\tab
He smiles at me. ``Come on, once we bring these in, I want to take you somewhere.'' He dodges the question. I smile eagerly wondering where he’s going to take me, yet in the back of my mind I wonder why he didn’t answer. ``We’re going to have to switch the garden soon. It’s spring now.'' We grab the rest of the vegetables and take them into the kitchen.
\newline
\tab
``So, where are you taking me.'' I ask. He smiles and tells me to follow him. We walk into that forest Connor collects water from. It’s much livelier and more vibrant than the clutter of white-grey staleness it used to look like. There’s greenery everywhere, the foliage has grown back just enough that the sunlight is much more plentiful than what I’d imagine it to be like in the summer. The forest is practically glowing; as well as Abel. He takes me across the river that Connor presumably gets water from. ``We’ve been walking for a while, are you seriously not going to tell me?''
\newline
\tab
``Don’t worry, we’ll be there soon.'' He replies eagerly. After a few more minutes, he stops walking. ``Here we are!''
\newline
\tab
``A flowerbed?'' I question. There are red and yellow flowers centre of the forest. In the distant background, Abel tells me there are orchids, though I don’t know the difference between those and anything else here aside from their smell resembling that of a corpse. It looks beautiful but I wonder why he brought me here. Does he want to pick flowers?
\newline
\tab
He grins at me devilishly before tackling me to the ground. He climbs onto my chest and smiles at me. ``Isn’t this place great? I love coming here!''
\newline
\tab
I smile back at him in agreement, roll over, place my head on his chest, and close my eyes. ``It really is.'' I mutter.
\newline
\tab
``You’re not even looking!'' He whines. His arms slowly wrap themselves around me and we stay like this for a while. No words pass between us, yet for the first time in my life, the silence is calming, and I genuinely enjoy it. I never want this to end.  ``You fell asleep!'' He says accusingly, slightly whispering just in case I was actually asleep -- how considerate!
\newline
\tab
``Never.'' I reply grinning. I don’t think I’ve ever spent so much time smiling before this... before him.  ``Thank you.'' I whisper in a tone I assume only I can hear.  
\newline
\tab
``For what? We haven’t done anything.'' He replies clearly confused at something he wasn’t meant to hear. I can feel my face start to heat up.
\newline
\tab
I whine, not knowing how to respond to him. He pats my head with his left hand. ``Don’t worry.'' He says vaguely between laughter. ``Let’s stay here for a while.'' He says calmly and confidently. I nod, moving my arms to a more comfortable position and unintentionally tickling him in the process and causing him to burst out laughing. He rolls over and starts tickling my sides from on top of me. I never want him to leave.
\newline
\tab
After we settle down, he places his head on my chest and asks me something I’m not entirely sure how to answer. ``How do your miracles work?''
\newline
\tab
I think about it, contemplatively stroking his head. ``It’s kind of hard to explain,'' I start, ``I sort of just envision the end result, then get emotional -- I think that’s the right word -- and then something happens, and everything just sort of progresses towards that ending. It’s not really explainable, I’m not really the one in control of the process.''
\newline
\tab
He snickers. ``Wow, that’s so much more confusing than mine.'' He’s practically radiating happiness. A nice cold and bright blue engulfs us both.
\newline
\tab
``You know, you still haven’t answered my question.''
\newline
\tab
``Hmm?''
\newline
\tab
``Are you happy? Here, with the way things are now, are you happy?''
\newline
\tab
``Do I \textit{really} need to answer that?'' He retorts, ``I brought you here to a bed of flowers. We’ve been lying here smiling practically forever. Of course I’m happy! Isn’t it obvious?''
\newline
\tab
``Speaking of being here, Emma’s going to starve to death isn’t she… We should probably head back now.'' I killed the mood with those two sentences. All good things must come to an end; though they don’t necessarily have to end on a bad note. Something takes over my body, it’s too familiar for it to be a product of rain. It almost feels like it could be my subconscious or some form of instinct. I gently pull his face towards mine and place my lips against his.  After a couple seconds, I pull my face away. His face is a bright crimson; mine probably is as well. We walk back to our home in a blissful silence.
\newline
\newline
\tab
``Where’d you two go?'' Emma asks with a devilish smirk on her face.
\newline
\tab
``What, you hungry?'' Abel retorts with the same level of playfully evil familiarity in his voice. 
\newline
\tab
Connor jumps into the conversation -- if I can call it that -- sooner than I expected. ``No, she isn.t I fed her.'' Such a responsible person. ``We were betting on how long you two would be gone for.'' Okay maybe not as responsible as I thought.
\newline
\tab
``Oh?'' I reply, ``Who won?'' I wonder what they thought we’d be doing. Did Abel tell them about this beforehand? I glance at him, but he doesn’t seem to notice. He’s just smiling away, standing beside me.
\newline
\tab
``Who do you think?'' Connor replies. Given Emma’s current cheerfulness, I’d say Connor lost. That being said, he doesn’t seem overly upset by it. 
\newline
\tab
``What were the stakes?'' I ask.
\newline
\tab
``Half of dinner.'' He replies in such a nonchalant and smug way that I wonder about the trick he’s going to pull. Emma grins. Connor discretely points to the kitchen, while Emma happily sits herself down in another room. Abel and I make our way into the kitchen. There’s a covered pot with some sort of pink squishy-looking smooth object bathed in ice water. Connor appears suddenly behind us. ``I caught a rabbit while you two had your alone time. Dinner’s gonna be bigger than usual.'' He sounds prideful.
\newline
\tab
I stare at the rabbit meat, knowing I probably won’t need to eat it. ``I wonder if I’ll taste anything. Probably not.''
\newline
\tab
Connor pipes back in. ``If you don’t want to eat it, I’ll gladly take it.''
\newline
\tab
``So that was your trick! That’s why you made the bet.'' I reply. He may not be entirely responsible but at least he’s smart.
\newline
\tab
``No, I was actually planning on giving her the vegetable half of my dinner. Your idea probably works better though.''
\newline
\tab
``We’ll see how things go. Who knows, you might get lucky.''
\newline
\tab
``So, what do we do now?'' Abel asks.
\newline
\tab
``Wanna hear a story?'' Connor asks.
\newline
\tab
Abel and I nod and smile in agreement. Emma peeks her head in and waves for us to walk into the other room. She whispers something into Connor’s ear -- or fails to, because she’s completely audible -- ``What story are you going to tell them?''
\newline
\tab
``Probably the one about the Wetiko.'' He replies.
\newline
\tab
``What? Really? That gave us nightmares last time we heard it. Do you even remember it that well?'' She sounds doubtful. 
\newline
\tab
``It’s a story. I don’t have to remember anything. Besides, we were little when they told it to us. It was meant to stop us from going into the forest -- and think about how well that went.'' He replies straightforwardly and dryly.
\newline
\tab
``I guess. Alright then.'' Emma replies cheerfully. 
\newline
\tab
``Alright then. Let’s begin. There once was a farmer who lived in a village. The farmer was well-liked by those in the village, though he was known for his short temper and paranoia. Many people tried to keep conversations with him to a minimum, which he enjoyed very much. For you see, the farmer rather disliked the people in the village.
\newline
\tab 
``All they would do is come to him for food, talking only as a facade to achieve their goal. Nobody bothered to have a genuine conversation with him. He knew that nobody wanted to have a genuine conversation with him, so he never expected anyone to come without wanting food. That’s why he was always angry with the villagers.''
\newline
\tab
Emma interjects. ``Wait so if he never expected a genuine conversation, why would he be angry with them?''
\newline
\tab
Connor sighs. ``Do \textit{you} want to tell the story then?'' His voice clearly filled with annoyance.
\newline
\tab
Emma grins. ``Fine by me!'' Connor sits in annoyed silence while Emma continues. ``He yearns for a genuine conversation with someone yet believes anyone coming to him only wants food. One day, a young maiden walks up to the farmer.
\newline
\tab
``The farmer stares at her with a reluctancy in his eyes and asks the maiden what she wants. She replies kindly, saying she wants a conversation. The farmer, clearly angered by her taunt, tells her to leave. The maiden smiles, turns around, and does as instructed.
\newline
\tab
``The next day, the maiden comes back and asks again for a conversation. The farmer tells her to leave, which she does, only to return the next day. The farmer, now greatly annoyed by her existence, decides that the best way to get her to stop was to entertain her for one conversation. So, they talk and talk and spend the whole day talking. Every day, at the same time, the maiden would come, and they would spend the rest of the day talking.
\newline
\tab
``Unfortunately, these daily conversations would start to impede on his work time. People would come to him and ask for crops, but he would never have enough for them anymore. So eventually, when the village became significantly annoyed at his lack of work, they forced him into a forest just outside the village border and a new farmer was selected to take his place. The farmer is left to wander throughout the forest without any food. He wanders for two days on end without finding anything to eat.
\newline
\tab
``Dragging his feet through the forest, so very hungry and thirsty, he hears a thought in the back of his mind. \textit{Eat me. I will heal you.} His gaze darts towards a plump, black fruit. He makes his way over, takes a bite of it, and begins to fell rejuvenated. With an increasing hunger, he searches the forest for more black fruits, devouring all he could find. One day, while scavenging for fruit, he comes across a deer. He sees something in that deer that he had never seen in any other animal before. The deer started running away, and he ran after it. He was surprised to know that he was significantly faster than it. He caught up to the deer in no time and promptly sank his teeth into it’s neck, ripping off it’s head and relishing in the buffet that stands before him.
\newline
\tab
``He happily devours the great corpse of food with no hesitation whatsoever. After that feast, he grabs the head of the deer from the ground and stares into its eyes. He felt so proud of his kill that he decided to keep the head as a mask, and promptly voids it of its contents before placing it atop his head. At first it felt awkward, but in time he got used to it. And so, his search for the black fruit continued.
\newline
\tab
``Now, he left that maiden all alone, with nobody to talk to. She decides one day to go look for him. She enters the forest and starts wandering, hoping to find her farmer. After eating another one of those black fruits, he smells something new, something he hadn’t smelt in a long time. Something that smells delicious. So, as anyone would do in that situation, he chases after the smell.
\newline
\tab
``Before the maiden stands a lanky, tall, rotten corpse with the head of a deer. She stares at the monster in horror. Its grey ribcage is plainly visible with no organs inside. Bits of rotting flesh drape around its chest. Its nails are long, curved and black, and look ten times as thick as regular nails. He stares back at the maiden in disbelief, how could such a delicious meal not be eaten? The mouth of the deer opens, he picks up the maiden, placing her head inside his mouth and decapitates her. As he relishes in the vibrant and delicious tastes of the maiden’s head, the body drops to the ground eagerly awaiting his next bite.  The maiden never returned home to the village. Many people went into the forest to search for her, only one came back. That one described the fierce monster to the villagers. After some time, he started being referred to as the Wetiko. \textit{The cannibal demon of the forest.}''
\newline
\tab
I find my arms wrapped around Abel and wonder how Emma came to know such a disturbing story. Connor thoughtfully comments on the adaptation of the story he was originally going to tell. ``That’s where you went with it? I was going to -- ''
\newline
\tab
``I know,'' Emma interrupts, ``You were going to have the farmer kill the Wetiko and be the \textit{brave hero}, right?'' He sighs and nods. ``Did you ever stop to think about where the Wetiko came from? These things are important! That’s why I’m so much better at storytelling than you.''
\newline
\tab
Connor replies disappointedly. ``Alright, alright. I get it. I don’t think we were ever told about how the Wetiko was created though. Where did you hear that from?''
\newline
\tab
Emma grins.  ``I made it up as I went. The best stories are improvised.'' She states confidently. There’s a look in Connor’s eyes of what I’m guessing is doubt. 
\newline
\tab
Connor gets up. ``We should probably start making dinner now.'' Abel and I follow him into the kitchen. He lights the oven. Connor grabs the vegetables and passes us each a third along with a knife. ``Chop up the vegetables into thin slices.'' He says.
\newline
\tab
``Which one of us has been cooking for most of the time?'' Abel retorts. He mutters something under his breath along the lines of ``I know how to cook.'' I stare at him playfully, which seems to cheer him up a bit. I watch Abel and Connor -- well mostly Abel -- and try to understand how they chop the vegetables so finely.
\newline
\tab
``Here, let me help.'' Abel says, suddenly behind me. He grabs my right hand, placing the knife just barely above the edge of the scallion while placing my other hand around the middle of the vegetable, holding it down firmly. Slowly, he pushes my right hand down, slicing very thin pieces. After he guides me through the first vegetable, he lets go of me and returns to chopping his own section. A chill of loneliness runs through my spine as I lose Abel’s heat from my body.
\newline
\tab
``Thanks.'' I say with a mild sadness and want for another embrace. I continue to chop the vegetables I was given. The chopped vegetables get progressively thinner with time.
\newline
\tab
``The rabbit should be boiling now.'' Connor opens the lid to the pot, dumps all the vegetables in and places the lid back on, carefully making sure that there’s an open section.
\newline
\tab
``How long do we wait?'' I ask, curious as to how much time I’ll spend watching them engulfed in hunger.
\newline
\tab
``You getting hungry?'' Abel asks jokingly, ``give it fifteen minutes.'' We sit in silence, watching Connor flip his semi-existent coin. Abel gets up a few times to check on the food. He comes back around the third or fourth time saying it’s ready. We sit at the table in our usual arrangement and gulp down the stew we made. Emma grins wickedly at Connor, who meets her gaze with that same level of smugness I saw earlier. No words pass between them. I eat half my food before passing it to Connor, who then passes it to Emma. She happily accepts more food and devours it in seconds. Abel stares out the window. ``I want to climb that mountain at some point.'' He says contemplatively, making it sound more of like a thought experiment than a challenge.
\newline
\tab
``What mountain?'' I ask, confused as to where he’s looking. ``I haven’t seen any mountains anywhere close by.''
\newline
\tab
``That one,'' he points, ``With the twin peaks.'' I look out the window and see two distant grey triangular peaks.
\newline
\tab
``I’ve never seen that before.'' I say in shock.
\newline
\tab
``The winter snow lessens the distance you can see.'' Connor says. ``It’s not surprising that you wouldn’t have seen it before, you came from the south right?'' I nod.
\newline
\tab
I look back at Abel. ``Let’s go together!'' I say, failing to hide my excitement so poorly I almost jump out of my seat.
\newline
\tab
``Yeah,'' he says, ``I’d like that.''
\chapter{Anew}
\tab
It’s night. As usual, I’m still awake. I spend some time staring out the window at the mountain Abel had pointed out. I wonder why he wants to climb it, though I doubt it’s worth asking him. Two massive peaks showered in grey and erected seemingly from nowhere, standing so tall they almost touch the stars. It looks like it would take a week to get to the base of the mountain from here. It’s so silent here, it’s almost unnerving, knowing I’m the only person currently awake. The perfect setting for a nightmare.
\newline
\tab
Abel gets up and walks towards me. ``You’re still awake?'' He asks, mildly surprised.
\newline
\tab
``I typically don’t try to sleep until I run out of thoughts.'' I respond, turning around to look at him.
\newline
\tab
``Run out of thoughts? Is that even possible?''
\newline
\tab
``Well, run out of the good ones. Did I wake you?''
\newline
\tab
``No, don’t worry about it. Wanna go for a walk?''
\newline
\tab
``Sure.'' And with that, we find ourselves outside under the twilight moon with a lantern of Abel’s stardust guiding our path.
\newline
\tab
``You know, my stardust wasn’t always hot. Now, even with such a small number, I can still feel a decent amount of heat.'' He sounds kind of saddened it.
\newline
\tab
``It’s keeping us warm though, right? Besides, it could just be an age thing. As you grow older, your stardust gets hotter.''
\newline
\tab
``Are you calling me old? Aren’t we around the same age?''
\newline
\tab
``Probably; I was never told how old I was. I wonder how hot it’ll be when we grow up?'' We walk parallel to the forest, and eventually settle down a fair way from our home. We lie down and stare up at the night sky, cluttered with stars. We spend the time talking about nothing in particular -- sometimes talks like that are good to have, where emotion isn’t required. We talk about what vegetables to grow in the summer, how he learned to cook, and other parts of our lives that remain relatively mundane.
\newline
\tab
Suddenly, we see two people sprint into the forest from the direction of our home. ``Who's that?'' Abel asks, quickly rising from beside me.
\newline
\tab
``We should go back and see if Connor and Emma are okay -- or if that was them.'' I say. He nods and we run back. ``Did you get a close look at who those people were?''
\newline
\tab
``No, I’m worried.'' We get back to the house, Connor and Emma aren’t there. Out of nowhere, a new voice appears.
\newline
\tab
``There you are Abel. Let’s go home, after we get rid of him!'' His eyes are void of colour, though the stale, rotten orange around him clearly makes up for it. There’s something missing from him that terrifies me. It’s something I’ve never seen absent in anyone before. I want him as far away from me as possible.
\newline
\tab
``Aiden?'' Abel asks, a dark red outline slowly engulfing him. ``What are you doing here?''
\newline
\tab
``You remember me! I waited for you to return after all this time, but you never did. When the town said you’d been captured by others, I offered to kill them and bring you back. A couple others came with me as well, though I’m not sure what happened to them. I think I lost them along the way.'' From his sleeve, he pulls out a shortsword, accidentally cutting himself. He doesn’t seem to notice. Blood drips from his arm without any sort of reaction. Can he not feel it?
\newline
\tab
``Aiden, don’t!'' Abel shouts. ``I wasn’t captured! I ran away!''
\newline
\tab
``No! No! NO! No, you didn’t! You were captured! I know it! Stop lying to me!'' He lunges towards me, weapon extended. I’m frozen. I don’t know what to do. There’s nothing for me to do. Suddenly, Abel appears before me, smiling. I watch as the now red shortsword shoots out of his stomach, and blood from his mouth. ``Run,'' he says weakly,  ``I’ll deal with him.''
\newline
\tab
``No! Please! Don’t leave me!'' I cry. Why did this happen to him? I was supposed to die, wasn’t I? Why did he take my place? Why do people keep taking my place?
\newline
\tab
``RUN!'' He screams at me. I stare at Aiden in anger, who still hasn’t moved, petrified by what he’s done. ``Don’t worry about me. I’ll take him with me.'' He smiles, ``You were slightly off --'' Blood pours from his mouth, his breathing becomes more laboured. He’s not going to survive. ``Thank you. You made me so happy. Now please, run away. I don’t want all of us to die. Live; for me.''
\newline
\tab
I lean forward and place my lips on his. ``I’m sorry,'' I cry. He can’t speak. His lips move slowly into a smile and soundlessly say ``Don’t be.'' I run as far away from the house as possible. I run towards the mountains, hoping he’ll come chasing after me, but I know he’s not coming out of our home, and that my hopes are meaningless. Tears flow from my eyes again. Without warning, a massive ball of bright yellow engulfs the house, setting everything ablaze.
\newline
\tab
I finally understand. He was a star, now slowly disappearing. I know the person who stabbed him couldn’t have survived that. I watch as my closest friend slowly disappears from this world, until there’s nothing left. A dead star lost forever. I fall to my knees crying. He was the only one who truly understood me, and now he’s gone forever. All of them are; they’re all gone. I am alone. I don’t know my way well enough in the forest to not get lost. Even if it was Emma and Connor who ran into it, chances are I’d never find them. They wouldn’t know to look for me either. Getting lost in there wouldn’t do any good, and it might not even have been them anyway. I pray they remain alive and weren’t killed by those people. For the first time, no matter how hard I wish, nothing happens. No glow, no rain, nothing. There’s nothing left for me to do but pray. I still have hope.
\newline
$\prec$Please!$\succ$
\newline
\tab
A sudden drowsiness takes over my body. Unable to fight it, I collapse to the ground.
\newline
\tab
When I wake up the next morning, I stare in the direction of the house. Charred remnants are all that remain. I remember Abel’s wish to climb the mountain. Tears stream from my eyes when I recall how happy he was when I said I’d come with him. We were so happy, why did it have to end? With tear-blurred vision, I start walking towards the mountain.
\newline
\newline
\tab
We manage to escape into the forest before those people could capture us. I turn to Connor, ``Who were they? Who were those people?''
\newline
\tab
He looks extremely paranoid. ``I don’t know. I wonder if Abel and Nabu are alright.''
\newline
\tab
``Do... do you think they caused it?'' I ask, concerned. It’s not out of the realm of possibilities, right?
\newline
\tab
``No, neither of them would’ve wanted to go back to where they came from. These were real people, there’s no way this was planned by either of them, nor would this be something Nabu could create.'' His voice is shaky and I doubt he believes what he just said. None of us know the actual extent of Nabu’s abilities, though I don’t think he’d actually do something like that.
\newline
\tab
``There are night birds, mostly owls and nighthawks, out right now. I’ll try to get them to see if they can find Abel and Nabu.'' I try to cheer him up with confidence, but he only nods, looking at me without any hint of cheerfulness. In those eyes, there’s only fear and concern. I ask the birds to look outside the forest in the language taught to me as a child, trying to get them to find anyone looking similar to us.
\newline
\bird{We will not leave!}\bird{We will not leave!}\bird{Will not leave!}\bird{Will not leave}\bird{Not leave}\bird{Not Leave!}\bird{No!}
\newline
\tab
I look back at Connor in horror, his eyes always calm me down, especially in situations like these. ``They won’t leave.'' I say, ``They won’t leave the forest.''
\newline
\tab
``Why?''
\newline
\tab
``I don’t know. They just don’t want to leave.''
\newline
\tab
``What do we do?'' he asks, unnaturally indecisive.
\newline
\tab
``We stay in the forest, it’s probably the safest place to be right now.'' I reply, some things are finally starting to make sense, Connor’s powers weren’t limited to that coin. ``Show me your coin.'' 
\newline
\tab
``Why?'' He asks.
\newline
\tab
``Do it.'' He pulls out the coin from nowhere, I can see its reflection in his eyes. ``Good, now look at it.''
\newline
\tab
``I am.'' He says, confused as to what I’m trying to do.
\newline
\tab
``No; look at your eyes. Use the coin as a mirror.'' He looks at me slightly surprised.
\newline
\tab
``You figured it out? I never told --''
\newline
\tab
``I know you didn’t. Just do it.'' He does as he’s told and the coin cracks. It works, except there’s now a jagged fracture on the coin’s head. ``You’re good now, right?''
\newline
\tab
``Yeah.'' His voice is much calmer now. I’m relieved. ``For the time being, we should sleep.'' We lie down on the ground and close our eyes. I doze off almost instantly.
\newline
\newline
\tab
I snap my eyes open. I don’t think I was meant to use the coin like that. My calmness ability shouldn’t have been used on myself. Something’s wrong. I get up, unable to sleep, and keep watch just in case anyone or anything comes near us. It’s a quiet night, and I spend most of the time staring up into the night sky, wondering as to who those people are. Dusk turns to dawn sooner than I expected, and I wake Emma, knowing it probably isn’t best to stay in the same place for a long time.
\newline
\newline
\tab
Connor wakes up before me. ``Did you sleep well?'' I ask, not feeling as rested as I’d like to be.
\newline
\tab
``Yeah,'' He replies with a surprising calmness to his voice. ``You?''
\newline
\tab
``I wish,'' I say grumbling. ``It felt like I was sleeping on a bed of jagged rocks.'' I get up and wipe the dirt off my clothes.
\newline
\tab
``What do we do now?'' He asks.
\newline
\tab
``I don’t know. I’ll try and get the birds to guide us to some food. The morning birds are always the nicest.''
\newline
\tab
``That seems like a good idea.''
\newline
\tab
I ask the birds to guide us to food. A couple of them bring us to a small berry bush that they assure is edible. They tell me that there isn’t much food in the forest and that we shouldn’t eat too much because we’ll destroy their habitat. We eat a few berries as I pass the information to Connor. ``We should leave the forest and find somewhere else.'' I say, he nods in agreement with me.
\newline
\tab
``The only problem with that is we’re lost.'' He says, surprisingly unenthusiastically.
\newline
\tab
``I’ll get one of the birds to show us to the exit.''
\newline
\bird{No!}\bird{Don't go!}\bird{Not safe!}\bird{Stay in forest!}
\newline
\tab
There’s nothing I can say to convince them to show us the way out, we continue walking, hoping that we’ll eventually find an exit. The forest is only a finite space, right?
\newline
\tab
Two more days pass, both of us are starving and the birds don’t let us leave, nor do they guide us to any more food. They’re only reasoning for keeping us here is because ``it’s not safe'' outside the forest. It angers me, but there’s no point in fighting. Once again, I ask them for food.
\newline
\bird{You can eat him!}\bird{Eat him!}\bird{We won't steal!}\bird{He's all yours}
\newline
``You know, that’s not a bad idea.'' Connor replies calmly, suddenly understanding the language of the birds.
\newline
\tab
``What are you talking about\textinterrobang Yes, it is! How did you even understand that?'' I scream at him in anger and disbelief for even considering such a solution.
\newline
\tab
``I just guessed. They sounded happier, or less angry. I assumed it was either \textit{eat him} or \textit{eat each other}.'' His calmness is starting to scare me. What happened to him?
\newline
\tab
Hunger overwhelms me and my stomach growls, yet the thought of eating Connor removes my appetite. ``Why would you even consider that\textinterrobang'' I yell at him.
\newline
\tab
``Do you have food?'' He asks. There’s a lack of passion in his voice, as if casually asking someone for a snack when you’re not even hungry. ``Exactly. It’s okay, you can eat me. I want you to live Emma. You can live for both of us.''
\newline
\tab
``Then what\textinterrobang'' I yell, tears streaming from my eyes. ``I eat you and that erases my hunger for a day, then I die trying to find the exit!''
\newline
\tab
``We’ve walked in the same direction for two days straight. You’ll make it, it’s okay. Trust me.''
\newline
\newline
\tab
I try to calm Emma down by holding eye contact with her, but it doesn’t seem to work. It may have something to do with the crack on the head of my coin. Emma starts at my leg. It’s incredibly painful but communicating my pain in any way would probably make her stop. Instead, I just sit here silently while she rips off a piece of my leg with her teeth, ripping out a surprisingly significant chunk of flesh and muscle. When blood sprays everywhere she starts freaking out and asking if I’m okay. ``I’m fine,'' I say, smiling. ``Enjoy your meal.'' She looks incredibly guilty but continues to devour me. Bite by bite I became lighter and lighter as she continues to eat me. I can feel my vision start to blur and my mind starts to go blank. I smile at her one last time. ``Goodbye Emma,'' I say. She doesn’t seem to notice or hear me. I fall asleep for the last time, never to wake up again.
\newline
\newline
\tab
I continue eating the corpse. It took him a while to die. With every bite, I become more and more calm, finally understanding what his last moments were like; blissful calmness. I lie back after finishing my buffet. This place will make a great new home. The birds are nice, the place is quiet, and there’s plenty of food! I fall asleep, basking in the noon sun peacefully and satisfied. ``That was a good meal.'' I say to nobody in particular.
\newline
\tab
I wake up during the night. The owls tell me I’ve changed. I laugh. One of them tells me that there’s this annoying eagle that keeps destroying parts of his nest during the day while he sleeps. ``Take me to him. I’ll get rid of him for you,'' I say happily. Eager to get a new meal, I follow the owl to the eagle’s nest. The owl tells me that we’ll need to knock the eagle down to the ground. ``Don’t worry about it.'' I say happily, reaching up and grabbing the eagle by its neck. It wakes up, startled by my hand and starts pecking at me. I giggle, and it freezes in shock.
\newline
\bird{You changed!}
\newline
\tab
I devour it in two bites, then smile at the owl. What a wonderful place this is. Smiling up into the air, I think to myself; \textit{things are always better when improvised}.
\chapter{Reminiscent}
\tab
I miss them. I miss the time we spent together. I miss the stories, the meals, the sleep. There’s none of that anymore. They’re gone. I continue walking towards the mountain with the twin peaks. I’ll climb it for both of us. The scenery around me is beautiful, but I try not to look at it. I lost the most beautiful thing ever; nothing can compare to them -- to him. The thought of them brings tears to my eyes once again. It’s not worth wiping them away when more will come to fill its place. I’ve cried enough in my life. Just when I thought I’d stop needing to cry...
\newline
\tab
I don’t need sleep, or food. All I do is walk closer to that mountain. All I have left to do is climb that mountain. I don’t take breaks to rest, or to eat, all I do is walk. The world around me is grey. There’s nobody hear to colour anything for me. All that remains are my monochromatic failures manifesting as reality. I’m not even conscious of my walking anymore. There’s thunder.
\newline
\tab
Thunder and lightning fills the skies, but if there’s rain I don’t notice it. It reminds me of a story Emma once told us. I smile and decide to retell the story. I hear Emma’s voice in my head. ``I made it up as I went. The best stories are improvised.'' Every thought of them brings more tears that I’m unable to wipe. I decide to retell the story of the thunderbird.
\newline
\tab
``Long, long ago, there was a star. This star was massive and attracted all sorts of objects around it. As time passed, the dust orbiting the star would clump together, forming bigger and bigger rocks in the orbit. The more time passed, the more dirt would accumulate, and the rocks would get bigger and more spherical. --''
\newline
\tab
The feeling of rain consumes me once again. There’s nothing but a vast expanse of paradoxes and contradictions. Something catches my mind’s eye. There’s a boy -- or a silhouette of a boy -- sitting down and patiently listening. He raises his hand at me, as if telling me to continue my story. A voice -- my voice -- appears again from everywhere at once. ``You’ve never told a story before. Entertain us.'' And just like that, I’m brought back to my body and continue walking. The story progresses.
\newline
\tab
``There’s something special about this star. Within its core resides a phoenix. The phoenix lives a sad life. It lives to heat the sun, lays an egg, dies, and its child continues the process. This phoenix had thought about its lineage and decided that it didn’t want this life for its children. The phoenix realized that if it dies without children to continue its legacy, the sun won’t survive. For the first time throughout its family history, the phoenix lays two eggs. One of which is sent to one of the orbiting rocks, whilst the other becomes a meal for the phoenix, renewing its life.
\newline
\tab
``For the phoenix, the cycle continues. As long as there remains offspring on that rock, it will continue to rejuvenate its life by eating potential children. The child it sent to the rock hatched. The different environment took a toll on the egg, and as a result, the child was different. Instead of the normal vibrant yellow of the sun, its feathers and body were a deep, saturated blue. Angered by this difference, the child went to seek the phoenix, flying back to the sun enraged and furious.
\newline
\tab
``\bird{What is this? What did you do?} It asks, anger seething from its words.
\newline
\tab
``\bird{I only saved you from the loneliness of being trapped in this prison.} The phoenix responds to its child with compassion and confidence.
\newline
\tab
``\bird{You stole my destiny from me!}The child spits at its parent. 
\newline
\tab
``\bird{Look at what you created. Your destiny lies elsewhere.}The phoenix responds, motioning to the rock which its child flew from. \bird{With the flap of your wings, you brought water to that world.}
\newline
\tab
``\bird{I was meant to be a phoenix!}The child screams, unaccepting of its life.
\newline
\tab
``\bird{If you were meant to be a phoenix, why are you the blue that colours that world instead of the yellow that colours this sun?}The child, infuriated, flies back to the world it created. From its wings came water, which covered the desolate ground. From the water came plants, engulfing chunks of land in luscious greenery. From these plants came animals, and from animals came people. 
\newline
\tab
``The child looked back on its creation with contempt at what came to be. From the top of a mountain, it laid an egg, knowing its child would follow its path rather than that of the phoenix. Whilst caring for the egg, the child realized that it cannot be called a phoenix. So, it flies down to ask the people what it should be called.
\newline
\tab
``\bird{I’m am the one that brought you life, yet I am not the phoenix. I have no name. What would you call me?}The child asks to the people. The people look at the bird with great confusion, causing it to realize that they do not share a common language. The people offer it a young boy, which the child takes ang begins to raise as its own.
\newline
\tab
``Once the boy had spent a significant time with the bird, the phoenix child asked the boy for a name. \bird{What would you call me? I am not the phoenix. I have yet to be gifted a name. What would you name me?}
\newline
\tab
``The boy replies in the language of the birds, \bird{When you flap your wings, it makes noise like thunder. You are the thunderbird.}The boy says enthusiastically.
\newline
\tab
``Overjoyed with its new name, the thunderbird flew to the phoenix. \bird{The people gave me a name! I am the thunderbird!}it says excitedly.
\newline
\tab
``\bird{What a wonderful name.}The phoenix replies. \bird{But what of your child? Are they not hatched yet?}
\newline
\tab
``The thunderbird rushes back to the mountain in panic to check on its egg. The egg had been desecrated and destroyed by humanity. Enraged, the thunderbird screamed, and from the skies came lightning to smite the people. The thunderbird flew far away from humanity, residing on a mountain overlooking the entire world. There, it laid a new egg, and carefully watched over it this time to make sure humanity didn’t come to destroy it again.
\newline
\tab
``When the egg hatches, the child comes out in confusion. It looks at its parent and asks, \bird{What am I? Am I not a phoenix?}
``\bird{You are a thunderbird.}''
\newline
\tab
I wait for the rain to take over, to see that boy again, but it never comes. Nobody got to hear my first story. Something in the world changes. Colour comes back and everything turns a shade of sickly yellow. An old voice returns. ``It’s you! That child, it’s you!'' A monk from the ziggurat greets me with fear and disbelief.
\newline
\tab
Why would a monk be all the way out here? What could he possibly be doing? ``Was it you? Was it you who sent those people to kill my family\textinterrobang'' I scream at him. ``You took everything from me! You took the only people I cared about from me! You killed them!''
\newline
\tab
``I’m sorry! I didn’t -- please don’t hurt me!'' The monk backs away into a world of disgusting yellow.
\newline
\tab
``How dare you!'' I scream. My entire body engulfed in a crimson that bleeds into the world. ``How dare you take them from me!'' The world around me shatters. Nothingness begins to engulf the planet, getting larger and larger.''
\newline
\tab
``I didn’t do it!'' The monk screams. I stop, slowly descending into the remains of deleted land. I continue walking towards the mountain.
\newline
\tab
``Run.'' He does as he’s told, and the world’s saturation runs with him. I am returned to monochromia. 
\newline
\tab
I’m glad I didn’t kill that monk or didn’t have to. Enough people have died in my life, I don’t need more people from my past to disappear. I wish I could’ve talked to him. I wish I could let go of my anger for once. I wish for my crimson to become purple again, like before. I wish I was with Abel.
\newline
\tab
Part of me wonders why he was all the way out here. It probably would’ve taken a month to walk all the way here. I begin to wonder what’s changed at the ziggurat after I killed my father and ran away. Come to think of it, I don’t even remember my father’s name. It’s been so long since I’ve been there, I wonder if they would be more accepting of me. Maybe in another world, I’d go back. People wouldn’t look at me with disgust, I’d find friends, and eventually build a family. Maybe in the world where I didn’t run away.
\newline
\tab
I think it’s started snowing, or raining. It’s hard to tell the difference when you care so little for the world around you. I don’t feel anything. It reminds me of something Connor told me. ``The winter snow lessens the distance you can see.'' Was it really that long ago? A full year, gone by in a matter of days. I wish it could’ve been longer. I wish I could’ve spent more time with them.
\newline
\tab
To my right, there’s a town. Somebody seems to notice me, and they approach quickly, bringing colour into my world. Monochromia is replaced with saturated, bright, shining yellow.  ``We’re looking for a kid, around your age. He’s slightly shorter than you and has chestnut-coloured har. Have you seen him?''
\newline
\tab
Another voice comes from behind the man. ``Wait! That’s one of the kids that captured him!'' He screams.
\newline
\tab
``Captured?'' I reply, confused. After a moment, I understand. This was Abel’s town. ``He was happy. We were all happy.'' I begin to realize that purple could only be brought out by him. They were the exceptions. Humanity is evil by nature. ``You took them away from me. You took him away from me.''
\newline
\tab
``What are you talking about? You’re the ones that captured him!'' They yell at me in anger. Crimson bathes my sight, though I’m not sure whose it is.
\newline
\tab
``HE RAN AWAY BECAUSE OF YOU! WE MADE HIM HAPPY! THEN YOU TOOK HIM FROM ME! YOU TOOK THEM ALL FROM ME!'' This is definitely my crimson. I can feel my anger breathing through the universe. 
\newline
$\prec$SUFFER$\succ$$\prec$SUFFER$\succ$$\prec$DIE$\succ$$\prec$DIE$\succ$$\prec$DIE$\succ$
\newline
$\prec$REND$\succ$$\prec$REND$\succ$$\prec$DIE$\succ$$\prec$REND$\succ$$\prec$DIE$\succ$
\newline
$\prec$DIE$\succ$$\prec$REND$\succ$$\prec$DIE$\succ$$\prec$REND$\succ$$\prec$DIE$\succ$
\newline
\tab\tab$\prec$DECEASE$\succ$
\newline
The universe breaths deletion through me. Pralaya engulfs them along with the rest of the town. I delete the part of the world that took him from me. Nothing remains. No sign of life to be found anywhere. They took everything from me, so I took everything from them. I’ve been interrupted too many times now. Just as I start to continue walking, I realize I’m standing in a bed of flowers. Of all things to survive; a flowerbed. I lie down, hoping Abel will come out of nowhere and place his head on my chest. I want to feel his hair through my fingers once more. Just one more time.
\newline
$\prec$Please$\succ$
\newline
\tab
Just as I expected, nothing happens. He doesn’t appear. His head doesn’t lie comfortably on my chest. His hair doesn’t move gently through my fingers. His lips don’t meet mine. I scream, tears flowing from my eyes. There’s nobody to hear my suffering. I spend the rest of the night lying in the bed of flowers.
\newline
\tab
I bathe alone in the glow of stars, just like we had that night. I wish I could’ve saved him. I wish we could still be together. Even with my miracles, I know I can’t restore life to a corpse -- of which there isn’t one anyway.  I couldn’t even bury him. There was nothing left. I wish... Just one last time... please.
\newline
\tab
The next morning, I get up from the flowerbed and continue walking towards the mountain. There’s no home for either of us anymore. There’s nothing here. It’s within reach of a day’s walk. That being said, I’ve lost count of how many days I’ve been walking in monochromia. I’ve been all alone for such a long time.
\newline
\tab
I finally make it to the base of the mountain. ``We’re here.'' I say smiling with tears pouring into my mouth. There’s nobody to hear my words, but even so, I hope he’s listening. ``The last stretch is just ahead.'' 
\chapter{Soon}
\tab
I begin climbing the mountain. It’s much steeper than I anticipated. I begin to wonder why Abel wanted to climb this thing. I miss him. Tears flow from my eyes and I scream. A deep crimson engulfs my vision, and when I calm down, there’s a massive hole blown into the side of the mountain; not anything too deep, but much wider than I expected -- which to be fair was nothing.
\newline
\tab
Using the crater I accidental blew into the mountain makes climbing much easier. I wonder if I would’ve done something this destructive if Abel were here, climbing with me. I wonder why I couldn’t do something this destructive when it would’ve counted. I wonder why I froze, why I couldn’t have just killed or incapacitated him. I wonder why I wasn’t the one who died.
\newline
\suck{Chaos}
\newline
\tab
Everything’s chaotic; my mind, emotions, I’ve even been cursed with something my mind calls monochromia. The only colours I can see now are the emotions of others. I’m starting to think this is some sort of punishment for something. ``What have I done wrong? What did I do that deserved to have them killed?'' My voice is shaky and unpleasant to listen to. I scream. ``TELL ME!'' The rock I was holding onto shatters, maybe from my own doing, maybe not. I lose balance and quickly grab hold of something before falling into what would’ve probably been certain death. I try to calm down, allowing myself time to cry. It doesn’t work. I’m not calm.
\newline
\tab
I don’t want to be the only one crying. I want others to cry with me. I don’t want to be alone. Anybody would do. There’s no one. Nobody is here to colour in my world. All I have are monochromatic tears. I continue climbing. Something catches my eye, a rectangular stone. There’s a sense of familiarity to it, but I can’t remember why. I pick it up and continue climbing, thinking it’ll come to me eventually. I’ll remember why it seems so familiar later on. 
\newline
\tab
Once again, rain invades my body. It disgusts me.
\newline
\suck{NO!}
\newline
\tab
The ground I’m standing on cracks, and the rain is held back by my anger and disgust. Why is this the first time I’m realizing that could happen? Well, there’s a first time for everything. Just as I begin to feel like I have some amount of power, that feeling of a contradicting and paradoxical world seeps back -- no, that’s not right; comes from -- my body, engulfing everything around me. There’s a silhouette of a sitting boy again and though I can’t actually see him, I can tell he’s smiling at me. ``You’re finally beginning to realize it,'' my voice says to me.
\newline
\tab
I’m released, surprisingly quickly, from that feeling and continue climbing. What did it mean by ‘beginning to realize it’? I feel like there’s something missing from my memory. I can’t seem to recall my father’s name. The more I think about it, I can’t remember anything past a couple months before I ran from the ziggurat.  I can’t even remember why everyone hated me. There’s something wrong. 
\newline
\tab
If I begin to panic again, I won’t get anywhere. I’ll probably end up shattering something falling to my death. From where I am now, looking over to where Abel’s town was, I can see what I assume is a lake. It reminds me of one of Emma’s stories. We were sitting at the table eating dinner, Emma and Connor started talking about fishing for some reason. Connor reminded her of Aipaloovik, and she sprung into storytelling.
\newline
\tab
``This was one of the first stories we were told as children. They told us that they moved and rebuilt the village to run from this god. It was one of the only stories that doesn’t have an origin to the monster, because the monster was always there.'' And with that, the story began.
\newline
\tab
``There once was a village built bordering an ocean. The villagers were primarily vegetarian and would only eat fish for celebration. At the start of the summer season, the village began preparation for the summer festival. The village elder asked a man to take a boat and catch the largest fish he could find. So, the man took a fishing boat, a net, a fishing rod and a small box of worms before setting off into the ocean to fish.
\newline
\tab
``Once he got far enough away, he cast his fishing rod into the water and waited to see if any fish would approach him. His plan was to only bother setting down the net if he could catch at least two fish with his rod. Unfortunately, no fish approached him. He waited for an hour, but no fish came near his boat. So, he decided to switch locations. He moved even farther away from the shore, and once again, cast his rod. This time, he waited two hours, and nothing came. He didn’t want to be too far away from shore, so knowing there were currently know fish in the area, he set his sights westward.
\newline
\tab
``He paddled his boat for two hours, thinking that maybe there was something wrong with the area he was fishing in. He would be sure to make note of that area when he returned. Once again, he cast his rod and began waiting. After another three hours of waiting, he was close to giving up. He planned to return to the village empty handed, claiming there’s something scaring the fish away from his boat. He’d been out on a boat for eight hours now, and he was starting to get hungry.
\newline
\tab
``He quickly remembered that the festival was in two days and that if he were to return empty-handed, the elder would compensate by serving his head. The sky had already begun to turn dark, and he was scared of getting lost. Out of fear of returning empty-handed, he pressed onward, and travelled on more hour away from where he’d assumed to be shore. This time, he didn’t even bother casting his rod. He threw the fishing net down, waited, and pulled it back up. Nothing. He continued throwing the net down, waiting longer and longer each time. By this point he was starving and contemplated eating any fish he would catch.
\newline
\tab
``Dusk turned to dawn, and with the man’s absence, the elder sent another to go look for him. She had questioned if she should bring anything, food, fresh water, bait. The elder was very worried at this point and said, with clouded judgment, that it would only slow her down. She needn’t worry about such things if he’ll be returning to a feast.
\newline
\tab
``He hadn’t eaten or drank anything in a day, and it had started to affect his judgment. With infinite wisdom, he decided to forfeit his fishing rod and net, and swim to find fish.  He took off his clothes and jumped off the boat, swimming as deep as he could within the minute or so he could muster before having to go back up to surface for air. Just before he turned around, he caught a glimpse of something dark and slimy looking. Could it have been a fish? He surfaced, took a very deep breath -- to the point where he thought his lungs would explode -- and swam back down. He could see it clearly now. It wasn’t a fish. What he’d seen was a human skeleton, covered in some sort of black, shiny coating. Eyes appeared in the skull seemingly from nowhere, staring back at him. He began to swim away hastily when a large black arm reached towards him and plucked his body like a flower. The demon brought the man, now in desperate need of air close to his eye. It smiled and consumed him.
\newline
\tab
``The man woke up; he had surfaced and was dying in his boat. Something was different, something he hadn’t noticed until his body had started to move. He could actually see his body. He was staring down at himself from a bird’s eye view and was thoroughly confused as to why. Then, he noticed something else; he was not controlling his body. He started panicking, what was he to do? He soon realized panicking does nothing, especially when he’s bodiless. He slowly began remembering the events that transpired before he became like this and concluded that the demon in the ocean is the one controlling his body. 
\newline
\tab
``After further thought, he concluded the demon was the reason that he was unable to find any fish. So, as the next day began, he watched as the demon meandered around the small boat and swam around in the ocean, thankful that he could no longer feel that hunger. He began to find it rather amusing, watching his body dive repeatedly back into the ocean and resurface for air. 
\newline
\tab
``Some more time passed, and he began to wonder if the demon could feel hunger whilst using his body. In the distance, he saw another boat quickly approaching. He tried to scream for them to go away, but without a body, he wasn’t able to say anything. The boat quickly became clearer and more visible. He saw a woman rushing towards him. By this point, she was starting to scream for his -- or more specifically, the demon’s -- attention. The woman got close enough to the demon that she was able to see its face. They started talking. She was panicking and didn’t seem to notice that he wasn’t in control. By this point, he’d given up on trying to stop anything. The demon was in control. He won’t be able to change whatever’s going to happen.
\newline
\tab
``Amazingly, the demon managed to calm the woman down, and assured her everything’s okay. She asked if it’d caught any fish, to which it responded saying it caught a few small ones, but nothing too large. When she suggesting they head back, it hesitated, and said that it’d seen a large fish about a twenty-minute paddle away from the shore. Her response, filled with skepticism, was countered by the demon explaining that it went underwater to see where that bigger fish was. 
\newline
\tab
``With that, it had taken its boat, along with the woman, twenty more minutes away from shore. Factoring in exhaustion and lack of food, it would probably take them a day to get back to shore. However, that was of little to no concern for the demon. After all, it had no intention of coming back. 
\newline
\tab
``It cast the fishing net into the water, along with a couple worms and waited. Knowing that there would be at least a few fish left, it wasn’t surprised when it managed to catch four moderately-sized fish. By this point, the bodiless man had figured out that the demon must’ve been starving; it was showing in his eyes. He pulled one of the fish out of the net. The woman thought he was showing it to her and smiled. Her smile quickly disappeared when it bit off the head of the fish and swallowed it without chewing. Disgust turned to horror when it swallowed the body whole.
\newline
\tab
``She screamed at it, demanding to know why it ate a living fish. It responded simply by saying it hadn’t eaten in such a long time, and that it was her fault for not bringing food. She looked guilty and forgave him for eating the rest of the fish.
\newline
\tab
``What she did not forgive was when it stepped onto her boat and sank its teeth into her arm. She screamed, naturally, but they were too far away for anyone else to hear. The bodiless man watched as the demon used his body to eat an innocent, living woman. Unable to interfere or stop watching, he slowly started to lose his sanity. With every droplet of blood, a tiny fragment of reason and logic became lost to him. At the very end, he dropped the inedible remains into the ocean and used it as bait to catch more fish.
\newline
\tab
``The fisherman, now void of his sanity, watched as his skin began to peel off. The last bit of humanity he had left was fading. His skin peeled back to reveal a thin, black wrapping around his skeleton. Once the body’s skin came off, most of its organs fell out as well.  What was not devoured became used as bait for more fish. Though void of all logic and reason, the bodiless man still had his memories. He remembered a tale about a water god that resented humanity, told to him by the previous elder when he was a child.
\newline
\tab
```That’s right!’ a voice said to the fisherman. ‘I’m Aipaloovik’. It all made sense now, he was the god that despised humanity. He would possess other people, use them to take someone far away, and devour them alive.''
\newline
\tab
I miss hearing her stories. I would glance at Abel when things would get dark -- as they always would when Emma told stories -- and he'd smile at me reassuringly. Connor would sit listenting attentively, enthralled by her words. 
\newline
\tab
I wish I could hear one more story. Just one more. It started snowing, or raining, I’m not so sure anymore. I slip on a rock and begin falling. I need to survive. I need to make it to the top of the mountain. For him.
\newline
\suck{Please}
\newline
\tab
A great force pushes me towards the mountain side, and I grab hold of a rock, cutting a deep gash into my hand. The blood is nostalgic.  It’s been so long since I’ve seen my own blood. I bring my hand to my mouth and lick the wound. It stings. The iron in my blood tastes the same as it did back then. I guess that’s not surprising. If he were here, he’d be freaking out about the cut. I wonder if he was happy. All that time spend together; did I make him happy?
\newline
\tab
``We’ve been lying here smiling practically forever. Of course I’m happy! Isn’t it obvious?'' Hearing his voice makes me smile and cry.
\newline
\tab
``I’m glad. Thank you.'' I say out loud, despite knowing there’s nobody here to hear my words. Hearing his voice brings out a warm, purple glow from my heart.  Instinctively, I direct it to the stone I’m clutching in my hand. It glows the same colour as my heart, and slowly bits of dust fall from the stone. Unlike the last times, the characters are smoother, more circular, and less jagged. There are no white marks around the inscriptions, and I begin to remember why the stone looked so familiar. This is the last tablet I’ll ever make.
\newline
\tab
I hold the tablet in my arms and cry. ``I’m so sorry.'' I whisper. I’m not sure why, but I feel extremely guilty for making this tablet. I know when I’ll use it, and for some reason, I’m sure that its existence guarantees that I will use it. The event exists already. No matter what, I’ll get there in time. 
\newline
\tab
From my body springs that realm of contradictions I call rain. I’ve started to realize that the feeling comes from inside me rather than me being absorbed into it. The silhouette boy is closer to me this time, still sitting cross-legged and grinning at me. ``You know,'' my voice starts, ``I honestly believed that you were going to kill them. That’s one of the reasons I gave you Pralaya. It’s the energy that deletes the universe.'' I begin to realize it’s the body that’s using my voice. That only angers me further.
\newline
\suck{You thought I would be the one to kill them\textinterrobang}
\newline
\tab
``Well, yeah. We’re two sides of the same coin after all. Sorry, bad metaphor?'' The rain disperses with those words. That boy remains in my head. What does he mean? What gave him the impression that I’d kill them? A thought hits me like a rock to the head, I begin to see everything. Just as I finally understand, it leaves my mind, taking my other thoughts with it. I’m left with blurry vision and the knowledge that I’m somehow related to that boy. I look at my hands. My right hand is covered in blood, and my left is clutching the tablet so tightly I think it might shatter. Inhale. One. Two. Three. Four. Five. Exhale. One. Two. Three. Four. Five. I repeat that three or four times until things roughly go back to normal and I’m at least partially calm.
\newline
\tab
I’m almost at the top. Just a few more minutes and I should be there. My hand is throbbing with pain, but it doesn’t matter. Nothing in this monochrome world matters anymore. The thought occurred to me that I could’ve probably used a miracle to get to the top much quicker. Without the journey, the result is meaningless. Without him, both are meaningless. That’s what this tablet is for.
\newline
\tab
I make it to the top, finally. I stand in a pile of snow overlooking the world I’ve decided to leave. I…wait, that’s wrong. Rain plagues the world around me, the boy is standing in front of me. My silhouette has become a reflection. Was it always like that? I stare at my body, smiling back at me. It borrows my voice again and berates me with questions.``What do you think will happen when you kill yourself? What do you think will happen to your powers? Where do you think they will go? Look around you. They’re the ones who will get it. Those people who hated you and your friends so much. What do you think they’ll do with it? What do you think your death will cause?'' It releases me for the last time. I come to my own conclusions.
\newline
\suck{Death}\tab\suck{Destruction}\tab\suck{Chaos}
\newline
\tab\tab\tab\suck{The End}
\newline
\tab
I grip the tablet with both hands, accidentally getting a bit of blood on it. I reach into the tablet and engorge myself on the purple glow. It covers my body and the tablet slowly fades to dust, blown away by the wind. My skin slowly begins solidifying, turning to stone. I can feel my mind slowly beginning to fade. Such a different emotion, yet it brings the same ending. 
\newline
\tab
``Aah, finally. Nobody’s taking this from me. I’ll see you soon.'' I say out of bliss.
\newline
\tab
``Does it hurt?'' Abel asks softly, approaching from behind me.
\newline
\tab
``Of course not,'' I respond, smiling. ``I’ve wanted to see you for such a long time.''
\newline
\tab
``I’m sorry,'' he says regretfully. ``I --''
\newline
\tab
``Don’t be. Seeing you now was worth the wait.'' I intentionally cut him off. I don’t want any more regrets.
\newline
\tab
``Thank you. It’s a shame we won’t be able to talk longer.''
\newline
\tab
``What are you talking about? That tablet’s wish wasn’t to kill me, it was to bring me to you. This purple glow is the reason you’re here with me now. Be happy, like we used to be.'' I smile at him. Most of my body is already petrified. All that’s left is my head.
\newline
\tab
``I’ll see you soon,'' he says grinning. He moves closer and presses his lips against mine. My body turns to stone. Abel disappears and my mind is reaching the end of the line. It was worth the wait. I have no regrets. Though I wouldn’t call this a good life, I don’t hate it.
\newline
\suck{I’ll see you soon}
\backmatter
\chapter{Epilogue: One Last Story}
\tab
I’m going to tell you a story. Bear with me, I haven’t had much practice with this. Sorry if I’m cut off, I’m not sure how much time I have left.
\begin{itshape}
\newline
\newline
\tab
There was once a boy who lived with his family. They lived in a forest clustered with hundreds of other people that would hollow out trees to use as homes. They were all very happy. His parents were nice, and he loved his two younger siblings dearly. However, there was something he was hiding from them. At first, he didn’t think much of it. He had assumed that it was fine if they didn’t know. Everyone has secrets, right?
\newline
\tab
Slowly but surely, the secret began to eat away at the boy. It was such an integral part of his life that he couldn’t help but want to tell his family. When he thought about how they would react, he became scared to tell them. They were very… set in their ways, and he was scared they wouldn’t accept him.
\newline
\tab
One day, while eating dinner with his family, he built up the courage he needed and told them his secret. They all laughed, thinking it was a joke. He told them again, seriously. He felt the air change. The laughter quickly died off; all eyes were on him. His father looked at him gravely, demanding for it to be a joke. The boy told his father he was serious and from that point onward, his father ordered that nobody speak to him until he ``goes back to being normal.''
\newline
\tab
The boy was devastated. From then on, there had been one less seat at the dinner table, his room became an extra storage space for the family, and nobody would talk to him. Not even his younger siblings acknowledged his existence.
\newline
\tab
When he ran away, nobody batted an eye. His family continued life as normal, and he became a distant memory in the minds of his younger siblings. He left his home and wandered the forest, being fed by those who took enough pity on him to bring him food. Days went by where he wouldn’t get fed. He was becoming skinnier and unhealthier. Though his situation became worse than what he had with his family, he found himself to be mentally in a happier place -- or at least that’s what he forced himself to believe.
\newline
\tab
One day, a boy who looked to be around his age walked up to him, offering food. The boy introduced himself. ``My name is Adam.'' He said as he watched the boy slowly consume what was offered to him. ``Do you want to come with me?'' He asked.
\newline
\tab
``I’ve got nowhere else to go; sure. I’m Ea.'' With that, Ea got up and started walking alongside Adam. They walked in silence and Ea realized just how much he had missed having someone beside him. Unnatural though it was, he looked at Adam with a closeness bordering family. He was happy, something he hadn’t actually been in a long time. After a while, Ea began to wonder where they were going. ``Where are you taking me?'' He asked out of curiosity.
\newline
\tab
``I don’t know. We’ll figure it out when we get there.'' Such an odd response. They wandered the forest of the city for a while, eventually reaching an exit. Ea focused his gaze on the side-profile of his new friend, studying the way he looked. Black, short hair contrasted by pale skin. He was skinny, but not nearly as skinny as Ea. The forests had become such an uninteresting sight to Ea that he didn’t even notice where they were until Adam stopped moving. They meandered along the border of the city until the sky turned dark. Adam sighed. ``Didn’t find it today either.'' He sounded disappointed.
\newline
\tab
``What were you looking for?'' Ea asked, wanting to learn more about his mysterious new friend.
\newline
\tab
``I don’t know. I’ll know when I see it. For now, do you want to stay with me, or do you prefer living outside?'' His comment greatly confused Ea, and the only reason why he didn't ask Adam what he meant was because he didn't feel like it was his place.
\newline
\tab
``Do you think anyone would want to remain out here?'' Ea asked playfully, with a mild accidental irritation in his voice.
\newline
\tab
``Good point. Alright then, I don’t live too far from here.'' They continued walking in the same direction for ten minutes before reaching a small boring looking house. Had it stood out from the rest, Ea might’ve recognized it from his mindless wanderings, but it looked like every other house around it. ``Don’t worry. I live alone.'' Adam said, with a mild relief pigmenting his voice. Adam walked in, while Ea remained in the entrance, silently nervous. ``Are you going to come in?'' Adam asked, grinning at him.
\newline
\tab
``Can I?'' Ea responded nervously.
\newline
\tab
``I wouldn’t have brought you here otherwise.'' With that, Ea entered and sat himself down on a couch. The house looked surprisingly bigger on the inside and was much more open than he’d expected. ``What do you want to eat for dinner?'' Adam asked, as he sat down beside Ea.
\newline
\tab
``Don’t worry about me. I --''
\newline
\tab
``Don’t be silly. Just tell me what you want to eat.'' Adam could sense that Ea didn’t want to be a bother and would pretend to be fine without food. Ea’s skinniness practically screamed to feed him.
\newline
\tab
``Make whatever you want. I’ll eat anything.'' That response seemed to have satisfied Adam.
\newline
\tab
``Alright then.'' He smiled and walked over to his kitchen. Half an hour later, he returned with some kind of stew. 
\newline
\tab
They sat down and ate the stew in blissful silence. Once again, Ea felt like he was part of a happy family. He wasn’t sure why Adam had picked him. There were certainly others that shared his situation. Maybe it was because they were around the same age. Adam let him sleep on the couch. Ea hadn’t slept well in such a long time and was very grateful for all Adam had done for him.
\newline
\tab
When he awoke the next morning, he decided he would tell Adam what he had told his family. He didn’t want it to slowly eat away at him forever. So, he turned to Adam and told him. Adam grinned at him. Ea began to fear he too had assumed it was a joke.  ``I know, I could tell. That’s why I took you with me. You’re not alone.'' Those words relieved Ea of his stress. Ea ran up and hugged Adam. 
\newline
\tab
``Thank you. Thank you so much.'' Ea said over and over again. Adam embraced him, also knowing what it’s like to be rejected by family.
\newline
\tab
They lived together for a while, happily. Ea realized what happiness actually felt like; no worries, no regrets, nothing to hide. He was extremely grateful and did his best to help out with whatever he could. However, all good things must come to an end.
\newline
\tab
Adam’s parents came to his house one morning. He let them in. The way he spoke to them was different. There was a change in the air. Something Ea recognized. It made his stomach lurch. ``Too many people are talking about you. They say you picked up a homeless boy. Come back home, you’re being ridiculous. Why can’t you just be normal? Why can’t you just be like everybody else?'' Adam’s parents acted the same as Ea’s parents did. They cared too much for their reputation and were too set in their ways.
\newline
\tab
``Why can’t I just be normal? Why can’t you just accept me for who I am?'' Adam’s voice was filled with anger. He at least had the confidence to stand up for himself, which enforced his parents’ view of him as an obstacle. Adam stood up and screamed at his parents. ``We live on our own without affecting anybody! What right do you have to fuck up our lives\textinterrobang''
\newline
\tab
``How dare you!'' His mother screamed. The realization of what he was doing settled in and he backed down. Even then, he still kept control of the situation.
\newline
\tab
``Leave. Don’t ever come back here again. GET OUT!'' At that point, Ea walked in and grabbed Adam’s hand, trying to calm him down. Adam was shaking.
\newline
\tab
His parents looked at both of them with disgust, which only infuriated Adam more. He said nothing, just watched with angered eyes as his parents walked out the door. Adam knew they would come back; and he knew that when they did, he would be forced to go with them.
\newline
\tab
Ea spent the rest of the day doing his best to comfort Adam. Though he was in a similar situation, he couldn’t imagine what he would do if his parents tried to take him away -- not that they even remember him by this point. Ea was sure that if he still existed in his family, it was in the distant memory of his siblings.
\newline
\tab
Ea cooked meals and did his best to take Adam’s mind off things. By the time night came around, Ea climbed into Adam’s bed and snuggled against him. ``Wh... what are you doing?'' Adam asked timidly and with great embarrassment.
\newline
\tab
``You’re not alone.'' Ea replied, continuing to hug him.
\newline
\tab
The next day, Adam woke up, surprised to see Ea so close to him. The memories of the previous day’s events quickly set in. He was thankful to have Ea there for him. He also knew that it wasn’t going to last much longer. Soon, his parents would come again, and no matter how hard he fought, he would be forced to go with them.
\newline
\tab
He got up and made breakfast for the two of them. They ate happily in silence and embarrassment. Ea hadn’t planned to sleep next to him. He was going to wait until Adam fell asleep, then quietly head to his couch. However, soon after Adam had fallen asleep, Ea lost consciousness. When he woke up, Adam had been in the kitchen, and Ea soon realized where he was. 
\newline
\tab
Though Adam recognized it was going to be soon, he didn’t expect them to come later that day. When the door opened, Adam froze, eyes widened by the intruders. ``This is your last chance.'' His father said. ``Come home now, without a fight.'' Two massive and bulky men walked into the house. His father grinned.
\newline
\tab
``STOP!'' Ea screamed, running towards them with a hubris as big as his lack of logic. He had seen Adam’s intent to fight and didn’t want him to get hurt. Even though he had no chance of winning, he had hoped that he could at least do something.
\newline
\tab
``Don’t make me hurt you.'' One of the beast-like men said, to no avail. Ea charged at him, taking the full force of his punch to the gut. He flew backwards, hitting his head on a chair and blacking out. He knew what was going to happen. He didn’t want to lose Adam, but didn’t have the strength to stop them, let alone get up. When he reopened his eyes. he saw Adam being punched and kicked repeatedly by the two men. Each time he was knocked down, he would get up with increasing difficulty. Each time he would get up, his body became more and more bloodied.
\newline
\tab
``We’ll stop whenever you agree to come home.'' His father said, as if he were the one who was beating his son. The men seem as if they enjoy beating up a defenseless, bloodied child. At some point, Adam collapsed and became unable to stand. They continue to punch and kick him, unaware of his lack of consciousness. ``Stop.'' His father orders. They comply, stepping away from the child. ``Hit the other one two or three times, then carry this thing back.''
\newline
\tab
Out of fear, Ea closes his eyes and acts as if he’s knocked out. The two men, not caring for his state, grab him by the neck and punch him in the gut. His eyes snap open from the pain and the force ejects blood from his mouth. They drop him to the ground and one of them picks up Adam, throwing the boy over his shoulder. Adam manages to regain consciousness and smiles at Ea while being carried out the door. ``I’m sorry.'' He says silently, praying that Ea reads his lips. ``I’ll return soon. I promise.'' No matter how much he’d hoped. He knew that that promise was fake. Adam would not be returning.
\end{itshape}
\newline
\newline
\tab
I wish I got to spend more time with you. I know you’ll continue on without me, no matter how much you suffer. I’m sorry I wasn’t able to climb the mountain with you. I know you’ll get there on your own just fine though. I just wish I could spend one more day with you.
\end{document}