\RequirePackage{fix-cm}
\documentclass[a4paper, 12pt]{book}
\usepackage[utf8]{inputenc}
\usepackage{authblk}
\usepackage{setspace} 
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{geometry}
\usepackage{textcomp}

\usepackage{fontspec}

\geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 top=20mm,
}
\title{Those Who Were Once People}
\author{Liam Gardner}
\date{\today}
\doublespacing

\newfontface{\cuneiform}[Scale=MatchUppercase]{SantakkuM}
\DeclareTextFontCommand{\textcuneiform}{\cuneiform}

\newcommand\tab[1][1cm]{\hspace*{#1}}

\DeclareMathAlphabet{\mathpzc}{OT1}{pzc}{m}{it}
\DeclareFontFamily{OT1}{pzc}{}
\DeclareFontShape{OT1}{pzc}{m}{it}{<-> s * [0.900] pzcmi7t}{}
\DeclareMathAlphabet{\mathpzc}{OT1}{pzc}{m}{it}

\begin{document}
\newcommand{\AmaGi}{$\stackrel{\hbox{\fontsize{15}{60}\selectfont ama-gi}}{\hbox{\fontsize{30}{60}\selectfont {\symbol{"120BC}\symbol{"12104}}}}$}




\maketitle
\section*{Part 1}
\tab
``That’s all everyone’s been talking about for the last four months!'' I say with more annoyance in my voice than initially intended. ``Even if that kid said he performed the ritual, that doesn’t mean it’s true. He’s probably lying about it.''
\newline
\tab
``That kid was missing for an entire month. He was found with an arm and eye gone. You really think he’d have a reason to lie?'' 
\newline
\tab
``The ritual itself is full of inconsistencies. Why would you inscribe a Sumerian word onto a stone, then pray to a Roman god?'' I reply. These conversations are getting increasingly annoying. ``What’s the point of it being an old building anyway? Or why does it have to be at midnight? Shouldn’t a time god be able to move freely throughout time?''
\newline
\tab
He answers with a smug annoyance in his voice. ``Janus is the god of doorways and passages, idiot. He’s not a time god.''
\newline
\tab
I sigh, realizing why plot-holes like this manage to continue to exist. ``Janus'', I begin reading from the Wikipedia page of my phone, ``is the god of beginnings, gates, transitions, time, duality, doorways, passages, and endings.''
\newline
\tab
``If you’re so confident that the ritual is fake, why don’t you do it? The school used to be an old church, right?''
\newline
\tab
I wonder how much trouble I’d be in if my parents figured out that I’m spending the night at school performing a weird ritual. ``Yeah, yeah, fine. I’ll prove you wrong. You owe me \$50 if it doesn’t work.''
\newline
\tab
He looks at me in shock. ``For what\textinterrobang'' he almost shouts.
\newline
\tab
I turn to him before entering my next class. ``For wasting my time.''
\newline
\tab
Annoyingly, he follows me in. ``How am I supposed to get that money?'' He asks in a begging voice that only serves to further infuriate me.
\newline
\tab
``If you’re so confident it works, you don’t have to worry about getting the money.'' I retort, grinning. The teacher walks into the classroom causing him to leave, so as to not attract unwanted attention. 
\newline
\tab
Classes continue on as usual. People spend their conversations purely on the topic of that urban legend popularized on the internet. The day goes on and I do everything in my power to avoid these types of conversations, which typically leads to avoiding most people entirely. Unfortunately, that particular conversation between classes led to a decent chunk of my classmates thinking I was bragging about me going to perform the ritual. I guess I don’t really have much of a choice about backing out now.
\newline
\tab
The day moves onward as more and more people find out about how I’m going to perform the ritual. I hear some people talk about someone else also going to do it as well, but I don’t really care enough to listen in. The day ends and I go home to pack my things. On the bus, a younger student hands me a stone with letters carved into it. ``For the ritual,'' he says quietly and embarrassed. ``Good luck.'' I nod, staring at the cuneiform inscription, \textcuneiform{\AmaGi} the Sumerian word for freedom. I almost begin to laugh. The more I think about it, the more it seems like something an edgy teenager would try to run away from their life and responsibilities.
\newline
\tab
I get home, enter the kitchen, and grab a pack of candles and a lighter. Heading up to my room, I grab a few blankets to sleep on, choosing to ignore taking a pillow for the sake of remaining relatively light. Chances are, it’ll be easier to stay at school for the night rather than to bus all the way back home. It’ll probably also be safer as well. Heading towards the bus stop, the thought slowly creeps up in the back of my mind that the ritual might actually work. I take a seat on an almost vacant bus and pull up the blog post on my phone. 
\newline
\tab
\textit{
Place the candles in a triangle, with the stone in the middle and say the words ``O god of passage, strip us of our sins and bring us to the free world!'' 
}
\newline
\tab
Reading over it, it also says there’s no way back. A wave of relief washes over me. There’s no way to know if it’s impossible to come back or not. You either don’t know, because you haven’t tried the ritual yourself, or you know you can come back, because you tried it and returned to make the blog post. The more inconsistencies I find in this, the more reassured I feel about my success.
\newline
\tab
Walking into the main hall of the school, I find one other student who probably shares my intention. ``Andraste!'' I call out to her, walking over to see what she’s doing.
\newline
\tab
``Oh,'' she replies, ``I didn’t think you’d show up.''
\newline
\tab
``I didn’t really have much of a choice. This is probably the most effective way to get rid of the legend, right? Or at least in our school.''
\newline
\tab
``Yeah, probably. It’s only 21:00, what do you want to do for three hours?'' She asks. If we share a common goal, we may as well work together, not that it’d help if I stated that. My stomach slowly starts to silently tell me that I haven’t eaten in a while.
\newline
\tab
``Have you had dinner yet?'' I ask, getting increasingly hungry as we speak.
\newline
\tab
``Imagine that, the last thing that happens to me in this world is being asked out on a date!'' she replies almost laughing. ``No, I haven’t eaten yet.'' 
\newline
\tab
I choose to ignore that comment, not wanting to start an argument. ``Let’s get burgers then,'' I say, ``I haven’t eaten since lunch.'' She nods and we head out to get dinner. Aside from a few staff, the burger joint is completely empty. It feels kind of eerie. There should be at least a few more people here at this time, right? We order our food and sit down. ``What do you think of this?'' I ask, attempting to distract myself from the unnerving atmosphere.
\newline
\tab
``Zius, you don’t really believe in all this, do you?'' she asks, seeming almost concerned.
\newline
\tab
``My name is Ziustra, not Zius,'' I reply with an almost instinctual hostility. After a couple seconds, I continue in a calmer manner. ``No, I don’t believe in any of this. I just hate that it hasn’t died off yet.''
\newline
\tab
She smiles and nods at my response. ``Good, we’re in the same boat then.'' I could’ve probably told her that before we got food...
\newline
\tab
We walk back to the school, talking about all the inconsistencies we found in the ritual. Mixing of religions, not being able to get back, eventually, we found out that the post was copied from another, less-popular forum. Slowly but surely, time passes. Both of us get more and more anxious as we get closer to midnight. Neither of us bring up the possibility of the ritual being true, especially with the thought of being unable to return. The clock shifts to 23:55. ``I guess we should get started,'' I say with a mild tinge of regret in my voice.
\newline
\tab
I pull out three candles from my bag and place them in a triangle about 30 centimetres apart from each other. I reach further into my bag and pull out the inscribed stone given to me by that kid on the bus. Placing the stone in the middle of the triangle, inscription-side down, I look back at the clock to see how much time we have. 23:57. I take out the lighter -- which in hindsight shouldn’t have been placed around blankets and candles -- and light the candles. We wait for the clock to reach midnight before beginning our prayer. 00:00. ``O god of passage, strip us of our sins and bring us into the free world.'' One second has passed. Two seconds have passed. Three, five, ten, thirty; nothing happens. We look over at each other, holding our breath. I practically expect some sort of jump-scare, but nothing comes. We breathe a sigh of relief. We end up spending the night at school in makeshift sleeping bags made from the blankets I brought. I leave the candles as they are just to provide some light since the school’s lights are off.
\newline
\tab
When I wake up, Andraste’s sitting around the now-extinguished candles. I get up, slowly, and she snaps her head in my direction, looking at me like I’m a ghost. I begin to think that maybe I did or said something in my sleep.
\newline
\tab
There’s no sound. No hums from the air conditioner or lights. No insects or wind, nothing. I can hear the sounds of my breathing and heartbeat so clearly it feels like I have control of their pacing. I feel like I have to consciously think to keep my heart moving. ``Do you... hear anything?'' I ask slowly. Even the sound of my own voice feels off.
\newline
\tab
It takes her a moment to reply ``Nothing.'' I nod slowly.
\newline
\tab
We pack up the stuff into our bags and begin to walk towards the exit. ``There’s something... off,'' I begin speaking without really thinking, ``not the silence but --''
\newline
\tab
``The atmosphere.'' She stated in a grave and serious tone before turning back to me. Her next words were the only thing I didn’t want to hear. ``It worked.''
\newline
\tab
I laugh to myself, ``looks like I’m not getting that \$50,'' she gives me a disgusted look but says nothing.
\newline
\tab
We performed the ritual in the corner of the school, on the second floor. It’s typically completely empty during the day, so just in case anyone else shared our thoughts, we wouldn’t see them. I’m sure there are even a couple students that didn’t know this place existed. In one of the main stairways lies confirmation that our ritual worked. A fully-clothed metal statue of a student looks towards the top-left of the stairway -- away from us -- with outstretched arms. ``I don’t think... that statue’s... manmade.''
\newline
\tab
Andraste’s words only serve to terrify me further. She’s probably right, but I don’t want to believe it. I say nothing. Looking at the statue, the metal itself seems so polished and clean that it could be a mirror if it weren’t for the shape.
\newline
\tab
We move closer towards the statue, half-expecting it to move. It doesn’t. ``Look!'' I say, pointing at it’s feet. ``A notebook.'' We haphazardly rush down the stairs. Looking back at the statue in fear, I get a clear look at its -- her -- face. The statue’s face looks like that of a crying girl. Her teardrops solidified onto her face, her eyes are slightly slanted downwards, and her face looks... worn? No, that’s not right. I can’t really describe it, but it only serves to make things even more terrifying. Andraste’s right, that thing doesn’t look manmade. Nobody could sculpt a face that... powerful.
\newline
\tab
She picks up the notebook and begins flipping through it. I move to stand behind her just as she begins reading the last entry of what we’re now figuring out is a diary.
\newline
\tab
\textit{
It started a month ago. Everyone thought it was just a flu, another strand of the influenza virus. Our first hint should’ve been the vaccines -- they didn’t work. A lot more people died, but that’s nothing in comparison to what’s happening now. To be honest, I’d rather be dead. Most people recovered on their own, it was really just the very young children and elderly who were at fatal risk. A week after people recovered, they would start turning into these metal statues. Nobody’s sure why, or even how, but we’ve discovered a few things:
}
\begin{enumerate}
\item \textit{The statues somehow block all technological communication. No radio, no wi-fi, nothing. Everything becomes distorted.}
\item \textit{The statues are virtually indestructible.}
\item \textit{The statues are not contagious and cannot spread the virus. I still wouldn’t go around touching them.}
\end{enumerate}
\tab
\textit{This is day 7 for me. On the off-hand chance that someone finds this, good luck.}
\newline
\tab
\begin{center}
\textit{April 11th, 2018.}
\end{center}
\tab
She drops the journal. ``That was two years ago.'' She says, looking at me.
\newline
\tab
I nod, picking up the journal and putting it in my bag. ``Let’s look around the school more.'' I say, trying to distract both her and me. She only nods, turning away from what once was a person and walking into the main hall of the school. There are more statues of students and teachers in the hallways and classrooms. Every statue either looks like it’s crying or about to cry. Part of me hopes that the journal was a prank or joke, but I know nobody has the ability to create something this... real. We walk into the main office; the receptionist is a crying statue. I walk over to the front desk and pick up a calendar. ``It looks like this all happened two years ago. At least that rules out time travel.'' I sigh. This means that time is synced with our world.
\newline
\tab
Andraste looks at up at me. ``If we didn’t time travel, that means the virus has had time to die off, at least in this area. We aren’t immune, but chances are we’re relatively safe from it.'' I nod in agreement. Her stomach growls, the silence only serving to make the noise seem louder. She blushes in embarrassment.
\newline
\tab
``We need a food supply. If it’s replenishable, that’s probably better. We don’t know how...'' I trail off, not wanting to finish that thought.
\newline
\tab
``You’re right,'' she says, ``let’s check the school garden.''
\newline
\tab
``They grow a few edible things, but we’d still need a way to get meat, right?'' The garden wasn’t ever meant to be used as a food source in the first place. It was probably just meant as a way to judge the students’ level of maturity or responsibility. Either way, small amounts of food is better than nothing, so I keep my mouth shut.
\newline
\tab
``It’s still worth checking out,'' I nod, and we head over to the garden. The moment we walk into the courtyard, I pause. \textit{There’s something wrong.} She walks over to the plants and lifts up a leaf. ``These seem fresh. We should be able to eat these.'' She says, turning to me with what almost seems like excitement in her eyes.
\newline
\tab
``Hey,'' I say slowly. She looks at me quizzically. ``Who’s been tending to the garden?'' she lets go of the leaf, slowly walking towards me. ``Let’s get out of here,'' she says. She has that look in her eyes that makes me think she’s noticed something. I follow her inside, closing the door behind us. ``Did you see something?'' I ask, wondering why she’s so freaked out.
\newline
\tab
``Don’t panic,'' she starts. I can feel my face slowly becoming pale. ``You’re right. If it’s been two years since everyone’s turned to metal, those plants would’ve been overgrown. But they weren’t. The grass was cut, the plants were trimmed, everything was clean. Just like --''
\newline
\tab
``The school,'' I say, catching on to her train of thought. ``There’s someone else here.'' She nods. We don’t move for a few minutes, individually trying to come up with our own ideas of what to do next. ``We should stay in the school. We’ll have an easier time monitoring if anyone comes in or out. Also --''
\newline
\tab
She continues my thoughts. ``We’re a lot less likely to see someone before they see us if we’re outside. We’d be like sitting ducks.''
\newline
\tab
``For now though, we still need food. Let’s go back out into the courtyard. Try and pick out the ones near the back, and only get one or two from each plant.'' With that, we go back outside, trying to make as little noise as possible, while picking out as many vegetables as we can within the span of a few minutes before rushing back inside and placing down our goods.
\newline
\tab
Andraste sighs, ``We’re going to have to cook most of these,'' she says. Looking at our new food source, we’ve collected a few carrots, onions, potatoes, radishes, and leeks. I sigh as well.
\newline
\tab
``We should try the cafeteria,'' I say. She nods in agreement. ``We uprooted most of these. If whoever’s here goes to the garden, they’ll notice that we’re here. We should avoid the garden for the time being.''
\newline
\tab
``If the cafeteria’s anything like our school, the fridge will be empty. At least we’ll be able to cook these,'' she says. We walk towards the cafeteria, carefully taking note of the crying metal statues as well as looking out for any movement.
\newline
\tab
We get to the cafeteria, open the door to the other side of the counter and move towards the deep fryer. She flips the power switch, causing the machine to start making a loud air-conditioner-like hum. ``Shit! Shit! Shit! Shit! Shit!'' she shouts, hurrying to turn off the power. ``What the hell was that\textinterrobang''
\newline
\tab
``We’re so used to the background noise that being without it makes everything else seem louder. You noticed it when we first woke up too right? The sound of your heart beating so clearly it seems like you have to manually control it.''
\newline
\tab
``So what do we do now? Eat everything raw?'' Andraste shouts at me.
\newline
\tab
``We have no idea who the person taking care of this place is or what their intentions are. They might actually want to help rather than kill us.'' She seems doubtful of my words, but the ideas at least calmed her down. ``Turn it on, I’ll wait by the entrance while you cook. If anyone starts coming towards us, I’ll let you know.''
\newline
\tab
``And then?'' She replies annoyed. ``What’ll we do if someone comes for us? What if they’re \textit{not} friendly? How can we even \textit{think} of fighting someone if we don’t know what weapons they have? Someone comes, following the sounds, we’re preparing to stab them with kitchen knives while they have a fucking machine gun!''
\newline
\tab
``Where would they even get a machine gun from?'' I reply in a calm voice, which only serves to anger her more. ``This is the safest option we have aside from eating an onion like an apple. Let’s go prepare the food first, then we’ll turn on the deep fryer when we’re ready. I’ll wait by the door and tell you if I see anything. If I see any movement, we’ll leave the deep fryer on and hide in a closet. If they have guns, at least we’ll stand more of a chance that way.'' She doesn’t fight this argument, though I’m guessing more out of not wanting to fight than out of agreement, and we begin preparing our food.
\newline
\tab
``We could boil these and make a soup,'' she says after a few minutes of silent chopping and peeling. ``It’d probably be healthier too.''
\newline
\tab
I smile in agreement, relieved that I don’t have to watch out for a potential murderer just yet. ``Finish up here, I’ll get the stove and water ready.'' She turns back to chopping the last carrot as I fill a pot with two litres of water and place it on the stove. She comes over, pouring the chopped vegetables into the water as I turn on the element. ``Did we ever check the fridge?'' I ask after half-covering the pot with a lid.
\newline
\tab
``I don’t think so,'' Andraste replies, ``Why? There’s nothing there normally. If this is a mirror of our world, there’d be nothing in it now, right?''
\newline
\tab
``If there’s someone here, and everything has power, why wouldn’t they use the fridge to store food?'' Her eyes widen with realization, but not from what I told her.
\newline
\tab
She looks at me in that same way she did back at the garden. ``If there’s someone here, and they use the cafeteria as food storage, this is probably the place we’re most likely to find them, right?'' The water starts whistling, signifying the end of our wait. Andraste moves to turn off the stove. We carefully ladle our soup into two large bowls, grab spoons, and move behind a stairway at the other end of the hall. ``We may as well leave everything there, if they look at the garden, they’ll notice that we’re here anyway.''
\newline
\tab
``Everything we do leads to us getting closer and closer to being noticed, right? If we’re going to stay here, we should stay in a classroom. That way we can at least lock the door.''
\newline
\tab
She ponders for a moment as to what our next move should be. ``Let’s sleep in the science wing, it’s on the opposite side of the school, away from the garden and cafeteria.''
\newline
\tab
``If someone finds out we’re here, they’d search the entire school.'' I reply, unconvinced that we should avoid our previous locations. ``We should stay on the first floor, somewhere with a window we can escape out of and into the city if we’re found out.''
\newline
\tab
``The science wing should at least have supplies to make some sort of weaponry. We’d be more prepared for defence than we are now. Let’s at least stop by.'' I nod, mostly out of not wanting another argument. As we finish the soup, I begin to wonder what materials she’d want from the science wing. We make our way up the stairs and towards the other side of the school, passing by at least ten other metal statues. Entering the chemistry lab and walking into the room labelled \textit{No Students Allowed}, I turn to her and ask, ``what is it that you’re looking for?''
\newline
\tab
She opens a drawer filled with opaque containers. ``Iron oxide, aluminium powder, and magnesium.'' 
\newline
\tab
``For what exactly?'' I ask slowly.
\newline
\tab
``Didn’t you ever pay attention in science class? I’m making thermite!''
\newline
\tab
I back out of the \textit{No Students Allowed} room slowly. ``What are you going to use thermite for? I can’t see that being easily weaponized.''
\newline
\tab
``You know that thing some people do where they’ll draw a line of salt to prevent demons from walking in? Here’s the anti-human version,'' she replies, smirking.
\newline
\tab
``Did you forget the tiny fact that we’re also human? That’ll kill us too!'' I almost shout. 
\newline
\tab
She turns to me, walking out and holding three containers. ``Hear me out,'' she starts. ``You were right. Sleeping up here makes us cornered. Having a window as an escape option is nice, but if we’re followed it becomes a test of stamina. If they have a gun, we automatically lose. Let’s assume they find us. The noise from trying to break down the door will wake us up and give us enough time to run Then what? How do we make sure we aren’t followed? Between the window and door, we’ll draw a line of thermite that we can ignite of we hear someone. It’ll be bright enough to stop them from getting a good look at us as we run away.'' It seems a bit overkill, but I don’t argue against the idea.
\newline
\tab
``Sprinkler systems activate from heat and smoke detection, so thermite should be able to trigger that as well.'' I reply. ``I never took chemistry though, so don’t expect me to help.''
\newline
\tab
She grins, as if hoping that I wouldn’t be able to help. ``Don’t worry, just get the room ready. I’m assuming you know which one we’ll be sleeping in.'' She says, focusing on sorting out how much of each material she’ll need.
\newline
\tab
``I’d rather not be alone with all the metallic statues,'' I admit, slightly embarrassed. ``There’s just something about the fact that they were all people. It’s kind of unnerving.''
\newline
\tab
She sighs, turning towards me and smiling. ``It’s alright. Sit over there.'' She says, pointing to the other end of the room. I smile back and make my way over as she begins to work her magic -- or I guess it’s more science. It takes her roughly 15 minutes to finish making a bucket-full of thermite. 
\newline
\tab
I’m staring out the window as the sun begins to set. ``We should probably stay in 107,'' I say, ``It has a decently big window on the opposite corner as the door. The room itself is also at a size where the distance between the door and window is fairly large, but it isn’t big enough for us to use all of that thermite.
\newline
\tab
She nods and we head down the stairway to room 107. We open the door and find two statues at the front of the room staring at a wall with semi-outstretched arms. Andraste turns to me. ``Are you going to be okay here?'' 
\newline
\tab
Her question catches me off guard. After a second, I respond. ``I’ll be fine. At least they’re not facing us.''
\newline
\tab
``Get the blankets ready. I’ll make the barrier.'' I chuckle at the word barrier being used to describe a thin line of thermite. I set up two blankets near the centre of the window. She turns back to me. ``You still have your lighter, right?''
\newline
\tab
I smile. ``Shouldn’t you have checked before making the thermite?'' I ask, only to get a glare telling me to answer the question. ``Yeah, I still have it.'' I reply, pulling it out of my bag to show her.
\newline
\tab
We lock the door to the room and get in our poorly made sleeping bags, laying there silent for 30 minutes. She’s not so close that I can hear her breathing or heartbeat, but she’s close enough that I can tell she’s still awake without having to turn my head. ``Are you okay?'' I ask softly.
\newline
\tab
``How could anyone be okay in this situation?'' She replies. In a softer, almost inaudible voice, she continues. ``I’m terrified.''
\newline
\tab
I almost reach out my hand but hold back the urge. ``So am I.'' I reply. ``I never thought that the ritual would actually work.''
\newline
\tab
``Yeah. I just wanted everyone to stop talking about it.'' She pauses. ``I wonder what they’re all doing right now?'' Her tone terrifies me. It makes her sound like she’s on the verge of crying. I can’t stop myself. I reach out and hold her hand -- more for my sake than hers. We stay like this in silence for as long as I retain consciousness.
\section*{Part 2}
\tab
I wake up before her, still holding her hand. I don’t want to wake her just yet, so I continue staring up at the ceiling. She gets up slowly, turning to me and smiling; still holding onto my hand. I smile back. ``How did you sleep?'' I ask. Her expression morphs from a smile to a frown, I begin to question if what I said was misleading. After a moment, I realize that her face wasn’t of anger or disappointment, it was of fear. ``What’s wrong?'' I ask slowly. In the back of my mind I begin to wonder if someone came in and was just watching us sleep. We would’ve heard them break in, right? Unless... they have a key. They could just walk in without a care in the world.
\newline
\tab
``Turn around,'' she says quietly. I don’t want to, but I don’t think I have much of a choice.
\newline
\tab
Gradually, I turn my head. A wave of relief washes over me, as I don’t see anyone else in sight. This wave evaporates as my gaze focuses on the statues. \textit{They’ve moved}. Rather than facing the walls, they’ve turned towards us with outstretched hands, crying. ``Did they...?'' the thought won’t finish. I don’t want it to finish. I don’t ever want to imagine the idea of it being true.
\newline
\tab
``Let’s go,'' Andraste almost whispers, probably recognizing my fear, or sharing it. I nod and we get up slowly, our eyes glued on the statues. They don’t move, continuing to reach towards the place where we slept. ``I’d rather not sleep here again today.''
\newline
\tab
We walk out of the room, closing the door on the way out and immediately looking back to see if the statues moved again. They didn’t. ``I really don’t want to be here right now,'' I say slowly. I’m not sure if going outside is safe or not, but currently, I want to be as far away from these statues as possible.
\newline
\tab
``Do you want to go outside?'' she asks hesitantly.  There is no good answer to that question. We still have no idea where the other person is. We have no idea if they even came to the school yesterday, or if they’re here right now.
\newline
\tab
I nod. ``Let’s... let’s go outside,'' I say after a while. ``It’s probably risky, but with the statues everything becomes risky.''
\newline
\tab
``It also gives us an opportunity to find other food sources as well,'' she says. ``The garden will need some time to grow back. I’d also rather not go to the cafeteria if possible -- at least for now. If someone is here, that’s the most likely place we’d find them, right?'' I nod, mostly to hurry up and leave the school.
\newline
\tab
We move towards the main exit. ``All the statues seemed to have turned around.'' I say as we pass by the main office.
\newline
\tab
``Wait,'' she says, suddenly coming to a stop. ``Let’s go back to where we got the journal. I think...'' she trails off.
\newline
\tab
``What, Why?'' I respond. ``Let’s just leave the school for now, we can come back later today.''
\newline
\tab
``You don’t see it?'' she asks me, almost annoyed, as if I’ve missed something completely oblivious. ``Where are all the statues facing?''
\newline
\tab
I turn around slowly, trying to recall where each statue was facing before we fell asleep. I genuinely don’t remember. Thinking back to the statue where we found the journal... ``They turn towards us when we sleep?''
\newline
\tab
``Probably,'' she seems way too calm for the situation. It doesn’t really help my mental state, thinking that I’m the only one of us freaking out.
\newline
\tab
``It was a virus that did this, right? If this happened after the symptoms went away, what caused them to all be crying? It’s more reasonable that they’re faces would turn after, right?''
\newline
\tab
``Well, maybe not reasonable, but considering they moved...'' Standing here posing questions about the statues isn’t getting anything done, but the fact that none of them have moved again so far is mildly reassuring. I’m starting to actually believe they can only move when we’re asleep.
\newline
\tab
We continue onward, leaving the school from the main hall. There are statues everywhere, all of them either crying or about to cry wile facing towards the school -- towards us -- with outstretched arms. Sometime clicks in my head as they all stare towards us. I turn to Andraste, whose eyes tell me she’s thinking the same thing I am. ``Their arms are all reaching towards us, so what happens if they touch us?''
\newline
\tab
I pull out the journal and flip to the last entry. \textit{I still wouldn’t go around touching them}. The text stares back at me with an arrogance gained from either omniscience or disaffiliation. ``Did... did they know what happens if someone touches the statues? Did they know the statues move when --''
\newline
\tab
``No, they probably didn’t,'' Andraste cuts me off. ``This is just an idea, but what if they can only move when \textit{everyone’s} asleep. Outside of us, there’s probably only a few other people who are here since the school seems to be taken care of. That would mean that the statues only have to wait for, let’s say five people to be asleep, compared to seven billion. If I’m right, the people probably never would’ve realized that the statues could move, since there would always be a few people awake every few kilometers,'' she begins developing this idea, but something about it feels off.
\newline
\tab
``That doesn’t explain why they all turn towards us though.'' I reply. Talking about this is only making me more and more uncomfortable. ``Let’s look through the city.''
\newline
\tab
She looks at me, feeling as uncomfortable as I do, and nods in agreement. We leave what was once school property and begin to explore the city. The city is clean; perfectly. There’s no garbage in sight. Garbage cans and recycling bins are all empty, having no stains from garbage that might’ve once inhabited it. We continue walking, passing by an alleyway everyone used to avoid. It’s clean, perfectly. The sun’s light passes through it in ways I had never assumed possible. The places we were taught to avoid as children due to frequent assaults, along with occasional rapes and murders, now look like the rest of the city, purged of the stench of despair and regret. ``The city... it’s...'' she trails off.
\newline
\tab
``Clean,'' I complete. ``Everything’s clean.'' There’s something off about this place. I begin thinking out loud. ``There’s no way one or two people could keep an entire city clean like this. Things should be, at the very least, overgrown somewhere, right? For the city to be kept this clean... there would have to be a group of people actively keeping everything clean, but --'' 
\newline
\tab
``There isn’t.'' Andraste says, cutting off my thoughts.
\newline
\tab
``How do you know?'' I ask, wanting to confirm my assumption.
\newline
\tab
``Think about it. If there were people here, we would’ve seen them or heard at least one person, right? If they only move at night, the statues wouldn’t have turned towards us, since other people would’ve been awake.''
\newline
\tab
``That’s assuming they can only move when everyone’s asleep though. We still don’t know if that’s true yet.'' I reply, unconvinced. No, that’s not right. Andraste’s probably right, but that only leaves one other possibility as to who’s been cleaning everything. I don’t want to that end up being true. What was that saying? \textit{Better the devil you know than the devil you don’t}.
\newline
\tab
``If there were others...'' she takes a deep breath before continuing, ``why do the statues all turn to us?'' I stop talking. There’s still a chance that there are other people here, but if there are, there’d be something different about them that makes the statues ignore them.
\newline
\tab
``Let’s go into that grocery store. There’s probably a few things we could salvage.'' I say, pointing.
\newline
\tab
``It’s been two years since anyone’s worked at the grocery store -- or worked anywhere -- chances are all the food’s expired,'' she says. ``Besides,'' her voice gets softer. ``There’s gonna be statues there as well. At least here we’re out in the open.''
\newline
\tab
I put a hand on her shoulder. ``Don’t worry,'' I say, ``we’ll be together.'' Her eyes tell me that did nothing to lessen her fear, but there really wasn’t anything else to say. It wouldn’t be fair to tell her that everything would be okay. We walk into the store. There are statues at every register, and some scattered throughout the rest of the store, but they all seem to be wearing an employee uniform. The only statues here are staff. I choose not to say anything. I’m sure she’s noticed by now, but she’s already unnerved. I walk over to the produce aisle with Andraste following quickly behind me. ``Nothing here looks --'' I pick up an apple and bring it closer to my face -- ``or smells expired.''
\newline
\tab
I take a bite out of the apple. Andraste screams at me. ``What the fuck do you think you’re doing\textinterrobang What if that was --'' I cut her off, not wanting her to worry about anything for the time being.
\newline
\tab
``It’s fine! Here take a bite.'' I attempt to hand her the apple, but she moves around me and grabs her own.
\newline
\tab
``If there’s something wrong with this, I’ll kill you,'' she says playfully. I begin laughing. We sit down on the clean floor, laughing, eating, and enjoying ourselves in this anomalous world. I know it won’t last. When compared to survival, even without the thought of someone or something trying to kill us, having fun holds so little importance that there’s no point in even thinking about it.
\newline
\tab
I look at the sticker on the apple. \textit{Best Before Jan $1^{st}$, 2021}. I stop eating, causing Andraste to look at me quizzically. ``Is something wrong?'' she asks. Her tone is almost lacking the recognition of abnormality.
\newline
\tab
``Look at the expiry date.'' I say slowly.
\newline
\tab
Her head drops towards the apple. ``20...21?'' she asks -- more to herself than me. ``That can’t be real, right?'' she turns to me with a face of confusion and fear.
\newline
\tab
``It explains why they’re edible... kind of. Let’s go look around the store some more.'' I say, trying to take both my mind and hers off yet another anomaly, though I doubt this store will get any less anomalous. 
\newline
\tab
We walk around the store some more, noting that every expiry date for every item is January 1st, 2021. Every item is arranged perfectly symmetrically. Nothing looks squished or haphazardly placed. All items seem like they were each individually placed with care. A couple of them even look like they should fall right off but remain as inanimate as the statues -- at least for now. We walk towards the meat section. Everything is perfect, it feels like -- ``A utopia...'' Andraste’s words cut me off. ``It feels we’re alienated from a utopia.''
\newline
\tab
``Let’s grab some meat to bring back with us.'' I suggest.
\newline
\tab
She looks at me mildly suspiciously. ``Can you cook meat?'' she asks skeptically.
\newline
\tab
``I... uh... probably. How hard can it be?'' I reply with what I’m starting to see as a withering hubris more than anything else.
\newline
\tab
``You don’t sound confident whatsoever,'' she spouts while giggling. It takes her a few seconds to regain her composure. ``what kind of meat do you want to get?''
\newline
\tab
``I don’t really know. Get something that’ll be easy to cut into strips, I guess.'' I reply. ``Do you want to try using the deep fryer?''
\newline
\tab
``I guess the risk isn’t nearly as big as we initially made it out to be,'' she says, more to herself than to me. ``It’s probably fine, right?'' she responds after a moment. Turning back towards the meat, she pulls a package of steak from the back. ``This works, right?'' I nod. We continue to walk around the rest of the store, now looking more for things to buy -- or I guess just take -- rather than scouting for new anomalies.
\newline
\tab
``Let’s head back now, that’ll give us some time to prepare the meat. We can head past the produce section on the way out to get some more vegetables to cook with.'' 
\newline
\tab
She turns to me with a dramatic shock on her face. ``Are you perhaps planning to actually cook something?''
\newline
\tab
There’s a fear behind her eyes that she’s trying desperately to hide. It’s almost as if she’s thinking \textit{if we pretend things are fine everything’ll go back to normal}. I can’t really ignore that, especially now that I’ve seen it -- at least, I think. ``I can cook perfectly fine, thank you very much,'' I respond with equal dramaticism. In her eyes, I can see it didn’t help. She saw my intent. 
\newline
\tab
``Thanks,'' she whispers softly. I pretend not to hear it.
\newline
\tab
We walk back towards the entrance of the store, almost pausing at the cash register. ``I feel like we’re just blatantly steaking,'' I say as a surge of guilt washes over me.
\newline
\tab
Andraste turns to me. ``The statues block all forms of data transfer, right? Even if we had a credit card, I doubt it’d actually work. Even the barcode scanner probably doesn’t work,'' she turns towards me, now grinning. ``It’s not stealing if nobody finds out, right?''
\newline
\tab
``That’s not... Have you ever stolen something before?'' I ask as we walk past the cash register.
\newline
\tab
``You have.''
\newline
\tab
``No I haven’t. When?''
\newline
\tab
``You stole that dead girl’s diary,'' she says teasingly. ``Reading someone else’s diary without their permission is like 7 different kinds of red flags you know.''
\newline
\tab
I grin. ``You should’ve told me that before I read your diary.'' 
\newline
\tab
She doesn’t respond past that. Part of me thinks that I might’ve gone to far. The rest of me wishes that were the reason she fell silent. Both of us realize that the teasing doesn’t help the situation. All we’re doing is distracting ourselves from something we can’t afford to be distracted from. We don’t have the luxury to truly feel normal right now. ``Let’s go back to the school.''
\newline
\tab
We make our way directly to the cafeteria and begin to prepare the food. Since there’s really nowhere to store the food, everything we took from the grocery store has to be eaten as soon as possible or it’ll go bad. ``Start chopping the meat into thin slices. It’ll start preparing the vegetables.''
\newline
\tab
``What are we making?'' she asks half sarcastically.
\newline
\tab
``I’m thinking we fry almost everything and just eat it like a wrap.''
\newline
\tab
``A wrap? We didn’t get bread How are we meant to eat it like a wrap?''
\newline
\tab
I turn the faucet on, letting the water rush out and onto my fingers. ``That’s what the lettuce is for.'' All of my confidence is met with a glare of pure skepticism and doubt.
\newline
\tab
The meat is cut into thin strips that look almost like bacon. We dunk them in the deep fryer along with small chunks of other vegetables -- peppers, onions, carrots, and a few other things. After waiting a minute while everything cooks, we fish them out and put them on a leaf of lettuce. It’s not as good as I expected. Oil pours out of the food, burning the inside of my mouth as I try not to yelp in pain. Andraste seems to have no problem eating it. ``This actually wasn’t as bad as I expected,'' she says as I struggle to eat without incinerating my mouth. I choose not to respond.
\newline
\tab
We finish eating and leave the cafeteria. I stare back at the clock on the wall. 13:56. I turn back to Andraste. ``What do you want to do now?''
\newline
\tab
She thinks for a moment as we slowly walk back to the main hall. ``Let’s look into a drug store. We’ll probably need vitamins, and it wouldn’t hurt to get some medicine or painkillers either.'' We walk about twenty minutes to the closest drug store and find the exact same thing. No customers, only employees -- or I guess they’re just statues. Every item has a bets before date of January 1st, 2021. Everything seems placed with extreme care and in a way where all items are entirely symmetrical. We walk through the aisles and find a few containers of various vitamin pills, which Andraste picks up and puts in her bag. ``You really seem used to stealing.'' It takes me a few minutes before I realize that I had said that out loud.
\newline
\tab
She turns to me, repeating the joke she said at the grocery store. ``It’s only stealing if you get caught.'' I really hope that’s a joke, but I guess it doesn’t matter now anyway.
\newline
\tab
``That’s not suspicious whatsoever,'' I reply dramatically. She laughs it off and we begin to walk out of the store. Something catches my eye and I pause by the checkout counter. ``Hey,'' I say slowly, tapping Andraste’s shoulder.
\newline
\tab
She turns to me in a much more casual way than I expected. ``Yeah?''
\newline
\tab
``Look at the magazines,'' I say. They’re all completely black, except a title. White pages, the only writing on them is a black magazine title in a Times New Roman font. Even weirder, the title isn’t centered, but is aligned to the right of the page.
\newline
\tab
She picks one up and flips through the pages. ``There are only titles,'' she says, extremely unnerved. She drops the magazine and we head back to the school.
\newline
\tab
``There was... no smell.'' I say, thinking back to the drug store. ``They typically have that smell, right?''  She looks at me with pure confusion. ``They typically smell like worn-out hospitals'' I say, unable to come up with a better way to describe it.
\newline
\tab
``Oh!'' she replies, as if having a minor epiphany. The fact that my simile made sense surprises me. ``The smell of different medicines all mixing together. Yeah, that is odd. I didn’t notice it either,'' she pauses for a moment. ``You called it a worn-out hospital?'' she asks laughing.
\newline
\tab
``Am I wrong?''
\newline
\tab
``Kind of. Do you want to go to a hospital and find out?''
\newline
\tab
``Not really.''
\newline
\tab
``So we’ll go with yes; you’re wrong.'' With her mundane victory complete, we head back to the school, which feels like it’s on the other side of the city. Before actually getting back to the school, Andraste turns to me. ``What do you want to do for dinner? We’ve really only had one meal today.''
\newline
\tab
``I hadn’t actually considered that'' I respond, not really feeling that hungry to begin with. ``Do you want to head by the grocery store again?''
\newline
\tab
``I really don’t want to prepare anything myself though...'' she replies, trailing off into thought.
\newline
\tab
``We could stop by the grocery store and see if they have ramen cups or packaged sushi. Those don’t really take any preparation.'' 
\newline
\tab
``We could stop by the grocery store and see if they have ramen cups or packaged sushi. Those don’t really take any preparation.'' 
\newline
\tab
``What are we, college students?''
\newline
\tab
I know it was meant as a joke, but I can’t help but think that I’ll never be able to go to college or university. ``We’ll never be college students.'' I mumble out. She looks at me sympathetically. ``Sorry,'' I say, smiling at her. In her eyes I see a distant hint of alienation. It’s almost as if she doesn’t realize that we’re in the same situation. 
\newline
\tab
We walk back into the grocery store. Near the back, we find a selection of gas-station sushi packages. We pick up two packages, along with a few apples, which I put in my bag, and leave the store for the day. ``Are we staying in the same room as last night?'' she asks.
\newline
\tab
``I don’t see why not. The thermite is still there, so we won’t have to set anything up aside from the blankets. Besides, it’s already fairly late. It’ll be more convenient.'' I don’t really think the thermite’s going to be that useful, but the idea that something can protect us is nice to have.
\newline
\tab
We get back into the school and Andraste turns to me. ``The statues will be facing where we sleep. Are you going to be okay?''
\newline
\tab
``They didn’t actually move, right? They just turned around. It’ll be fine. There’s not really any threat from them.'' I do my best to reassure her that I’ll be fine. I’d rather not have the statues watching us as we sleep, but there’s no reason to make her needlessly worry. We enter the classroom and set up our makeshift beds. I look up at the clock as I open my sushi. ``01:56? Doesn’t that seem...''
\newline
\tab
``That doesn’t seem right,'' she says, opening her container of sushi as well. She looks out the window. ``The clock itself doesn’t seem inaccurate. Look outside.'' I turn my gaze to a pitch-black window. ``Something does feel off though.''
\newline
\tab
We finish our sushi and head to sleep, leaving the apples for tomorrow. I do my best not to look at the statues and to keep them out of my mind. As I stare up at the ceiling, I think back to the journal. There’s still so much we don’t know about the statues. We don’t know how they turned to us. We don’t know if they only move when we’re both asleep. We don’t know if they can move freely or not. We don’t know why everything’s so clean.  \textit{We don’t know anything}. I’m not sure how much time I actually spend thinking about this, but I’d guess about two hours before I fall asleep. 
\newline
\tab
I wake up, not knowing what to do. I don’t want her to wake up to this, but we don’t really have a choice. Fear takes full control of my body. I don’t know what to do. I don’t know what to do. I don’t know what to do. I don’t know what to do. I don’t know what to do. $\mathpzc{Someone\, Help\, Me}$. I stare up as my metallic face stares down at me. Grinning. Their smiles look almost impossible. It’s as if they were sculpted without knowing the full range of a smile. Adrenaline floods through my body and I turn and shove Andraste, quickly waking her up. It takes her a couple of seconds to fully understand the situation. She screams. We sprint out of the room with only our bags. ``What th... what the fuck was that\textinterrobang'' she yells. Andraste falls to her knees and bursts into tears.
\newline
\tab
``I don’t know... but those aren’t the same statues that were in the room before us.'' I look back through the classroom door’s window. The crying statues are still by the wall. They don’t seem like they’ve moved whatsoever. I reach into my bag to get one of the apples we took from the store. ``What?'' I pull out a brown spheroid of congealed... gunk. I drop it onto the floor, and it splatters everywhere. ``What happened to the apples?''
\newline
\tab
``These have no smell,'' she says softly. ``whatever it is, it doesn’t have a smell.'' Things are just getting weirder and weirder. I begin walking towards the door. ``What are you doing\textinterrobang'' Andraste shouts at me.
\newline
\tab
``Don’t worry, I think these... counterparts... work the same way as the normal statues.'' It feels mildly bizarre to call them normal, but there’s no point in thinking about that right now. ``They haven’t moved at all since we’ve woken up. I’ll be fine.'' Even though I’ve said that half my attention is still on the statues. I open the door. There’s no signs of damage on either side of it. I walk in. The windows are still locked and there’s no break in the line of thermite. I can’t see a way they could’ve gotten in. Did we forget to lock the door? I’m pretty sure it was locked before we went to sleep. I walk out of the room, not having crossed the thermite border. ``I have no idea how they got in,'' I confess. ``The door was locked. There were no marks on the door. The line of thermite wasn’t damaged. The windows were still locked...''
\newline
\tab
``For now, we still need food, among other things. Let’s head back to the grocery store and --'' I cut her off.
\newline
\tab
``Let’s go to our houses,'' I say, unable to take my mind off the smiling statues. ``Those were this world’s version of us, right? We might be able to learn something about them if we go to our --'' I correct myself. ``Their houses.''
\newline
\tab
``I’d rather not see my parents and siblings as statues,'' she says, staring at the floor.
\newline
\tab
``You might not have to. If everyone were home, the school would be empty, right?''
\newline
\tab
She nods slowly, getting up on her feet. ``Let’s at least get some food first.'' 
\newline
\tab
We head to the grocery store and get some food. Everything seems to have reverted back to the way we first found it. It’s as if everything we took was replaced or put back -- perfectly. We head for the sushi again. ``This doesn’t taste like something they’d sell at a gas station or grocery store,'' Andraste says, turning towards me. ``I’m not sure how I didn’t notice yesterday, but this tastes like it was made in a high-class restaurant.''
\newline
\tab
``Really, you can tell?'' I ask, mildly doubtful. ``I can’t really taste the difference, though it’s been a while since I’ve gotten sushi from a restaurant.''
\newline
\tab
We finish eating our packaged, restaurant-grade sushi and begin walking towards my house. Just in case her siblings or parents are home, I’d rather not want to freak her out any further. ``We’re here,'' I announce. \textit{This isn’t it. This isn’t my house. I have no memory of ever being here.} $\mathpzc{This\, isn’t\, my\, home}$. I turn away from Andraste and walk up the steps towards the door. Andraste remains at the driveway. I don’t ask why. I’m too focused on suppressing the feelings of nostalgia and homeliness. I open the door, almost falling onto my knees. Every surface, every wall, even the floors and ceilings have the words ``welcome home'' written in a dark red. I can feel the blood drain from my face. I slowly take a step in. Every family photo we took and framed doesn’t have people in it. It’s just framed landscapes. Even the people that were in the background are no longer there. I back out of my -- no; the -- house and shut the door. I try to walk down the steps, but my knees give in and I fall.
\newline
\tab
Andraste rushes up and catches me. ``Are you okay? What happened? What did you see?''
\newline
\tab
I don’t have the energy to respond properly. ``Let’s head back.'' I mutter.
\newline
\tab
We walk back to the school, with her half-carrying me. When we get back to the room, the counterpart statues are gone. She lies me down on one of the makeshift beds and places a hand on my forehead. ``Rest here. I’ll stay up and keep watch.'' I smile weakly at her and close my eyes. I do my best not to think of that place, but I can’t get it out of my head. What happened? Who did that? Was it the counterparts? It seems like everything we find only raises more questions. I doubt I’ll actually be able to sleep like this. The counterpart’s disappearance fully clicks in my head.
\newline
\tab
The counterpart statues can move when we’re awake. What’s stopping them from coming back here and... I do my best not to finish that thought. Andraste looks down at me. ``Are you feeling better?''
\newline
\tab
I smile. ``A little. How long as it been?''
\newline
\tab
She turns her head up towards the clock. ``It’s been six hours,'' she states. Six hours\textinterrobang\, I feel like I’ve only been lying down here for ten minutes. At most, it feels like twenty.
\newline
\tab
I mutter to myself as I get up. ``What the hell is going on here?''
\end{document}