\documentclass[a4paper, 12pt]{book}
\usepackage[utf8]{inputenc}
\usepackage{authblk}
\usepackage{geometry}
\usepackage{setspace} 
\usepackage{amsmath}
\usepackage{mathtools}
\geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 top=20mm,
}
\newcommand\tab[1][1cm]{\hspace*{#1}}
\newcommand\jquotes[1]{$\lceil$#1$\rfloor$}
\title{An Ant on a Frisbee}
\author{Liam Gardner\\Mr. DeFranco\\EWC4U}
\date{\today}
\doublespacing
\begin{document}
\maketitle
\tab
It was two years ago now. I heard a voice in my head. I was dreaming, though I can’t remember of what. Suddenly, I lost my sight; everything went black. The world around me was deleted. I heard a voice. It was warm and comforting. “You must restore humanity’s honor. Walk a straight path, void of any misleading curvature, and find the hidden walls at the end of the earth.” Imagine waking up to that.
\newline
\tab
As usual for back then, I got up, went to class, listened to a boring lecture on stuff I already knew, fell asleep, got called out by the prof in front of hundreds of students, pointed out the mistake the prof made, and fell back asleep. Then, at the end of the lecture, I would wake up and walk over to the next one. The only difference -- aside from that dream -- compared to any other regular day was that when I was eating lunch, I noticed a group of people outside the campus’ Tim Hortons. They weren’t students here, you could tell since they didn’t carry around that half-dead look in their eyes. They seemed to be talking about something and handing out pamphlets. I finish my sandwich and coffee, walk out the front door to see what all the commotion was about, and am greeted by a cute, warm smile of a girl that looked to be around my age. I can’t remember exactly what she was wearing, this was two years ago after all. She was spouting some nonsense about the earth being flat and other bullshit along those lines. I was going to tell her to screw off and get out of the campus grounds, but I remembered my dream – or at least the interrupted segment. Instead, I asked if we could talk about it later, in a quieter area. She agreed happily and I got her phone number.
\newline
\tab
We dated for around nine months. She was loads of fun in bed, but she was an absolute lunatic. Ever since that dream, flat earth believers kept shoving their way into my life like a circus following me around. That was two years ago. For two years, my life has been infected with people who believe the earth is flat. There’s nothing I can do to get them out.  
\newline
\tab
I gave up trying to fight it. If I’m going to get rid of these people, I’ll probably have to follow that dream. I started with some basic googling and research. As it turns out, the flat earth has existed forever – the theory, that is. Alexander the great believed he would find the end of the earth at Oceanus. "My goal is the end of the world. My destination is the furthest border of the East. I want to behold Oceanus with my own two eyes. I want to leave my footprints at the beach beside that endless sea.” Apparently, that’s a quote from Alexander translated to English, though I doubt its authenticity. 
\newline
\tab
As I continue my day browsing the web like a NEET, I find this interesting post about the geometry of the streets and roads. According to the post, it’s been mathematically proven that all streets come across a point in which they curve ever so slightly.  This mostly happens multiple times per block. It’s meant to help with… gravity? Something along those lines. All I can see are the numbers drawn onto the images of sidewalks and fancy math equations I can neither read nor understand. I don’t have the ability to disprove any of it, so I take it to be true.
\newline
\tab
I feel like a nerd living in their mother’s basement. I spend another day browsing sites that seem to be run by progressively more demented people. I find one reddit post about a guy who claimed he was going to walk to the edge of the “Eatrh” and prove that it’s flat by taking a photo with his phone. That post was from two years ago and is now in reddit’s archives. In the comments there’s a link to an article about his death. The report says that government officials had found his corpse and that he’d been mauled to death by a bear. The government officials said there was no sign of any sort of electronic device present in a 10-kilometer radius around where his corpse was found. The parents of the reddit user said they don’t believe what the government officials said, and they think that the truth about their son is being hidden because he actually found the end of the earth. They think that the government destroyed his phone. 
\newline
\tab
I feel like these are progressing in stupidity. Yet, everything in my body is telling me that I have to find it. That warm voice repeats in my head. The prediction has become a mantra of mine. It’s written in black sharpie all over my beige walls. My maroon curtains are closed. My computer screen is the only thing producing any amount of light. God’s judgment rains downwards onto me like pancake-shaped meteors. I haven’t showered or brushed my teeth in three days. All I’ve eaten are ramen cups. I feel like the only thing separating me from a conspiracy theorist is a tinfoil hat! 
\newline
\tab
My computer dies, and along with it goes my sanity. My room is encased in darkness. There is nothing. I close my eyes. One second has passed. Two seconds have passed. Three seconds have passed. Four seconds have passed. Five seconds have passed. Light shines through my eyes and I can see my room at its full brightness. There is a voice. “You have attracted too much attention. The time has come. You must leave. Now!” It’s the same voice, but that warmth and comfort is gone.
\newline
\tab
I open the last article on my phone and walk calmly to my car. I’m a normal person. Reading more carefully, there’s a place he went when he started on this journey he never came back from. “Fuck!” I run back upstairs and grab a three-litre bottle of water from my fridge. I’m going to be walking for a while. This’ll be important. I input the coordinates of his journey’s beginning into my car’s GPS. Right before I click enter, I realize the government will notice. I pause for a few seconds, replace a few of the digits at the end of the coordinates, and put it into my phone’s google maps. The closest thing that comes up is a park called KUR. 
\newline
\tab
The park isn’t found by my car’s GPS. So instead, I set it to the Burger King 1500 metres away from the park’s entrance. One second has passed. Two seconds have passed. Three seconds have passed. I drive away. A thought occurs to me. One that brings a great deal of fear into my heart. 
\newline
\tab
\textit{That was the last time I’ll ever be home.}
\newline
\tab
The article described this guy’s strong beliefs that the earth – which on his reddit post was occasionally spelt “Eatrh” – is a flat disk whose edges used to have an almost endless amount of fresh water. It was almost like ramblings of a madman, yet it all seemed freakishly believable. This is either the charisma of a cult leader or it’s all true. He goes on to say how the world governments all made a pact to withhold information of the shape of the earth among other things from their civilians to preserve a common education and to hold a substantial amount of power over their people. Like a fifth-grade math teacher, denying the existence of imaginary numbers because they majored in politics and don’t want to explain something to a curious child when they know it’s too complicated for the child to understand. Instead they tell the child it’s impossible and doesn’t exist. 
\newline
\tab
The governments froze massive mountains of ice around the ends of the world to provide the illusion of a spherical planet – which actually is backed up by mathematics. I don’t know how, but the math actually makes sense to me now. 
\newline
\tab
I park my car. According to a few follow-up articles, it should be about a two-day’s walk to reach the end of the world. And so, it starts. 
\newline
\tab
\textit{This is the end of my life, isn’t it?}
\newline
\tab
KUR is a long forest that seems to stretch on forever. I leave my car behind at the Burger King, in fear of attracting attention. Many families and groups of people seem to be floating around the area and exploring bits of the forest. The three-litre water bottle is concealed within a backpack. I don’t look out of place.  
\newline
\tab
Continuing my journey, I watch as many groups of people turn back before me. There was an uncountable amount of people at first. Then it faded to probably around twenty. Not long after, it became five, then three. After a while, I was alone. I continue down this bout of reality – or insanity – alone. For hours on end. By the time the sun starts setting, I get a phone call from an unknown number. Hesitantly, I answer it. 
\newline
\tab
“Hello? Are you Alex?” It’s the voice of some man I’ve never heard before. Fear engulfs my body. The government could easily be tracking my phone.
\newline
\tab
I hide any and all fear deep in my heart and respond confidently. “Yes, may I ask who’s speaking?” 
\newline
\tab
“Do you know \underline{\hspace{2cm}}? You’re her emergency contact. She was just hit by a car. The ambulance is coming, but I think it’s fatal. I’m so sorry.” 
\newline
\tab
I can’t hear her name. I hear static. There’s nothing. She’s nothing. They’re all fake. She was created to die after she’s been used. Her name escapes me. She never existed. One second has passed. Two seconds have passed. I throw my phone to my left as hard as I can. It doesn’t hit anything and I can still hear the man on the other end of the phone call. 
\newline
\tab
“Hello? Hello? Are you there? Alex?” 
\newline
\tab
His voice faded to static. He didn’t exist either. I continue walking, taking the water bottle from my bag and drinking a large swig. It’s night now. I need to take my mind of things. I explore the idea of what a flat earth would be like. 
\newline
\tab
An ant on a frisbee. A kid left it on the ground at light and the ant crawled onto it to sleep. It woke up the next morning on the frisbee, but something was different. The frisbee was flying through the air. The ant desperately held on, knowing its world was shifting. The frisbee was caught by another child and thrown back. Desperately, the ant held on for its life. Eventually, it grew tired and could hold on no longer. It flew off the frisbee at an incredible speed and collided with the concrete ground. No damage could be seen on its body, but its brain was crushed by the force of the impact. That frisbee killed the ant, just like it killed me. 
\newline
\tab
Everyone’s name escapes me now. I’m slowly losing their faces as well. All I can see are blurs. All I hear is static. I fall asleep, but my body continues walking. I am awake, and I continue walking. I can’t tell if it’s night or day anymore. One second has passed. I am awake. I take another swig of water. I’m hungry, but I can't stop walking. I should have eaten at the McDonald’s when I parked my car. 
\newline
\tab
I start thinking about ways to describe what the governments have done. It was described in the article written by \underline{\hspace{2cm}}. 
\newline
\tab
\textit{Oh, right. He doesn’t exist. }
\newline
I think it was described as something along the lines of God telling Adam and Eve to avoid the forbidden tree because that’s where he secretly hides all his pornography. I wonder as to why I can remember the names Adam and Eve. I can’t see any particular reasoning as to why they’d be special.
\newline
\tab
\textit{They’ve always been fake, so I guess it doesn’t matter.}
\newline
\tab
I consider my own name. It takes me a few seconds to remember, but when I do, I say it out loud with an enthusiasm I thought I had lost. 
\newline
\tab
“My name is Adam!” 
\newline
\tab
There is no one to hear my voice. I don’t know that. Eve will always be with me. She’s just behind me a few paces. I can’t turn around, but I know she’s been following me since the very beginning. She’s always been here, in this forest with me. We’ve always been in this forest together. It’s like we’re ants on... on a flatbread! 
\newline
\tab
Two ants walk sneakily onto some flatbread dough, just before it goes into the oven. One ant turns to her friend and says “How long do you think it’ll take for the humans to notice us?” They were never noticed. Into the oven goes the ant and her friend. As they sit, watching the humans from inside the oven, they laugh and laugh and wait for the humans to finally notice them. The ant turns to her friend, just as she’s about to make a joke, she realizes her friend is not there. She doesn’t scream, for her friend was never there to begin with. The ant embraces the heat and from her death, the flatbread is complete. When it was ready, the humans pulled the flatbread from out of the oven, promptly gasped about the baked ant that laid atop it, and threw out the bread.  
\newline
\tab
\newline
I want to turn around, and see Adam following behind me; but I’m not allowed. I take my last swig of the water. There’s no more of it. That was the last time I’ll ever drink something again. There’s nothing left for me. I’ve reached the end of the earth. There’s nothing here but me. There’s nobody here but me. I put down the empty water bottle. Using my nails, I carve my legacy into the tree that stands before me. The forbidden tree, now tainted with my name. 
\newline
\begin{center}
\jquotes{My Name Is Eve}
\end{center}
\end{document}