\documentclass[a4paper, 12pt]{book}
\usepackage[utf8]{inputenc}
\usepackage{authblk}
\usepackage{setspace} 
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{geometry}
\geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 top=20mm,
}
\title{Desolate Fugue}
\author{Liam Gardner}
\date{\today}
\doublespacing
\newcommand\tab[1][1cm]{\hspace*{#1}}
\begin{document}
\maketitle
\tab
I awake from that dream, covered in the sweat of a thousand sorrows. I turn over to my nightstand, grimacing as my body weight shifts onto a small gash on my arm. Grabbing my phone, a world of unwanted colour ignites in a bright explosion. 05:43. Tuesday, April 26, 2016. I don’t want to get out of bed, but I doubt I could ever actually remain comfortable in a sea of my sweat.
\newline
\tab
I get up, stripping my bed of the dirty sheets and tossing them to the ground. Nobody else is awake at this time. I wander through a long corridor over to the bathroom, brush my teeth, and hop in the shower. I turn on the shower and stare at the ground, temporarily forgetting where I am. After a few minutes, the room becomes engulfed in a mist. As beams of searing water collide against my back, I contemplate that one recurring dream.
\newline
\tab
A raining night. Waves crashing against a nearby cliff. Thunder erupts in the dark clouds above. As the rain pours onto us, I hold him close to my chest, kneeling on the stone ground. In a silent smile, he lays motionless in my embrace -- dying. His long green hair slowly begins to reduce to clay, along with the rest of his body. I turn my gaze to the sky and whisper something in a language I don’t speak nor understand. All that’s left is my arms are chunks of clay. He’s gone.
\newline
\tab
I turn the shower off, dry myself, and walk back through that long corridor in an attempt to find clothes. Returning to my room, I find half an hour has passed. After packing my bag, I make my way to the front door and leave for school. Nobody’s awake.
\newline
\tab
The bus stop isn’t far from my house and it doesn’t take long before I’m on a bus. There’s almost nobody on. I blink. My eyes close and open so quickly it’s not even worth considering them to have ever closed in the first place. Yet, in that instant, the world changed. Holding one of those metal poles built for people who can’t control their balance, I watch as ghost-like, colourless, skeletal fish swim through the sky-blue ocean of a bus unassumingly. From what seems like miles away, bubbles appear from the other seats on the bus. It doesn’t take long before the bus stops again to pick up more people, and the world returns to order. 
\newline
\tab
I’m not sure why it happens, and I don’t have many people I can talk to about it, but ever since I’ve started having that dream, the world will sometimes... shift? Change? No, both of those aren’t right. Whatever it is, it doesn’t happen when I’m around a lot of people -- thankfully.
\newline
\tab
I push my head into the back of my bag and close my eyes. The bus stops announcements blur with the chatter of the passengers. Everything becomes white noise. For a few seconds, I see peace. Tears well up in my eyes, and the coldness of them streaming onto my cheek forces me awake. It doesn’t last longer than a nanosecond, but an overwhelming feeling of loss engulfs my being. Only for an instant, I am paralyzed in a fearful depression. I calm down and get off the bus one stop early. Realizing I haven’t eaten, I walk over to a coffee shop near the school to order breakfast. The sky is pitch-black and aside from two or three employees, the shop is empty. The clock on the wall says it’s 05:43. There’s probably something wrong with it, but I don’t want to bother the baristas with it. I order my breakfast and sit at the furthest point in the shop from the entrance. I start to question if it’ll happen again. There are roughly three people actively moving around the shop, so it probably won’t happen again.
\newline
\tab
Ever since those dreams began, I’ve felt as if something’s been missing from the world. No, that’s not entirely accurate. It’s something that was never there to begin with, and I’ve come to realize it’s inexistence. That’s still off, but it’s the closest I can manage to describe this feeling. I pull out my notebook and write down the letters $\mathcal{MCPSG}$. Random characters I’ve assigned as a way to refer to this feeling. It’s entirely unpronounceable, not even the names of the letters themselves form a nice-sounding word.
\newline
\tab
I finish my breakfast and leave the coffee shop without a word. It’s still dark outside. The sun has yet to show any signs of existing. It’s possible my phone’s clock was wrong. I walk out onto an empty parking lot, lit by blue streetlights. For a second, it feels as if it’s going to happen again. In this dark, open area, the world will change into something I’d never be able to comprehend, and only a moment later, it’ll revert back to normal. I try to brace myself, but it never comes.
\newline
\tab
``Don’t go to school.'' I turn quickly to see who spoke. There’s nobody around. It takes me a few seconds before it clicks in. That was my voice. I feel like I haven’t heard my own voice in such a long time, but I ordered food thirty minutes ago. I can recall speaking, I remember the exact words I said, but I don’t remember hearing anyone’s voice. I go to pull out my notebook, but it’s already in my hand. $\mathcal{WFVNR}$. I don’t remember writing that, nor even thinking of it, but it describes exactly what I’m feeling right now. I flip over to the next page. 
\newline
\tab
$\mathcal{WFVNR. WFVNR. WFVNR. WFVNR. WFVNR.}$
\newline
\tab
$\mathcal{WFVNR. WFVNR. WFVNR. WFVNR. WFVNR. WFVNR.}$
\newline
\tab
$\mathcal{WFVNR. WFVNR. WFVNR. WFVNR.}$
\newline
\tab
$\mathcal{WFVNR. WFVNR. WFVNR. WFVNR. WFVNR. WFVNR.}WFVNR.$
\newline
\tab
It fills the entire page. For some reason, a wave of relief engulfs my body as I look through the page. That is, until I see the last word. Squished into the bottom-right, only one thought fills my head as I look at it. \textit{That’s not my handwriting.}
\newline
\tab
I drop the notebook on the ground and run as far away as I can. I turn my head back as I run, only to find the notebook absent from where it was dropped. When I turn back, I find myself in an unknown alleyway. The sun begins to rise, and a morning glow slowly covers the world. \textit{Wait.} Why is the world brightened by the sun? It should only be the part facing the sun, right? So -- the sound of hissing catches my attention. A thin, black cat stands on a garbage can. Its red eyes focus so much anger onto me, it’s almost as if it were sentient, conscious, like a person. I back away, slowly. Fifteen seconds pass and I begin to realize that I haven’t moved, and neither has the cat. I’m walking without moving as it’s making empty threats in that primitive language of hissing.
\newline
\tab
I stop walking, take a deep breath, and prepare for the worst. I turn around, and just as I begin to run, I find myself at the edge of the city, starting at a red sun hovering over a distant building. As I begin to turn back, just above the sun, and in a shade of blue only slightly darker than the sky, lies the skeleton of a pliosaurus spanning the entire city in length. It takes me a few seconds before I realize that the skeleton has no eye sockets. I begin to wonder if that’s how I’ll end up when this is all over, a misplaced skeleton.
\newline
\tab
Slowly but surely, the skeleton turns towards me. I can feel it staring at me. ``Go home,'' it says to me with a voice as present as its eyes. I nod, turn around and begin walking to god knows where. I wonder if I can actually get back home. Probably not, but I may as well keep walking until I find a place to call home. I sigh, closing my eyes. I can feel them closed, yet I’m on a beach, facing a distant volcano. \textit{This is nothing’s replacement.} The waves crash against my bare feet. It’s cold but refreshing. I feel a mild inability to control my body. I sit there, head on my knees, wondering what it means to be home. I know I woke up today. I know it feels natural to assume that everyone else was still asleep. The more I think about it, the more I realize that I don’t remember what \textit{everyone else} looks like. I don’t even remember who \textit{everyone else} is. 
\newline
\tab
I close my eyes -- even though they’re already closed -- and sigh. I’m not ready to deal with that yet. I open my eyes and unsurprisingly end up in a bar. The maroon couch is rather stiff, but I haven’t lied down in a while and I’m getting tired. I reach into my pocket and pull out my phone.  05:43. Monday, April 25, 2016. I can tell that something’s off, but I can’t figure out what. I put my phone back in my pocket and stare up at the bland, burgundy-coloured ceiling. The manager’s out for the next hour, and the bar’s empty. I can stay here for at least thirty minutes. I feel like so much has happened, yet I’ve gone nowhere. The bell at the top of the door rings, but nothing else moves. I turn my head to see what caused it. On the door are the letters $\mathbb{HQWRP}$. \textit{This again?} I know I’ll have to leave this place sooner than I wanted to. Getting up slowly, I make my way to the door and open it, wondering where I’ll end up next.
\newline
\tab
``You’re gonna have to stop this eventually.'' I look up from my desk and out the window as she speaks. I don’t turn to her just yet.
\newline
\tab
``I know,'' I say softly. ``It’s just... hard.''
\newline
\tab
``We’re all mourning. It’s okay to feel like something’s missing.'' She sits on my bed, staring at the floor. I haven’t cleaned my room in months. I’m sure I have things scattered around that I’d rather she not see.
\newline
\tab
``It’s not just that something’s missing, it’s that everything else is continuing like it never happened.'' I reply, dropping my pen onto the floor. ``I’m sorry, I can’t work on this just yet.''
\newline
\tab
``Don’t worry about it, take your time. You were with him the most, it’s only natural that you write his eulogy.'' It must’ve taken a tremendous amount of effort to say that.
\newline
\tab
``Thank you.'' I reply softly, getting up and moving to hug her. Just as I turn around, the world changes again. 
\newline
\tab
I’ve returned to a city again. Standing in the middle of the road, I look up at a purple comet streaking through the sky. Its tail stretches through the entire sky. I turn my sights forward and begin walking down the road. The lights in the buildings are out. There are no cars in sight. It feels like this place was abandoned. The streetlamps are off too. There’s nothing left in this place. Even a comet as bright and large as the one above me can’t bring people back here.
\newline
\tab
``They’ve grown tired of this place.'' Hearing my voice for a second time now is much less surprising.
\newline
\tab
I sigh. ``So it seems.'' Part of me wonders who I’m talking to; most of me doesn’t care. ``This is so tiring.''
\newline
\tab
``So why don’t you return home?'' A black cat with red eyes walks beside me. It’s slim, almost anorexic. ``You remember how to get back, so why are you still here?''
\newline
\tab
``Home? What makes that place any more of a home than here?'' I turn my head towards the cat as I speak.
\newline
\tab
``He did.''
\newline
\tab
``So why should I go back?''
\newline
\tab
``He’s not what I’m looking for.'' I turn around in an attempt to leave, but I remain in the city of comets and cats.
\newline
\tab
``Don’t think you can get away that easily.''
\newline
\tab
``I need to rest,'' I say, sighing, ``this is so tiring.''
\newline
\tab
I begin to close my eyes. A sigh fills my ears along with two words. ``Go home.'' \textit{We both know I’m not ready for that just yet.}
\newline
\tab
When I open my eyes, I find myself alone, sitting on a bench at the back of a small, lone house at the edge of a forest. Above me is a waning crescent moon slowly dissolving and fading into the blackness of the sky. A band of stars blankets the dying moon as it returns to dust. It’s such a nice night. I want to rest here, but the world is against the idea of my comfort. As much as I would like to lie back onto the grass and close my eyes, I know it will only bring me somewhere else. The dying moon will spend its last moments alone if I leave now.
\newline
\tab
I get up off the small bench and walk towards the house. I know I can’t stay here. I know I won’t be able to sit with the moon until it’s gone. I have to go. I pull out a small tool from a drawer and place it in my pocket. I can’t look at it. I don’t know why, but even though I’m staring right at it, I can’t focus on it. I can’t see it. I shove it into my pocket and ignore it. Walking out of the house, I take one last look at the moon, doing everything I can not to cry. I’ve cried enough already. With that, I walk into the forest. The foliage fills my vision, everything slowly turns black. Right before the world switches again, I think of the moon. \textit{I’m sorry. I’m so sorry.}
\newline
\tab
I’m not fully sure if I’m still in the same place.  At the other end of the forest is a small set of shallow stairs that lead up to a fence blocking a large grey house. The sky is lit just enough for me to see everything. The window curtains are closed. A slow fear starts engulfing my body. I feel the blood drain from my face. \textit{I’m not ready.} I collapse to the ground and close my eyes. \textit{Please, let me leave this place. I don’t want to go back. I’m not ready just yet. I need more time. I can’t move forward. I need more time. Please... someone.}
\newline
\tab
A gentle breeze wakes me from my despair. Of all the places I could’ve awoken to, of everywhere this accursed world could take me, this is the last place I want to be. The sky is clear. The thunder and rain are gone. The waves are calm. The sun shines upon the place where he returned to clay. The world has moved on as if nothing’s happened -- just as I feared. Those words come back to me. That language comes back to me. I don’t want to remember what I said. I don’t want to think about this anymore. There’s nowhere for me to run. There’s nowhere I can go. I lie on the stone ground, staring up at the sky. The sun burns my eyes but that’s nothing compared to what I’ve lost. ``I’m so sorry,'' I say, now crying. ``I’m so sorry we can’t spend more time together. I’m sorry I couldn’t stop it. I’m sorry I’m being a hindrance to everyone. I’m sorry I’m not ready to go back I’m sorry...'' Half of me expects him to sit beside me and comfort me; but he’s not here anymore. He won’t ever be here to comfort me. I close my eyes, unintentionally trapping the tears. There’s nothing left for me here.
\newline
\tab
I’m lying on a park-bench in a cloudy autumn day. The streetlamps and coloured leaves give an orange aura to the surrounding area. The evergreen trees all share a dark-green leaf colour. For a moment, I forget why I’m here. I get off the bench and start walking down the cobblestone trail. A single withered, leafless tree catches my attention and invokes in me all the memories I’ve been running from. I remember why I’m here. I continue down the cobblestone trail, wondering if I’ll ever be able to move on. The trail curves fairly often. The stones are uneven. On either side is a forest of various evergreen trees, semi unsaturated green grass and -- what am I doing? All I’ve managed to do is pile distraction on top of distraction. Is this how people move on? Distract themselves until they’ve run so far that they forget why they’re running? That’s pathetic. I’m not reducing him to a distant memory. I’d rather d -- A notification from my phone cuts off my thoughts. A text message from an unknown number. ``It’s time to go home.'' Sighing, I drop my phone on the cobblestone and continue walking. I was never looking to go home in the first place. I didn’t come here to find him either. I close my eyes. I’m not ready for that just yet either.
\newline
\tab
I sit down at a bus stop in the rain. It’s night again, and the streetlights provide a rather cold shade of white. I think it could be snow, but I’m not sure. It’s getting hard to see what’s around me. I think there’s an apartment complex nearby, but the fog makes it hard to see past a few metres. Jellyfish illuminate the sky. A transparent mushroom-like cap protects a nexus of orange-glowing tentacles. They hover around the bus stop silently and unassumingly, as if I’m not here.
\newline
\tab
I can’t keep doing this. It’s too tiring. My hand moves towards my pocket. The realization of what I’m about to do sets in. It wouldn’t be unexpected, right? Haven’t I already said ‘goodbye’? Why am I hesitating? ``You don’t know where you’re going... where he went... if there is a place. You don’t know.'' The jellyfish facing me is reduced to dust, but those -- my -- words remain in my head. I’m not sure if I’ll see him again.
\newline
\tab
I can see it now. The tool in my pocket. I pull it out and stare at it. The metal reflects the light from the streetlamps. I smile. It feels like I haven’t done that in a while. Instinctively, my eyes close, though I can still see the world around me. It only lasts an instant, almost going unnoticed entirely. As the sound of metal landing on the cold, paved ground fills my ears, I turn to see a red tinge lit by a false moon. Everything’s returned to darkness.
\newline
\tab
``What are you doing?'' His laughing voice asks through the breeze, as I lie on a bed of purple flowers and stare up at the blue sky.
\newline
\tab
``Join me.'' I reply, turning my sights towards him. He smiles. His long green hair waves slightly in the air as he sits down beside me, picking up a flower. ``Did you have any regrets?'' I ask, incapable of looking him in the eyes as I do so.
\newline
\tab
``None.'' He replies, smiling. ``I wonder what they’ll do without us.''
\newline
\tab
``They’re strong; stronger than I am, at least. It might take a bit, but they’ll be okay.''
\newline
\tab
``I know they will.'' He places the flowers on the ground and lies down. ``Living in a small house by a like and a forest like this, it almost feels like we’re in a painting.'' He turns to me and smiles.
\newline
\tab
``It’s so peaceful here,'' I reply.
\newline
\tab
``There’s something off about this place though.''
\newline
\tab
``I know'', I reply. I breathe a long sigh and turn my gaze back towards the sky. ``Just let me pretend this is real for a little while longer.''
\end{document}