\documentclass[a4paper, 12pt]{book}
\usepackage[utf8]{inputenc}
\usepackage{authblk}

\usepackage{setspace} 
\usepackage{CJKutf8}
\usepackage{geometry}
\geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 top=20mm,
}
\title{Emptiness}
\author{Liam Gardner}
\date{\today}
\doublespacing
\begin{document}
\newcommand\tab[1][1cm]{\hspace*{#1}}
\maketitle
\tab
I’m standing outside the bar. What used to be an amazing place filled with power and life has been replaced with a decrepit, run-down, abandoned building. Fifteen minutes from union station by foot, I stand outside the place most people don’t even dare approach. It’s been thirteen years, we’re all… we’re all dead. I close my eyes and walk inside.
\newline
\tab
I don’t want to open my eyes just yet. This place used to be so lively; polished, dark wood cleaned with coke, the stench of alcohol and sweat with a mild sweetness hidden in between. There were people talking over each other, smiling and laughing. If I open my eyes, I know it’ll all disappear. I want to be back there for just a little while longer.
\newline
\tab
The stench of rat shit and mould wakes me up from my dream. I open my eyes to a cracked, broken bar with tipped chairs and emptiness. 
\begin{CJK}{UTF8}{min}
空色 (からいろ). 
\end{CJK}
The colour of emptiness. This place holds nothing anymore. All that remains are memories of another time, another world. I sit down on a half-broken bar stool at a half-broken counter. The lights don’t work here anymore. I pull out my phone.
\newline
\newline
\centerline{Saturday}
\newline
\centerline{February 22}
\newline
\centerline{12:49}
\newline
\newline
Tears flow from my eyes once again. I stain this broken emptiness with depression and melancholy, an unsaturated sky-blue. 
\begin{CJK}{UTF8}{min}
空色 (そらいろ). 
\end{CJK}
It’s the same word, just pronounced differently. This is the difference between nothingness and the sky. Ken taught me that. He taught me how to read and write in this language. Though I never learned much of it, it’s one of the few things I still have to remember him by. There’s nothing left in this place.
\newline
\tab
I leave and get back on the subway. The train doors close but we don’t move. People are starting to get confused. Some are even worried. It doesn’t matter. An announcement comes through the speakers after a while. ``Sorry for the delay folks. It appears there was an unauthorized personnel on track level. The issue will be cleaned up and we’ll be on our way shortly.'' I sigh. Someone died. Another person committed suicide. You can tell in his voice and use of language. Hidden behind an authority and informality, there lies a scared child who can only manage to take short and shallow breaths. He’s scared of death.
\newline\newline\newline
\tab
This class is so boring. I sit down in the back left of the room, furthest from the door and the teacher’s line of sight. I place my arms on my desk and bury my head into them. This class holds nothing for me. I’m smart enough to pass without putting in any amount of effort. Ten minutes into the class I can hear the teacher calling my name. He sounds like he’s trying to coax me into participation like getting an animal out of hiding. I flip him off. I’m no animal. 
\newline
\tab
``Alright, if you’re going to do that, I’ll fail you.''  He says with offense and annoyance plaguing his voice.
\newline
\tab
``Last I checked,'' I start, gazing at him with eyes of authority, ``I have the highest average in the class. How would you explain that if you had a sudden meeting with the principal, or someone \textit{else}?'' My voice is filled with a kind of superiority that keeps the lesser kids away from me. He scoffs and turns back towards the board. ``Oh, there’s a mistake in your answer for problem two by the way.'' I smirk and try to fall back asleep.
\newline
\tab
``Wha…'' He looks at it in shock before hastily fixing it. He leaves me alone for the rest of the class, letting me sleep. There are uneasy gazes from classmates; and gazes of fear from those who know me.
\newline
\tab
The class ends and I head to the subway station. There, I meet up with Ken, and we take the subway to Union, talking and complaining as usual about school. Winter’s just ending even though it’s only March -- or at least it seems like it’s ending. We walk for fifteen minutes, passing by people who move out of the way for us, mostly out of fear, until we arrive at the bar.
\newline
\tab
The door opens to the liveliness one might expect from a mafia. We walk to the front and take a seat at the bar. The wooden counter is polished and clean, giving off a faint smell of something sweet, though I’m not exactly sure what it is. Despite the place being a bar, very few people actually drink here -- at least right now. Customers are forbidden, it’s not a real bar anymore, or at least it stopped being a bar when we inherited it. Money typically comes from desperate people borrowing more than they can pay back and becoming the equivalent of slaves to us. It’s more profitable than I’ve made it seem -- I can’t really explain it properly -- and much more profitable than running a bar.
\newline
\tab
I joined more out of boredom than anything else. Ken was already a part of it when I met him. Being my only friend, and having no parents around, it was only a matter of time before I joined. I’m good enough with computers that they have me keep tabs on what our slaves do with their lives on the internet. Because of me, we pretty much have access to every slave’s online presence. Given the right account, we can cause large amounts of damage by typing a few words and pressing send. That’s how pathetic their lives are. One simple post seen by their employers is enough to get them fired from the part-time job that keeps them tied to this life. Once they lose that, they enter a world of all kinds of debt. The only options left for them is suicide or a miracle and I have yet to see the second one play out. I’m passed a laptop and begin working.
\newline\newline\newline
\tab
I get home and open the door to an empty house. The answering machine is blinking. I have a new message. It’s a newer model that performs the same functions as the old retro one yet can also send the messages to yourself as an email and it has the option for voice-activation. I walk over and look at the number. The extension code is +49. My parents called again. They moved to Germany in the summer before my last year of high school because of a stupid job offer. The only reason I didn’t go with them was because they had already paid my tuition and it was too much of a hassle to get a refund. So, they moved without me, and I was meant to come to Germany after I graduated high school.
\newline
\tab
I stare at the machine in hesitation, before finally convincing myself to play it. My mother’s voice comes on. ``When are you going to come to Germany? You can go back to school here. We’ll even pay for your flight over. Your little gang is gone now, yes? So there’s --'' I grab the answering machine and throw it against the wall. It shatters, bits of plastic fly everywhere.
\newline
\tab
``FUCK! Fuck this shit! They were more of a family than you \textit{ever} were. What gives you the fucking right to tell me what to do?'' I fall to the ground, crying. I’m angry because I know I have no choice. I’ll have to fly to Germany. I don’t have the money to keep living here on my own. They’re right. The mafia is dead. A battery from the broken answering machine rolls its way over to me, a reminder of my parents’ orders.
\newline
\tab
When the mafia was attacked and killed, there were only a few that weren’t there. I was talking with Ken about methods of torture used in the medieval times for our history class when the machine gun went off from outside. Bullets flew everywhere. The initial spray was angled to the left of the room, away from us. Two people died then; their bodies riddled with so many bullet holes that all their blood was able to spill out in only three seconds. Some people got guns, others got knives, and a few of us hid and waited either to ambush them or for it to end. I hid behind the counter, waiting for my chance to climb down into the cellar. Ken hid with me, initially. He built up enough anger and range that, despite my best efforts to keep him here and silent, he ran out with a pistol and switchblade. He killed two people before being shot in the leg, allowing the onslaught of the machine gun to finish him off. By the time everything was done, his corpse was unrecognizable. Three people survived. 
\newline
\tab
I hid in the cellar. We had sealed off the original entrance and replaced it with a trap door behind the counter, close to where I was hiding. When I climbed back up, there was a body blocking the exit. That’s probably why they didn’t find me. The other two only survived because they weren’t there. One of them moved countries -- I don’t know to where -- and went into hiding. The other, I haven’t seen around, but I know he’s still here. I took the money we kept in the cellar and ran. I didn’t return until two years later, and still have no idea who it was that took us out.
\newline
\tab
That money, along with a couple part-time jobs here and there, has gotten me to my current situation: thirteen years later and broke. There’s nothing left for me here. This world only holds enough space for people -- humans. I lost my humanity the first time I drove someone to suicide. I’m an accident, A mistake that should’ve been killed along with the rest of them. I am a memory of the most powerful people to ever wander Toronto. I am a memory of the day we lost that power, the day this city became free from us. I am a ghost, forbidden from entering the afterlife, yet incapable of atonement. I am one of many that cry for help in a city that ignores us to make money. This is how I will die.
\newline\newline\newline
\tab
Ken and I are sitting in the library alone at lunch. ``Wanna learn Japanese?'' He asks me, mildly intrigued at what my response will be. He has nobody here to talk to in his own language.
\newline
\tab
``There’s nothing else to do. Sure.'' I reply mostly out of boredom -- that’s typically the reasoning behind all of my actions. I spend the next hour learning basic hiragana, katakana and a small portion of kanji. He teaches me the fundamentals of his language like I’m in kindergarten, which greatly amuses me. I spend the next few days practicing during classes. I learned enough to talk with him about most things. It’s really convenient to be able to complain about someone behind their back when their right beside you and have no idea what you’re saying.
\newline
\tab
For the next few days, I would get home, study my coursework and Japanese for twenty minutes, and spend the rest of the time figuring out which one of the slaves is least likely to pay us back. I found one person working at Tim Hortons and living with their parents, Eve. Her parents are very religious, as well as her boss. That should be fun to take advantage of. I’ll have to meet with her one last time to see if she’ll actually be able to pay it off -- which I know she won’t, but it’s always good to check. It seems as if she gets off work in an hour. I’m not much on my own, but at least I don’t seem threatening.
\newline
\tab
I take the subway to Finch station and catch her getting onto an empty train. I sit down beside her, mildly annoyed that I couldn’t get there early enough to buy coffee.  She notices me and quickly figures out my affiliation to the mafia. ``So, when do you think you’ll be able to pay us back?'' I ask apathetically, staring out the window.
\newline
\tab
``I can have it by the end of the year. I’m coming up on something big, trust me, please.'' She’s staring at me with eyes of desperation and a voice of hopeful fear.
\newline
\tab
``We trust in results, not words. You have until the end of the month to show us you can pay us back.'' I say, the subway approaches my stop and I start to stand, preparing to leave the train.
\newline
\tab
``Wait! Please wait! Give me more time! I need more time!'' She’s started to scream, attracting the attention of the other people on the train. I look around discretely using the reflections in the window. Some people know what she’s going through and show sympathetic gazes. Others are going through the same thing and look at me with fear in their eyes, hoping I don’t see them. The door opens and I get off. She’s still screaming, I ignore her and head home. I’ve displayed my authority. I hold the power in this situation, not anybody else.
\end{document}