\documentclass[a4paper, 12pt]{book}


\usepackage[utf8]{inputenc}
\usepackage{authblk}
\usepackage{setspace} 
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}

\usepackage{geometry}
\geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 top=20mm,
}

\title{The Constellations are not Only in the Skies}
\author{Liam Gardner}
\date{\today}
\doublespacing
\newcommand\tab[1][1cm]{\hspace*{#1}}
\newcommand\nextline{\newline\tab}
\begin{document}
\maketitle
\tab
He made a gesture with his hand. A couple of seconds later he says ``Talk to me. What was it like?''
\nextline
Thinking back to my childhood, I smile. Even after those events, I can only describe it as nostalgic. ``It was fun.'' He looks like he's about to write something in his notebook, but his gaze does not leave my face, and his notebook remains on the table. ``That was my present. I was allowed to use the family computer.''
\nextline
``So, what was it like? Were there any rules, or strings attached?''
\nextline
``What do you mean by `strings attached'?'' I ask I was allowed to do pretty much whatever I wanted on the computer; though, I guess that's probably not true.
\nextline
``What did you do on the computer?'' His voice is calm, and undemeaning. It's different
\nextline
``I went to the church website. Sometimes I would read the ---, other times I would watch the recorded sermons, or learn a new prayer. There were also videos that would explain the passages of the ---.''  I smiled as I recounted most of my electronic memories. He grabs the notebook from the table, turns a new page and begins writing.
\nextline
``You would watch the videos that analyzed the holy texts? ``There's something else in his voice hidden behind verification, but I don't know what it is. I nod. ``What were they like?'''' His voice returned to that state of calm; maybe it was \textit{just} verification.
\nextline
``There were some parts that I couldn't understand, and the videos explained it to me. Sometimes, there were things that I thought I understood, but I had misinterpreted.''
\nextline
``Did you ever think that maybe the priests were the ones who misinterpreted, and that you were right? Or that maybe there are multiple interpretations?''
\nextline
``The priests say there's only one meaning, and since they study --- the most, it makes sense that they know better than I do, right?''
\nextline
He looks at me with verification again. ``Have you ever read the bible? There are some parts of the bible that even the highest priests disagree on the meaning. Christians typically have widely different interpretations of the bible, but each consider themselves to be Christian. That's why there are different types of Christianity.'' His voice seems almost excited.
\nextline
``I've never really interacted much with other religions. My friends were all from the church, and I never had the opportunity to meet many other people.''
\nextline
``Was it because of the homeschooling?'' I nod.
\nextline
``What do you think of that idea?''
\nextline
``I don't think it makes sense. Why would there be completely different meanings to the bible. Hidden meanings make sense, but why would there be two correct ideas that contradict each other?'' I back down and apologize. It was rude of me to disagree with him. He writes something down in his notebook while saying I didn't have to apologize. I don't say it, but I know he's wrong. I was being rude, and when you recognize that you're being rude, you apologize. 
\nextline
``You're not fully wrong. That's why there are different types of Christianity. However, they are all Christian. That's the important part.'' He pauses for a bit and acts like he's waiting for something before continuing. ``Now, back to you. What were your parents doing when you were on the computer?''
\nextline
I think for a minute. This was nine years ago. ``One of them would always sit with me and keep me company. If my father were with me, my mother would be cooking or doing laundry. If my mother were with me, my father was probably working.''
\nextline
``Did your parents ever leave you alone when you were on the computer?''
\nextline
I smile. ``No. They were afraid I'd get lonely.'' He writes something down in his notebook.
\nextline
``Do you think you would've gotten lonely if your parents would've left you alone?''
\nextline
``Probably not,'' I respond. ``They would leave me alone to do homework and I was never lonely then.'' 
\nextline
He scribbles something down quickly before moving on.  ``So, what did you like doing most of all on the website?'' His voice returned back to being calm.
\nextline
``I really enjoyed watching videos that explain the ---. Sometimes I would read it myself, but there were always things I would get wrong or not understand. So, the videos were better for learning.''
\nextline
He put the notepad down. ``Now that we already discussed Christianity – albeit briefly – do you still think that your interpretations were wrong?''
\nextline
I pause for a bit. ``It's not Christianity. It's different. In my religion, there is only one correct interpretation.''
\nextline
His eyes close for a moment. When they open again, there's a different emotion in them, but I don't know what it is. ``Do you still believe in it, after all that happened?'' 
\nextline
I don't want to answer the question. It would upset my parents. It's rude not to answer it though. I don't want to be rude again. I take a deep breath. ``I don't really know.''
\nextline
He smiles. ``Well that's okay. It's okay not to know.'' He pauses for a second. ``I know you say that it's different from Christianity, but let's use it for comparison, is that alright?'' I nod. ``In Christianity, there's a concept of good, and how to be good. We call them the Ten Commandments. They include things like `Don't steal', `Don't hoard or covet', `Don't lie', things like that. Do you remember anything like that in your religion?'' I don't like that he called it `my' religion, but it would be rude of me to say that, so I keep quiet.
\nextline
``We were taught things like `Don't be rude', does that count?'' He smiles and nods. ``We also had things like `Be like Æden', but I'm not sure that's the same idea.''
\nextline
He writes something very long down. ``Let's deal with one thing at a time, okay?'' He waits. I nod. ``Okay. When is something considered to be `rude'?''
\nextline
I spend some time trying to collect all the instances I can think of when someone was being rude, and what they all shared in common. ``Well, it's rude to disagree with someone who knows better than you, but it's also rude not to teach people who don't know things as well as you. It's really rude to disagree with a priest, but they tend to deal with it kindly.''
\nextline
Just before I can continue, he says ``How do they deal with it?'' His voice again seems almost excited for some reason.
\nextline
``After the service, they take you to the cleaning room to clean you. `If your body is clean, your mind will become clean as well', or at least that's what they tell us. The cleaning would always hurt, btu I didn't mind. Other than that, being rude also included things like interrupting people and talking without permission. I think that's it. Oh! But if you recognize that you're being rude, it's very important to apologize.''
\nextline
His face contorts, and suddenly he looks very stern. His voice seems to have lowered in tone a bit, but I don't think it's directed to me. ``When you were being cleaned by the priests, did you have clothes on?''
\nextline
I found it to be a funny question, but given his expression thought it best not to laugh or point it out. I responded as blandly as I could. ``The clothes would get in the way of the cleaning.''
\nextline
He stares at me with that grave look, unwavering. He doesn't write anything, doesn't say anything, doesn't move. He just stares. I start to wonder if maybe I was being rude. I can't really tell what he's thinking; I was never really good at discerning emotions in the first place, but I don't even have a clue right now. I'm scared.
\nextline
``I know this is very unprofessional of me, but may I go to the washroom? I promise it won't take away from the session.'' I can't tell why, but it looked like saying those words took a tremendous amount of effort. I nod, thinking he was worried about the implications of being unprofessional. He thanks me and leaves the room.
\nextline
It's quiet. There's nobody talking, nobody writing. There's no ticking clock. I can't hear myself breath. I can't hear my heartbeat. Everything's just silent. I begin to wonder if I was unknowingly being rude – if this silence is some kind of punishment. I'll have to make sure to apologize when he returns, just in case. I think it's been three minutes now. I don't recall the bathroom being too far away. I really hope that I didn't accidentally say something extremely rude.
\nextline
Two more minutes pass and he return and sits down. He doesn't say anything immediately, but he writes something down in his notes, breaking the silence. ``Sorry about that. I'm not specialized with dealing with cases like yours. I mostly deal with domestic cases and youths. I think it would be best if you transferred to a different therapist, one more specialized in cases like these. I'll send you an email with more information after the session. However, this new therapist would still have to be linked to the incident, so they would likely use the same confidentiality policy.'' He's rambling and stuttering a bit, and I don't know what to say. He takes a deep breath, closes his eyes and waits for around five seconds. ``You mentioned something along the lines of `be like Aiden' right? Can you elaborate on that idea?'' His accent is kind of funny, but it would be rude to bring it up, and I've been rude enough today.
\nextline
I think for a moment. ``Æden was called the ideal man. In one of the passages of ---, he's said to have been made from a constellation, but I don't remember which one. The priests said that when he had children, they were cursed by something and it made them different.''
\nextline
He pauses writing for a moment and looks at me weirdly. ``Different how?'' I didn't notice immediately, but he's writing as I'm speaking, rather than waiting.
\nextline
``They were said to act different, and have different opinions on duty, different likes and dislikes, stuff like that.''
\nextline
``You mean different identities? That they were all unique?'' He asks, interrupting my train of thought.
\nextline
``Something like that. We were taught that everyone's unique and different because of the curse. The priests would always say that we should do our best to be like Æden, and that although we can never get rid of the curse, we can try to make it negligible. We had to read and study the --- every day so that we could do our best to understand how to be like Æden. Otherwise, if people are too different, bad things happen. The priests would say that everything from war to homelessness to drug abuse could've been avoided if everyone was like Æden.'' He looks up at me, so I stop talking.
\nextline
A moment later, and still using that funny pronunciation, he says ``Do you want to be like Aiden?'' I nod. ``Do you want everyone to be like Aiden?'' I nod. ``If that can't happen... if everyone will always be unique. Would you still want to be like Aiden, despite that?'' I nod.
\nextline
``Even if the church was abolished, someone has to try. If not, then there will always be war, and I don't want that.'' His face contorts for a moment but returns to normal very quickly. I think I know the answer to that question he asked me earlier.
\nextline
``We're out of time, but I have one more question. Does the phrase `The constellations are not only in the skies' mean anything to you?''
\nextline
``It's from a passage in ---. It means that Æden exists in all of use, since he was made from the constellations and he, in tern, made us. I think the verses that follow talk about how there will always be someone who sees the constellations and try to void humanity of the curse.''
\nextline
``That's what one of the priests said right before they committed suicide.'' A moment later, he stands up and we shake hands. ``It's been a pleasure.'' And with that, I leave the room for the last time.
\end{document}