\documentclass[a4paper, 12pt]{book}
\usepackage[utf8]{inputenc}
\usepackage{authblk}

\usepackage{setspace} 
\usepackage{CJKutf8}

\usepackage[CJK, overlap]{ruby}
\usepackage{geometry}
\geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 top=20mm,
}
\renewcommand{\rubysize}{0.7}
\renewcommand{\rubysep}{-2ex}
\title{Different}
\author{Liam Gardner}
\date{\today}
\doublespacing

%EXAMPLE FURIGANA
%\begin{CJK*}{UTF8}{min}
%\ruby{黙}{だま}つて\ruby{死}{し}ね
%\end{CJK*}

\begin{document}
\newcommand\tab[1][1cm]{\hspace*{#1}}
\maketitle
\begin{CJK*}{UTF8}{min}
\tab
She stopped moving. It took me a few seconds to notice. I turn around to see her jaw drop and her eyes widened. She looked at me like I had said a really offensive joke and not noticed. I don’t think I could ever explain to someone how hard it was not to laugh. ``Are you serious? You’re joking, right? Come on, that’s not funny.'' I had to pinch myself to stop myself from laughing. ``You know that’s against the Lord’s will.'' I stopped needing to pinch myself. 
\newline
\tab
Her face and body blurred, and I became increasingly aware of my surroundings. The library is ten metres away -- closed. The school is about twenty-five meters away. I noticed the withering green on the tress and the grass next to the sidewalk. A single brown branch with infected leaves. I am no longer holding back laughter. I pull myself back to reality. 「\ruby{黙}{だま}つて\ruby{死}{し}ね。」
I whisper, my emotions have become clear now.
\newline
\tab
``What was that? I couldn’t hear you. Come on, stop joking around and give me a real reason you won’t date me.''
\newline
\tab
``You know what else is against the will of your god? Having pride. Funny, you criticize me for my sexuality yet --''
\newline
\tab
``Stop with the jokes already! Also, don’t say \textit{your God} or \textit{your Lord}. It’s \textit{the Lord}. Now please --''
\newline
\tab
``I AM FUCKING TALKING.'' She turns pale, not from my words but their implications. ``You seemed to have a lot of damn pride talking to your friends about dating and converting me.''
\newline
\tab
``That was…'' She turns her head away from me, towards the road. ``So, you’re really gay?''
\newline
\tab
``No. Now I’m finally going to tell you it was a fucking joke.'' I notice a tiny shimmer of hope that what I said wasn’t sarcastic. ``No shit, I’m gay.''
\newline
\tab
She seems to have sorted her emotions out as well. I can see it in her eyes, she took the same route I did. ``Disgusting faggot,'' she mutters, ``you know nothing of the Lord’s work.''
\newline
\tab
I choose to ignore her first comment. ``Really? I know nothing? I know things from a historical perspective. You know, the things you ignore. \textit{Love thy neighbour} you scream as your soldiers run rampant during the crusades.''
\newline
\tab
``That’s not --''
\newline
\tab
``Your next line is ‘that’s not what real Christians are like’,'' she freezes up, anger flushes her face a bright crimson. ``You want to save everyone, to show them the love of your god --''
\newline
\tab
``I told you, stop saying that, it’s \textit{the Lord} not --''
\newline
\tab
``Really? Because he isn’t my god, he’s yours. Why the fuck would I worship a deity who defines my existence as sinful? It’s your god, not mine, and I’m sure as hell not going to refer to him as lord.'' She reluctantly backs down. The war hasn’t ended just yet.
\newline
\tab
``You still can’t call that real Christianity. They hurt and killed people. I’m sure the Lord sent them all to hell.'' She remains clearly ignorant of the obvious.
\newline
\tab
``And what about the people they killed? Did those people go to hell?''
\newline
\tab
She replies meekly, ``no they --''
\newline
\tab
``Really? Those fake Christians tried to save them and show them the love of your god because they were different. Non-believers who dismissed your god, people like me.''
\newline
\tab
``No. Not like you! You’re not natural! The Lord’s judgment reaches all. You’re going to hell for your choice!'' she retorts in a bout of confidence, causing passing strangers to begin staring at us.
\newline
\tab
``Who the hell said it was a choice? Did your god whisper in your ear while you sleep giving you \textit{fucking clairvoyance}?''
\newline
\tab
``It’s obviously a choice! It’s so popular now to come out as gay or bisexual. It’s just a phase you’ll grow out of. Once you do, you’ll come crawling back to me, begging to date me and saying you were wrong.''
\newline
\tab
``Like any guy would ever date you.''
\newline
\tab
``You know, I thought you could be saved. I thought I could show you the Lord’s love. I guess you’re just going to burn in hell.'' She replies smugly before walking past me, over to her friends. She begins laughing in an eerily fake way. I stand there for a moment, attentively listening. ``He asked me out! Can you believe it? So gross! I turned him down, obviously!'' they all start laughing, completely ignorant of her previous contradictions. \textit{That bitch}!
\newline
\tab
The adrenaline still hasn’t worn off. I approach the group. ``Why the fuck would I, of all people, ask you out if I’m gay? Last I checked, you were the one spewing bullshit about how you were going to date and convert me. That’s why \textit{you} asked \textit{me} out, right?'' They turn to her in doubt for a moment. She doesn’t respond.
\newline
\tab
``Leave her alone!'' one of them shouts. ``What do you know about \textit{real} love, faggot?''
\newline
\tab
「\ruby{偽}{ぎ}\ruby{善}{ぜん}\ruby{者}{しゃ}め」 I can no longer respond in their tongue. 「\ruby{貴}{き}\ruby{様}{さま}らはただ\ruby{偽}{ぎ}\ruby{善}{ぜん}\ruby{者}{しゃ}だ！」I can see it in their eyes. Despite not having any understanding of the language, they know what I said. 「\ruby{自}{じ}\ruby{分}{ぶん}の\ruby{声}{くえ}\ruby{聞}{き}こえますか？\ruby{糞}{くそ}\ruby{偽}{にせ}\ruby{物}{もの}\ruby{人}{じん}！」 their hypocrisy infuriates me more than anything else. 
\newline
\tab
One of them tries to retort. ``Fucking --''
\newline
\tab
「\ruby{黙}{だま}つて\ruby{死}{し}ね！」 I scream at them. I attempt to walk past them, but she blocks my path. She’s a foot and a half shorter than me. I look down at her, enraged. ``move,'' I say, semi-quietly.
\newline
\tab
``Then admit you’re not gay. It’s just a fad and you know it!''
\newline
\tab
``Aah yes, a fad; just like what the Romans thought of your cult. What the fuck do you know?''
\newline
\tab
``It’s obviously a choice! If it wasn’t that means you inherited it genetically. How could you be born if your parents are gay? They can’t have children!'' She looks so smug at reasoning she probably plucked from the internet.
\newline
\tab
``Why are you different from your brother? There are two reasons: the first is that he’s much less ugly than you. The second is environment. Just because you grew up in the same household doesn’t mean you grew up the same way. Saying that it’s purely genetic is the same as saying there’s no difference between you and your brother.''
\newline
\tab
``It’s still a sin and it’s wrong. It goes against the natural order of things. Even you can’t deny that. Or are you going to try and be a ‘hero’ and fight a point you can’t win? You disgust me faggot!'' 
\newline
\tab
``You really took the whole \textit{love thy neighbour} thing to heart, didn’t you?'' I push her out of my way and walk back to school. 
\newline
\tab
``What the hell is your problem?'' one of her companions asks.
\newline
\tab
``My problem? You make it seem like I wasn’t the one being called a faggot because my existence goes against your beliefs. Mindlessly following orders like that makes you as bad as Nazis.'' I walk back to school, ignoring the slurs they shout at me. I can’t focus properly. The adrenaline wore off a while ago. I make my way to my locker, pack my bag, and stand in the stairwell of the emergency exit. The bell rings. I sit motionless and hidden as a sea of students pushes their way to their next class. None of them notice me. Three minutes after the bell, the stairway’s only auditory illumination is the sound of my breathing. There’s nobody else here. I open the emergency door and walk out to the bus stop. The alarm never worked for that door. The stairway is engulfed in silence. It’s 13:27. All lunch breaks ended a while ago. The bus stop is empty. I wait in silence for the bus to come. I don’t think to pull out my headphones and play music. I don’t know what to do.
\newline
\tab
Five minutes pass. A bus comes and I ignore it accidentally. I can’t sort out my thoughts properly. It’s her fault. I should’ve never talked to her in the first place. I had a feeling she was going to be like that. They always are. Even if they pretend not to be, you can see the pity in their eyes. They disgust me. That’s why I haven’t told my parents. I’m sure they would say they support me, then go consult the priest for advice on how to \textit{fix} me. 
\newline
\tab
Another bus comes. This time, I get on. I sit at the back, staring at the window, opaque from all the dirt. いじわる\ruby{人}{じん}. She’s probably going to tell one of the admins that I harassed her. It’s four against one in that case. Even if I’m in the right, I’d lose. \ruby{糞}{くそ}！
\newline
\tab
I get off the bus three stops early, only fully realizing it after the bus leaves. I begin walking home, staring at the concrete sidewalk, void of colour. My parents shouldn’t get home for a few hours. At the very least, the school’s going to call about me skipping class. I can probably just tell my parents I’m feeling sick. I can skip tomorrow that way too. Then what?
\newline
\tab
I get to the door of my house. While going to unlock it, I drop my keys. Sighing, I pick them up and enter my empty house. I take off my shoes, walk up to my room, drop my bag on the floor and collapse onto my bed. I want to disappear but can’t. No, that’s not right. I want the world to disappear -- to end. I want her to know what it feels like to have nothing. I want her to suffer with me.
\newline
\tab
As nice as that would be, even I can see it’s wishful thinking. There’s not much I can do on my end to make her suffer. My thoughts merge with a sudden bout of fatigue. I’m pulled into sleep. In the edge of consciousness, I only hope I wake up and find out this whole day was a dream. There’s no god for me to pray to. I can only hope. 
\newline
\tab
I’m in class, though I’m not sure which one. I sit in the middle of the classroom in a monochrome world. The teacher writes on the board, speaking words nobody hears. He never turns around to look at the class. He kept teaching, ignoring all going on outside of his head. He acts programmed. It’s off-putting. The students around me have all turned to face their little groups. They talk and laugh as if passing on new rumours to each other. Even though I can’t understand most of what they’re saying, I know those rumours are about me. It makes no difference. I’ve always been alienated. I stare forward, void of emotion. This doesn’t feel nearly -- ``Faggot!'' one of them shouts at me. The whole class bursts into laughter. The teacher does nothing. Another one shouts it, knowing the teacher doesn’t care. More of them join in. They start chanting. ``Faggot! Faggot! Faggot!'' I don’t know what to do. I start down at my desk and cover my ears with my hands. It does nothing to block the chanting. The door opens and, like a saint, she walks in, silencing the class. They still continue through the chanting motions, as if she had pressed a magic mute button. ``Let me save you.'' She says in a delicate and kind voice. Everything turns red.
\newline
\tab
I wake up, streaming. My mother bursts into my room only seconds later. ``Everything alright?'' She asks in a tongue she hasn’t fully mastered.
\newline
\tab
``I’m fine. It was just a bad dream.'' I reply, almost in tears.
\newline
\tab
``You covered in sweat!'' she says, moving closer and inspecting my bed. 
\newline
\tab
```you are', mother.'' She smiles and nods, making mental note of the correction. ``I had a fever, so I came home early. I’m going to go shower.'' I say, getting out of my drenched bed and making my way to the other side of the hallway. For a moment, it feels as if everything suddenly turned grey. I freeze out of fear, half expecting her to walk into my house. My mother turns to me, worried. I turn back and smile before entering the bathroom.
\newline
\tab
I turn the shower on. Steam begins to engulf me. I stare down at the white tiles. I can feel my face turning pale. It’s a slow process. Increasing stress coming from my thoughts manifests in a physical pain I can’t run away from. I’m drowning. It feels like trying to surface from the depths of a lake, only to find a thick layer of ice blocking your escape. With your remaining energy, you cry for help and bash at the ice, only for nothing to happen. There’s no one to save me. The water is grey.
\newline
\tab
I get out and head back to my room. I take the sweat-soaked sheets off my bed, tossing them to the ground to wash later. I don’t want to put the effort into washing them just yet. I don’t want to think about anything right now, though I doubt I can actually stop myself. I fall onto my mattress. My mother would kill me if she saw me like this. I’ll only be a few minutes.
\newline
\tab
I wake up in the school halls, standing in a crowd of people. Without drawing too much attention to myself, I slowly make my way forward, through the crowd to see what caused all the commotion. At the centre of attention, I see her face -- in tears. She’s kneeling on the ground facing the crowd, somehow managing to scream apologetic profanities. I can’t really tell what she’s saying or trying to convey. I sit there smirking as the people around me scream at her. Even now, I feel disassociated with the group. \textit{I’m not her}. I tell myself. \textit{I’m better}. They scream all these accusations of things she’s done. Interspersed with a plea for forgiveness, she shouts obscenities and attacks at them. Yet, my crimes are never brought into the light, and I don’t have the voice to overpower anyone. Even now, I’m still ignored. It’s still nice to see her being shoved around by a crowd, seeing her stripped of her privilege. I look down on her, bearing a grin that forces recognition and fear into her eyes. She screams at me, as if she has any sort of power.
\newline
\tab
Four girls push their way through the crowd, just as I think she’s going to be attacked, they kneel down around her and help her up, acting as guards and shaming \textit{us} for \textit{our} actions. The grin is stolen from my face. Why? After all this time, all I wanted was to watch her suffer like I did. Why does she have people who come to her rescue? Where were they when I was shamed for being gay? My only wish...
\newline
\tab
I wake up, infuriated at my failure. She’s probably already gone to one of the admins and spoon-fed them bullshit with her little group of dogs. They’re not going to take my word for shit, even I can see that. They’re probably going to think the same way as well. ``It’s just a trend. You’re only saying it to fit in. Nobody’s actually going to believe that!'' \ruby{糞}{くそ}！I shouldn’t go to school tomorrow. Even then, my parents are going to question me. My ``fever'' is gone now. It’ll be hard to use that as an actual excuse.
\newline
\tab
「ご\ruby{飯}{はん}」I hear my mother say from the room below me. I get up and walk downstairs. I’ll have to wing an excuse. There are no other options at this point. Anything to get out of school tomorrow will work. Where is that going to get me? I’ll have to tell them eventually. At least this way they might try and help my school situation. They’ll deal with my school issues before consulting a priest about fixing me -- even they have priorities over religion. I’ll have a temporal support of sorts this way. After that, I’m not too sure what’ll happen.
\newline
\tab
I sit down at the table and take a deep breath. ``I have something important to tell you,'' I say to my parents.
\newline
\tab
``Everything okay?'' my mother asks with much more concern in her voice than she had a few hours ago. 
\newline
\tab
I look at them with the most fear I’ve ever felt in my life. I take another deep breath, which only serves to increase my parents’ worry. I close my eyes. One second has passed. Two seconds have passed. Three seconds have passed. My eyes open. ``I’m gay.''
\end{CJK*}
\end{document}