\documentclass[a4paper, 12pt]{book}
\usepackage[utf8]{inputenc}
\usepackage{authblk}
\usepackage{geometry}
\usepackage{setspace} 
\usepackage{amsmath}
\usepackage{textcomp}
\geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 top=20mm,
}
\title{Two's Complement}
\author{Liam Gardner}
\date{\today}
\doublespacing
\newcommand\tab[1][1cm]{\hspace*{#1}}
\begin{document}
\maketitle
\tab
I take off my plain, navy t-shirt and toss it on the floor. “What are you - \textinterrobang” she shouts, embarrassed, quickly moving her hands to cover her eyes. She stops before they reach her face. I watch as her face contorts from embarrassment to fear. It was like her brown eyes were forced to readjust to the darkness of the room. “What happened?” she asked slowly, staring at the scar on my chest. A four-point star of unhealed, slightly pink skin decorates an area highlighting the centre of my ribcage.
\newline
\tab
“My father was an alcoholic.” I start, avoiding eye contact. “One night, when I was maybe ten or eleven, he came home, drunk as usual. He had a beer bottle in his hand. As he walked in the door, my mother asked if he’d been drinking. He silenced her with a glance and smashed the beer bottle on the side of the door. None of us knew what he was thinking. I ran over, assuming he had hurt my mother. My hubris seemed only to have angered him more. He looked as though he was going to push me away. When he tried, he used the hand holding the broken bottle. It slid right into my chest.” I place a hand over my scar. The skin is still a tad bit sensitive. She smiles warmly, placing her hand on mine. Though meant as a kind gesture, I can see in her eyes that she wants me to continue more than she wants to comfort me.
\newline
\tab
“When I woke up. I was on a hospital bed. Doctors were saying all sorts of things I couldn’t hear, nor understand. All I knew is that I would be there for a long time. As it turns out, there were no serious injuries and I only stayed there for a month. Though I was bedridden, I felt safe for the first time in my life. I began to realize that… maybe living with my family isn’t a good thing.” I sit on her bed, slumping my shoulders. It’s surprisingly neat, knowing her. I start to wish I could put my shirt back on, but I don’t think I could reach it from here. It’s just barely out of reach for me. She sits down beside me. For the first time in my life, I’m actually fully opening up to someone. I’m scared, but her presence prevents me from stopping. I smile at her weakly, and she puts a hand on my back. It’s not really comforting. It feels as though she’s trying to coax me into continuing, though in her eyes I notice a tinge of empathy.
\newline
\tab
“When I started middle school, I did whatever I could to avoid being home.  I joined as many sports teams as possible. I would always try hard enough to make sure that I wasn’t the weakest link, but even my teammates could see that I was expecting to fail with everything I did. I unintentionally created more animosity towards me, especially from people who weren’t as good as me. They couldn’t do anything about it though. One day, I looked at one of my teammates on the soccer team, there was something in his eyes that told me he hated me. I couldn’t figure out why, and I didn’t want to find out. So when I got the chance, I quit the soccer team. For field trips and sports games, I made sure I knew how to forge my mother’s signature. I was in as many places as possible and made sure to remain as close to the background as possible. Even though it was only middle school, neither my parents, nor I showed up to my graduation.” I turn to her and smile. I get up, put my shirt back on and head to the door.
\newline
\tab
“Wait!” she says, probably a bit too loud. As I turn to her, I make out the red digits on a clock she has set on her nightstand. 23:15. We make eye contact and she blushes a bit. “I want to hear more.”
\newline
\tab
I smile gently. “It’s late,” I reply with an unintentional delicacy in my voice.
\newline
\tab
“Then stay.” It takes her a few seconds to process what she said. Her face turns red, but she doesn’t back down.
\newline
\tab
“Okay,” I whisper, walking over and re-assuming my position on her bed. She puts her head on my shoulder and smiles. “Highschool was different. We had a computer club. I would spend most of my time there after school, learning to program. It was much more in the background than sports teams, and most students didn’t know we had that club in the first place. On Saturdays, I would volunteer at a local library. It was long hours that kept me away from my house. Almost nobody spoke, and there were no non-verbal conversations. To keep up my physical health, I still joined a couple of sports teams in highschool. After a couple months, I started a GitHub account called Phantom of Salieri. That’s where I put most of my projects.” 
\newline
\tab
She turns to me with recognition in her eyes. “So you aren’t Italian after all!” she glares at me playfully.
\newline
\tab
I smile back. “Moving on. I started to attract the attention of the computer science teacher. I was coaxed into taking grade eleven computer science and engineering. Engineering was my safe haven. It was cluttered and disorganized, which gave me the feeling of familiarity. Yet, the fact that it wasn’t in complete disrepair separated it’s atmosphere from that of my house. I finally understood what a home is meant to feel like. I was a quiet, average student. I got the work done speaking as minimally as possible – I think throughout two years I spoke a total of fifteen words. Just like the rest of my life, I remained in the background. I managed to take AP computer science and the first of two AP calculus courses. Though I didn’t really study all that much, I managed to score perfect on both exams. A year later, I scored perfect on the second AP calculus exam, though I spent time in most of my other classes studying for it. Right after my last AP exam, my father was arrested. The school year ended then for me. I began to think that it was my fault he was arrested. I started believing that he wanted revenge and could walk into whatever room I was in with the intent and power to kill me. I was omitted from writing final exams due to the anxiety and paranoia taking over. My grades only fell slightly due to things being reweighted. At the beginning of the last month of school, I received an offer from the university of waterloo engineering program.” I sigh. I keep having to remind myself that that chapter of my life is done. I look over at my shoulder to see her eyes closed. I smile, stroking her hair gently.
\newline
\tab
“You think I’m asleep, don’t you?” she says, grinning.
\newline
\tab
“I did.” I admit, smiling back at her. I pull my hand back and she frowns at me. “You want me to continue?” I ask, mildly confused. She nods with a beaming smile. “What are you, a cat?” I reply tauntingly. 
\newline
\tab
She retakes her position on my shoulder, closes her eyes and replies in a soft whisper. “Only for you.” Outwardly, I pretend not to notice. Inside, I feel like it’s okay to continue to tell her about my life. I feel safe with her.
\newline
\tab
“For various reasons, I accepted the engineering offer. One of them being for emotional security and familiarity. I wanted to feel the same way I felt in my engineering class. To a lesser extent, I also wanted others to feel that way too. I decided that I would stay in engineering and in school for as long as possible. My marks on the AP exam let me take some second-year courses during my first semester. Much like the rest of my life, I did as many things as possible to remain in the background. After a few months, I began to realize that I’m separated enough from my family that they can’t affect me here. University was like my hospital bed. My parents never visited so I didn’t have to worry about seeing them. My father never came for me and I got no messages from my mother. I was finally free.” She embraces me, just as I thought he had actually fallen asleep.
\newline
\tab
I place my hand over hers and continue my story. “I joined a small study group and became close friends with the people there. Though I was still scared to speak informally to others, little by little I began talking to more people. By the time I entered second year, I had pretty much completely integrated with the student populous. I went from being that student to another student. During reading week of my second year, I went back and visited my highschool. I wanted to thank my engineering teacher and tell him that I’d be graduating a year early due to the AP exams and some stroke of good fortune. He looked at me and apologized, asking if I was one of his students. I had completely forgotten about how I went through highschool existing only in the background. It’d make sense that he’d forget me. The class didn’t have an exam, so he was never told to reweight any of my assessments. It would make sense that he didn’t notice my frequent absences.” Though it’s been five years since that happened, I can feel tears begin to well up in my eyes. I don’t want to cry again.
\newline
\tab
“It’s okay,” she whispers, squeezing me slightly.
\newline
\tab
“Thank you,” I reply in a tone so soft that I’m not sure if she even heard it. We stay like this for a couple minutes until I feel comfortable continuing. “As a form of therapy, someone recommended that I begin to write to release my emotions, kind of like a diary but instead of keeping track of events it’s more keeping track of emotions. I started off writing to clarify hypothetical situations and conversations, setting in stone a single possibility of events – which typically ended up being the worst possibility. That only made things worse, so I began to write by developing characters around an emotion I was feeling and building a scenario around them. The stronger the emotion, the more I would write. What I wrote wasn’t the scenarios in my head anymore but the emotions I felt from them. The characters and situations were an afterthought with no relation to me whatsoever. That style of writing meant I was completely okay showing my work to other people.” I can see it written on her face. We’re approaching the part of the story she wanted to hear most. Her eyes are open.
\newline
\tab
“Some recommended that I send them to a publisher, which I didn’t do for many reasons. At the time, that was my last year before I’d be starting grad school, and I was debating between staying here, going to Toronto or going to OIST. I –”
\newline
\tab
She pokes me, cutting me off. “What’s that?” she asks, looking up at me.
\newline
\tab
I stare, mesmerized by her large, brown eyes for a few seconds before responding. “Okinawa Institute of Science and Technology.” I reply with a mild boom to my voice for dramatic purposes.
“You were going to go to the other side of the world why exactly?” I’m not exactly sure when, but her head moved from my shoulder to my lap where she comfortably resides looking up at me.
\newline
\tab
“There was a guy I looked up to that got his PhD in quantum physics there.” He was really the only reason I knew of it in the first place.
\newline
\tab
She began laughing. “That’s it? That’s the only reason?”
\newline
\tab
“Yeah, how else are you meant to choose?” I retort with an uncontrollable grin on my face. She reaches her hand up, placing it softly on my cheek. Her eyes shift into sincerity. I’m once again being coaxed into continuing my story; only this time, it’s different.  “The other reason I didn’t want to give it to a publisher was because I was scared of being asked to change certain scenes. In my head, they each contributed to the dominant impression of the piece. Changing any scene completely removes the underlying emotion the piece was written on. It would be like stopping Picasso from using blue. I decided that if I chose to stay here, I would write a novel and send that to a publisher to see what they would suggest.”
\newline
\tab
“Collage of withered hearts,” she says while staring at me with that same level of sincerity.
\newline
\tab
“To those of evaporated souls.” I corrected. I’m surprised she knew of my first published novel. “It was a collection of successive short stories. No immediately visible plot, only character interactions. I wrote a chapter a day for three months and it was rejected because the actual plot was entirely sub textual. The average reader wouldn’t be able to see the plot and they didn’t want to publish a book people couldn’t understand. Writing is an art. Publishing is business. This all happened after I decided to stay here. My family was here, not in Toronto. I also don’t speak nearly enough Japanese to survive at OIST. So, I restarted. I changed my style slightly from developing characters around an emotion to developing scenarios to produce an emotion and minimizing the character interaction necessary to fit the scenario. At the time I was taking a class on the calculus of variance, so I had begun to really study the mathematics of engineering.”
\newline
\tab
“Let me read your first novel,” she said. “I know you more than most. I’m completely capable of picking up any subtext you could’ve written.” She demands in a cutely serious tone.
\newline
\tab
“We’ll see. I can’t give it to you if you keep me in this room for the rest of my life.” I reply with a small grin on my face. I really wouldn’t mind being stuck here with you. Her face turns red and I smile gently. I stare over at the clock. It would seem as if I’m not the fastest storyteller. 02:15. I guess I really am going to be staying. “For obvious reasons, I published with the university under the penname Spettro Salieri.”
\newline
\tab
“And you wonder why people think you’re Italian?” She asks as a heartful attack.
\newline
\tab
“It means ‘Salieri’s Spectre.’ Nobody has a name like that.” I reply with playful defense for a name I’ve come to assume. “Anyway, after that novel went through, I sent in a couple of my short stories. They loved them much more than the novel and I published the first thirty stories as a collection. When I continued writing novels, my characters and scenarios ended up reflecting the kind of math I was studying. When studying numerical analysis, I wrote a novel about a singular event. Seven hundred pages of one car crash. Every single perspective was shown except one. Numerical Analysis won’t give the correct answer, only an approximation, and so, the reader only got an approximation as to what the entire event was like. There are similar stories behind most of my other novels as well.”
\newline
\tab
“Your fifth book, the one that was focused on all possible outcomes that could come from choosing to go on a walk instead of studying. what was that on?” She asks, skeptical of the true nature of mathematics.
\newline
\tab
“The one where the goal was to pick the best possible outcome?” 
\newline
\tab
“Yeah! That one!”
\newline
\tab
“Operations research.”
\newline
\tab
“So they really do stem from math.” She replies, satisfied with my answer.
\newline
\tab
“Everything begins and ends with numbers.” She smiles at my philosophical comment. “Moving on from that. Last year I was asked if I wanted to teach a first-year calculus class. Obviously, there were many implications behind having a class and obviously I considered none of them. I was told to get material ready for next year’s students. Come the beginning of this year, I’m standing in an auditorium filled with students teaching Calc 1. I have my own students now! I feel like for being twenty-three, that’s probably much more of an accomplishment than other grad students teaching classes.”
\newline
\tab
“You’re only 23?” she asks, her eyes and face plagued with shock. She sits up, barely missing a collision with my head.
\newline
\tab
“Yeah, why?”
\newline
\tab
“I thought you were the older one!” she replies, still shocked at my youth. “I’m turning twenty-five at the end of this year.” We both burst out in laughter. I look back on my life while staring into her eyes. \textit{This is what it feels like to be at home.}
\end{document}